\section*{Acknowledgments}
\addcontentsline{toc}{section}{Acknowledgments}

The author thanks the anonymous referees for their careful reading and valuable suggestions that improved the exposition of this paper.

\begin{thebibliography}{99}

\bibitem{alaeekhurilee2020}
A.~Alaee, M.~Khuri, and D.~A.~Lee,
\newblock Geometric inequalities for quasi-local masses,
\newblock {\em Comm.\ Math.\ Phys.}, 378 (2020), 467--505.

\bibitem{allenbrydentkazaraskhuri2025}
B.~Allen, E.~Bryden, D.~Kazaras, and M.~Khuri,
\newblock Proof of the spacetime Penrose inequality with suboptimal constant in the asymptotically flat and asymptotically hyperboloidal regimes,
\newblock {\em arXiv:2504.10641} [math.DG], preprint, 2025.
\newblock \texttt{https://arxiv.org/abs/2504.10641}

\bibitem{anhe2025}
X.~An and T.~He,
\newblock On Kerr black hole formation with complete apparent horizon and a new approach toward Penrose inequality,
\newblock {\em arXiv:2505.11399} [gr-qc], preprint, 2025.
\newblock \texttt{https://arxiv.org/abs/2505.11399}

\bibitem{agostiniani2022}
V.~Agostiniani, L.~Mazzieri, and F.~Oronzio,
\newblock Monotonicity formulas in potential theory,
\newblock {\em Calc.\ Var.\ Partial Differential Equations}, 61 (2022), art.~120.
\newblock \texttt{DOI: 10.1007/s00526-022-02223-y}

\bibitem{ammo2022}
V.~Agostiniani, C.~Mantegazza, L.~Mazzieri, and F.~Oronzio,
\newblock Riemannian Penrose inequality via nonlinear potential theory,
\newblock {\em Comm.\ Math.\ Phys.}, 402 (2023), 2085--2148.
\newblock \texttt{DOI: 10.1007/s00220-023-04763-2}

\bibitem{arnold1990singularities}
V.~I.~Arnold,
\newblock {\em Singularities of Caustics and Wave Fronts},
\newblock Mathematics and its Applications (Soviet Series), vol.~62, Kluwer Academic Publishers, 1990.

\bibitem{beckner1989}
W.~Beckner,
\newblock A generalized Poincar\'e inequality for Gaussian measures,
\newblock {\em Proc.\ Amer.\ Math.\ Soc.}, 105 (1989), 397--400.

\bibitem{BEE96}
J.~K.~Beem, P.~E.~Ehrlich, and K.~L.~Easley,
\newblock {\em Global Lorentzian Geometry},
\newblock Marcel Dekker, New York, second edition, 1996.

\bibitem{amo2022}
V.~Agostiniani, L.~Mazzieri, and F.~Oronzio,
\newblock Monotonicity formulas for quasilinear PDEs and the level set method,
\newblock {\em arXiv:2212.12152} [math.DG], preprint, 2022.
\newblock \texttt{https://arxiv.org/abs/2212.12152}

\bibitem{amo2024}
V.~Agostiniani, L.~Mazzieri, and F.~Oronzio,
\newblock A Green's function proof of the positive mass theorem,
\newblock {\em Comm.\ Pure Appl.\ Math.}, 77 (2024), 3027--3083.
\newblock \texttt{DOI: 10.1002/cpa.22185}

\bibitem{anderson2000}
M.~T.~Anderson,
\newblock On stationary vacuum solutions to the Einstein equations,
\newblock {\em Ann.\ Henri Poincar\'e}, 1 (2000), 977--994.

\bibitem{anderssonmetzger2009}
L.~Andersson and J.~Metzger,
\newblock The area of horizons and the trapped region,
\newblock {\em Comm.\ Math.\ Phys.}, 290 (2009), 941--972.

\bibitem{bartnik1986}
R.~Bartnik,
\newblock The mass of an asymptotically flat manifold,
\newblock {\em Comm.\ Pure Appl.\ Math.}, 39 (1986), 661--693.

\bibitem{bowen1980}
J.~M.~Bowen and J.~W.~York,
\newblock Time-asymmetric initial data for black holes and black-hole collisions,
\newblock {\em Phys.\ Rev.\ D}, 21 (1980), 2047--2056.

\bibitem{bray2001}
H.~L.~Bray,
\newblock Proof of the Riemannian Penrose inequality using the positive mass theorem,
\newblock {\em J.\ Differential Geom.}, 59 (2001), 177--267.

\bibitem{bray2009}
H.~L.~Bray,
\newblock On the positive mass, Penrose, and ZAS conjectures in general dimension,
\newblock in {\em Surveys in Geometric Analysis and Relativity}, ALM 20 (2011), 1--27.

\bibitem{braychrusciel2004}
H.~L.~Bray and P.~T.~Chru\'sciel,
\newblock The Penrose inequality,
\newblock in {\em The Einstein Equations and the Large Scale Behavior of Gravitational Fields} (P.~T.~Chru\'sciel and H.~Friedrich, eds.), Birkh\"auser, 2004, 39--70.

\bibitem{braykhuri2010}
H.~L.~Bray and M.~Khuri,
\newblock A Jang equation approach to the Penrose inequality,
\newblock {\em Discrete Contin.\ Dyn.\ Syst.}, 27 (2010), 741--766.

\bibitem{buntingmasood1987}
G.~L.~Bunting and A.~K.~M.~Masood-ul-Alam,
\newblock Nonexistence of multiple black holes in asymptotically Euclidean static vacuum space-time,
\newblock {\em Gen.\ Relativity Gravitation}, 19 (1987), 147--154.

\bibitem{chandrasekhar1983}
S.~Chandrasekhar,
\newblock {\em The Mathematical Theory of Black Holes},
\newblock Oxford University Press, 1983.

\bibitem{cheeger1983}
J.~Cheeger,
\newblock Spectral geometry of singular Riemannian spaces,
\newblock {\em J.\ Differential Geom.}, 18 (1983), 575--657.

\bibitem{cheegercolding1997}
J.~Cheeger and T.~H.~Colding,
\newblock On the structure of spaces with Ricci curvature bounded below~I,
\newblock {\em J.\ Differential Geom.}, 46 (1997), 406--480.

\bibitem{cheegernabervaltorta2015}
J.~Cheeger, A.~Naber, and D.~Valtorta,
\newblock Critical sets of elliptic equations,
\newblock {\em Comm.\ Pure Appl.\ Math.}, 68 (2015), 173--209.

\bibitem{chrusciel1986}
P.~T.~Chru\'sciel,
\newblock Boundary conditions at spatial infinity from a Hamiltonian point of view,
\newblock {\em Topological Properties and Global Structure of Space-Time} (P.~G.~Bergmann and V.~de Sabbata, eds.), Plenum Press, 1986.

\bibitem{chruscielherrzlich2003}
P.~T.~Chru\'sciel and M.~Herzlich,
\newblock The mass of asymptotically hyperbolic Riemannian manifolds,
\newblock {\em Pacific J.\ Math.}, 212 (2003), 231--264.

\bibitem{chrusciel2001}
P.~T.~Chru\'sciel, E.~Delay, G.~J.~Galloway, and R.~Howard,
\newblock Regularity of horizons and the area theorem,
\newblock {\em Ann.\ Henri Poincar\'e}, 2 (2001), 109--178.

\bibitem{christodoulou1999}
D.~Christodoulou,
\newblock On the global initial value problem and the issue of singularities,
\newblock {\em Class.\ Quantum Grav.}, 16 (1999), A23--A35.

\bibitem{dibenedetto1983}
E.~DiBenedetto,
\newblock $C^{1+\alpha}$ local regularity of weak solutions of degenerate elliptic equations,
\newblock {\em Nonlinear Anal.}, 7 (1983), 827--850.

\bibitem{dibenedetto1993}
E.~DiBenedetto,
\newblock {\em Degenerate Parabolic Equations},
\newblock Springer-Verlag, New York, 1993.

\bibitem{EHLS2016}
M.~Eichmair, L.-H.~Huang, D.~A.~Lee, and R.~Schoen,
\newblock The spacetime positive mass theorem in dimensions less than eight,
\newblock {\em J.\ Eur.\ Math.\ Soc.}, 18 (2016), 83--121.

\bibitem{federer1969}
H.~Federer,
\newblock {\em Geometric Measure Theory},
\newblock Grundlehren der Mathematischen Wissenschaften, vol.~153, Springer-Verlag, 1969.

\bibitem{gallowayschoen2006}
G.~J.~Galloway and R.~Schoen,
\newblock A generalization of Hawking's black hole topology theorem to higher dimensions,
\newblock {\em Comm.\ Math.\ Phys.}, 266 (2006), 571--576.

\bibitem{garofalo1987}
N.~Garofalo and F.-H.~Lin,
\newblock Monotonicity properties of variational integrals, $A_p$ weights and unique continuation,
\newblock {\em Indiana Univ.\ Math.\ J.}, 35 (1986), 245--268.

\bibitem{gilbarg2001}
D.~Gilbarg and N.~S.~Trudinger,
\newblock {\em Elliptic Partial Differential Equations of Second Order},
\newblock Springer-Verlag, Berlin, 2001 (reprint of the 1998 edition).

\bibitem{gilbargtrudinger}
D.~Gilbarg and N.~S.~Trudinger,
\newblock {\em Elliptic Partial Differential Equations of Second Order},
\newblock Springer-Verlag, Berlin, second edition, 1983.

\bibitem{gross1975}
L.~Gross,
\newblock Logarithmic Sobolev inequalities,
\newblock {\em Amer.\ J.\ Math.}, 97 (1975), 1061--1083.

\bibitem{hankhuri2013}
Q.~Han and M.~Khuri,
\newblock Existence and blow-up behavior for solutions of the generalized Jang equation,
\newblock {\em Comm.\ Partial Differential Equations}, 38 (2013), 2199--2237.

\bibitem{hankhuri2016}
Q.~Han and M.~Khuri,
\newblock The linearization of the generalized Jang equation and applications,
\newblock {\em J.\ Geom.\ Phys.}, 105 (2016), 1--30.

\bibitem{hawking1971}
S.~W.~Hawking,
\newblock Gravitational radiation from colliding black holes,
\newblock {\em Phys.\ Rev.\ Lett.}, 26 (1971), 1344--1346.

\bibitem{hersch1970}
J.~Hersch,
\newblock Quatre propri\'et\'es isop\'erim\'etriques de membranes sph\'eriques homog\`enes,
\newblock {\em C.\ R.\ Acad.\ Sci.\ Paris S\'er.\ A-B}, 270 (1970), A1645--A1648.

\bibitem{huisken1984}
G.~Huisken,
\newblock Flow by mean curvature of convex surfaces into spheres,
\newblock {\em J.\ Differential Geom.}, 20 (1984), 237--266.

\bibitem{huisken2001}
G.~Huisken and T.~Ilmanen,
\newblock The inverse mean curvature flow and the Riemannian Penrose inequality,
\newblock {\em J.\ Differential Geom.}, 59 (2001), 353--437.

\bibitem{ilmanen2001}
T.~Ilmanen,
\newblock Lectures on mean curvature flow and related equations,
\newblock Lecture notes, ETH Z\"urich, 2001.

\bibitem{jang1978}
P.~S.~Jang,
\newblock On the positivity of energy in general relativity,
\newblock {\em J.\ Math.\ Phys.}, 19 (1978), 1152--1155.

\bibitem{jangwald1977}
P.~S.~Jang and R.~M.~Wald,
\newblock The positive energy conjecture and the cosmic censor hypothesis,
\newblock {\em J.\ Math.\ Phys.}, 18 (1977), 41--44.

\bibitem{jaramillo2011}
J.~L.~Jaramillo,
\newblock An introduction to local black hole horizons in the 3+1 approach to general relativity,
\newblock {\em Int.\ J.\ Mod.\ Phys.\ D}, 20 (2011), 2169--2204.

\bibitem{kotschwar2009}
B.~Kotschwar,
\newblock Hamilton's gradient estimate for the heat kernel on complete manifolds,
\newblock {\em Proc.\ Amer.\ Math.\ Soc.}, 137 (2009), 3013--3019.

\bibitem{khurikunduri2024}
M.~Khuri and H.~K.~Kunduri,
\newblock Spacetime harmonic functions and applications to mass,
\newblock {\em Proc.\ Symp.\ Pure Math.}, 105 (2024), 1--23.

\bibitem{kundurimargalefmuth2023}
H.~K.~Kunduri, B.~Margalef-Bentabol, and O.~Muth,
\newblock The spacetime Penrose inequality for cohomogeneity-one initial data,
\newblock {\em Class.\ Quantum Grav.}, 40 (2023), 025003.

\bibitem{leekhuri2022}
D.~A.~Lee and M.~Khuri,
\newblock Stability of spacetime positive mass theorems under Ricci flow,
\newblock {\em J.\ Reine Angew.\ Math.}, 791 (2022), 195--226.

\bibitem{lieberman1988}
G.~M.~Lieberman,
\newblock H\"older continuity of the gradient at a corner for the capillary problem and related results,
\newblock {\em Pacific J.\ Math.}, 133 (1988), 115--135.

\bibitem{lockhartmccowen1985}
R.~Lockhart and R.~C.~McOwen,
\newblock Elliptic differential operators on noncompact manifolds,
\newblock {\em Ann.\ Scuola Norm.\ Sup.\ Pisa Cl.\ Sci.\ (4)}, 12 (1985), 409--447.

\bibitem{mars2009}
M.~Mars,
\newblock Present status of the Penrose inequality,
\newblock {\em Class.\ Quantum Grav.}, 26 (2009), 193001.

\bibitem{miao2002}
P.~Miao,
\newblock Positive mass theorem on manifolds admitting corners along a hypersurface,
\newblock {\em Adv.\ Theor.\ Math.\ Phys.}, 6 (2002), 1163--1182.

\bibitem{penrose1973}
R.~Penrose,
\newblock Naked singularities,
\newblock {\em Ann.\ New York Acad.\ Sci.}, 224 (1973), 125--134.

\bibitem{perelman2002}
G.~Perelman,
\newblock The entropy formula for the Ricci flow and its geometric applications,
\newblock {\em arXiv:math/0211159}, preprint, 2002.
\newblock \texttt{https://arxiv.org/abs/math/0211159}

\bibitem{perelman2003}
G.~Perelman,
\newblock Ricci flow with surgery on three-manifolds,
\newblock {\em arXiv:math/0303109}, preprint, 2003.
\newblock \texttt{https://arxiv.org/abs/math/0303109}

\bibitem{regge1974}
T.~Regge and C.~Teitelboim,
\newblock Role of surface integrals in the Hamiltonian formulation of general relativity,
\newblock {\em Ann.\ Phys.}, 88 (1974), 286--318.

\bibitem{schoen1981}
R.~Schoen and S.-T.~Yau,
\newblock Proof of the positive mass theorem.\ II,
\newblock {\em Comm.\ Math.\ Phys.}, 79 (1981), 231--260.

\bibitem{schoen_yau_1981}
R.~Schoen and S.-T.~Yau,
\newblock Proof of the positive mass theorem.\ I,
\newblock {\em Comm.\ Math.\ Phys.}, 65 (1979), 45--76.

\bibitem{shi2016}
Y.~Shi and L.-F.~Tam,
\newblock Positive mass theorem and the boundary behaviors of compact manifolds with nonnegative scalar curvature,
\newblock {\em J.\ Differential Geom.}, 62 (2002), 79--125.

\bibitem{wald1984}
R.~M.~Wald,
\newblock {\em General Relativity},
\newblock University of Chicago Press, 1984.

\bibitem{schoenyau1979}
R.~Schoen and S.-T.~Yau,
\newblock On the proof of the positive mass conjecture in general relativity,
\newblock {\em Comm.\ Math.\ Phys.}, 65 (1979), 45--76.

\bibitem{schoenyau1981}
R.~Schoen and S.-T.~Yau,
\newblock The energy and the linear momentum of space-times in general relativity,
\newblock {\em Comm.\ Math.\ Phys.}, 79 (1981), 47--51.

\bibitem{szabados2009}
L.~B.~Szabados,
\newblock Quasi-local energy-momentum and angular momentum in general relativity,
\newblock {\em Living Rev.\ Relativity}, 12 (2009), 4.

\bibitem{stampacchia1966}
G.~Stampacchia,
\newblock {\em \'Equations elliptiques du second ordre \`a coefficients discontinus},
\newblock S\'eminaire de Math\'ematiques Sup\'erieures, No.\ 16, Les Presses de l'Universit\'e de Montr\'eal, 1966.

\bibitem{tolksdorf1984}
P.~Tolksdorf,
\newblock Regularity for a more general class of quasilinear elliptic equations,
\newblock {\em J.\ Differential Equations}, 51 (1984), 126--150.

\bibitem{adamshedberg1996}
D.~R.~Adams and L.~I.~Hedberg,
\newblock {\em Function Spaces and Potential Theory},
\newblock Springer-Verlag, Berlin, 1996.

\bibitem{anderssonmars2009}
L.~Andersson and M.~Mars,
\newblock The time evolution of marginally trapped surfaces,
\newblock {\em Class.\ Quantum Grav.}, 26 (2009), 085018.

\bibitem{anderssonmarssimonfaller2008}
L.~Andersson, M.~Mars, and W.~Simon,
\newblock Stability of marginally outer trapped surfaces and existence of marginally outer trapped tubes,
\newblock {\em Adv.\ Theor.\ Math.\ Phys.}, 12 (2008), 853--888.

\bibitem{chakhuri2023}
P.~T.~Chru\'sciel and M.~Khuri,
\newblock Spacetime positive mass theorems for initial data sets with non-compact boundary,
\newblock {\em Int.\ Math.\ Res.\ Not.}, 2023 (2023), 9783--9822.

\bibitem{chill2003}
R.~Chill,
\newblock On the \L ojasiewicz--Simon gradient inequality,
\newblock {\em J.\ Funct.\ Anal.}, 201 (2003), 572--601.

\bibitem{chrusciel1990}
P.~T.~Chru\'sciel,
\newblock On the uniqueness in the large of solutions of Einstein's equations (``strong cosmic censorship''),
\newblock {\em Proc.\ Centre Math.\ Appl.}, 27, Australian National University, 1990.

\bibitem{chruscieldelay2003}
P.~T.~Chru\'sciel and E.~Delay,
\newblock On mapping properties of the general relativistic constraints operator in weighted function spaces,
\newblock {\em M\'em.\ Soc.\ Math.\ Fr.}, 94 (2003), 1--103.

\bibitem{dalmaso1993}
G.~Dal~Maso,
\newblock {\em An Introduction to $\Gamma$-Convergence},
\newblock Birkh\"auser, Boston, 1993.

\bibitem{eichmair2009}
M.~Eichmair,
\newblock The Plateau problem for marginally outer trapped surfaces,
\newblock {\em J.\ Differential Geom.}, 83 (2009), 551--583.

\bibitem{fabeskenigserapioni1982}
E.~B.~Fabes, C.~E.~Kenig, and R.~P.~Serapioni,
\newblock The local regularity of solutions of degenerate elliptic equations,
\newblock {\em Comm.\ Partial Differential Equations}, 7 (1982), 77--116.

\bibitem{garofalolin1986}
N.~Garofalo and F.-H.~Lin,
\newblock Monotonicity properties of variational integrals, $A_p$ weights and unique continuation,
\newblock {\em Indiana Univ.\ Math.\ J.}, 35 (1986), 245--268.

\bibitem{garofalolin1987}
N.~Garofalo and F.-H.~Lin,
\newblock Unique continuation for elliptic operators: A geometric-variational approach,
\newblock {\em Comm.\ Pure Appl.\ Math.}, 40 (1987), 347--366.

\bibitem{geroch1973}
R.~Geroch,
\newblock Energy extraction,
\newblock {\em Ann.\ New York Acad.\ Sci.}, 224 (1973), 108--117.

\bibitem{haaralasarsa2022}
P.~H\"a\"ast\"o and P.~Sarsa,
\newblock On the regularity of the $\omega$-minima of $\Phi$-functionals,
\newblock {\em J.\ Differential Equations}, 324 (2022), 1--39.

\bibitem{hardtlin1987}
R.~Hardt and F.-H.~Lin,
\newblock Mappings minimizing the $L^p$ norm of the gradient,
\newblock {\em Comm.\ Pure Appl.\ Math.}, 40 (1987), 555--588.

\bibitem{hkm1993}
J.~Heinonen, T.~Kilpel\"ainen, and O.~Martio,
\newblock {\em Nonlinear Potential Theory of Degenerate Elliptic Equations},
\newblock Oxford University Press, 1993.

\bibitem{huang2006}
L.-H.~Huang,
\newblock On the center of mass of isolated systems with general asymptotics,
\newblock {\em Class.\ Quantum Grav.}, 23 (2006), 205--221.

\bibitem{juutinenlindqvistmanfredi2001}
P.~Juutinen, P.~Lindqvist, and J.~J.~Manfredi,
\newblock On the equivalence of viscosity solutions and weak solutions for a quasi-linear equation,
\newblock {\em SIAM J.\ Math.\ Anal.}, 33 (2001), 699--717.

\bibitem{kato1995}
T.~Kato,
\newblock {\em Perturbation Theory for Linear Operators},
\newblock Springer-Verlag, Berlin, reprint of the 1980 edition, 1995.

\bibitem{kilpelainenmaly1992}
T.~Kilpel\"ainen and J.~Mal\'y,
\newblock Degenerate elliptic equations with measure data and nonlinear potentials,
\newblock {\em Ann.\ Scuola Norm.\ Sup.\ Pisa Cl.\ Sci.\ (4)}, 19 (1992), 591--613.

\bibitem{lee2019}
D.~A.~Lee,
\newblock {\em Geometric Relativity},
\newblock Grad.\ Stud.\ Math., vol.~201, American Mathematical Society, 2019.

\bibitem{lewis1983}
J.~L.~Lewis,
\newblock Regularity of the derivatives of solutions to certain degenerate elliptic equations,
\newblock {\em Indiana Univ.\ Math.\ J.}, 32 (1983), 849--858.

\bibitem{lindqvist2017}
P.~Lindqvist,
\newblock {\em Notes on the Stationary $p$-Laplace Equation},
\newblock SpringerBriefs in Mathematics, Springer, 2017.

\bibitem{manfredi1988}
J.~J.~Manfredi,
\newblock $p$-harmonic functions in the plane,
\newblock {\em Proc.\ Amer.\ Math.\ Soc.}, 103 (1988), 473--479.

\bibitem{mazya2011}
V.~Maz'ya,
\newblock {\em Sobolev Spaces with Applications to Elliptic Partial Differential Equations},
\newblock Springer-Verlag, Berlin, second edition, 2011.

\bibitem{meekssimonyau1982}
W.~Meeks, L.~Simon, and S.-T.~Yau,
\newblock Embedded minimal surfaces, exotic spheres, and manifolds with positive Ricci curvature,
\newblock {\em Ann.\ of Math.\ (2)}, 116 (1982), 621--659.

\bibitem{melrose1996}
R.~B.~Melrose,
\newblock Differential analysis on manifolds with corners,
\newblock Unpublished lecture notes, MIT, 1996.

\bibitem{metzger2010}
J.~Metzger,
\newblock Blowup of Jang's equation at outermost marginally trapped surfaces,
\newblock {\em Comm.\ Math.\ Phys.}, 294 (2010), 61--72.

\bibitem{meyers1970}
N.~G.~Meyers,
\newblock A theory of capacities for potentials of functions in Lebesgue classes,
\newblock {\em Math.\ Scand.}, 26 (1970), 255--292.

\bibitem{miao2012}
P.~Miao and L.-F.~Tam,
\newblock Evaluation of the ADM mass and center of mass via the Ricci tensor,
\newblock {\em Proc.\ Amer.\ Math.\ Soc.}, 144 (2016), 753--761.

\bibitem{nabervaltorta2017}
A.~Naber and D.~Valtorta,
\newblock Rectifiable-Reifenberg and the regularity of stationary and minimizing harmonic maps,
\newblock {\em Ann.\ of Math.\ (2)}, 185 (2017), 131--227.

\bibitem{petersen2016}
P.~Petersen,
\newblock {\em Riemannian Geometry},
\newblock Graduate Texts in Mathematics, vol.~171, Springer, third edition, 2016.

\bibitem{serrin1964}
J.~Serrin,
\newblock Local behavior of solutions of quasi-linear equations,
\newblock {\em Acta Math.}, 111 (1964), 247--302.

\bibitem{simon1983}
L.~Simon,
\newblock Asymptotics for a class of non-linear evolution equations, with applications to geometric problems,
\newblock {\em Ann.\ of Math.\ (2)}, 118 (1983), 525--571.

\bibitem{villani2009}
C.~Villani,
\newblock {\em Optimal Transport: Old and New},
\newblock Grundlehren der Mathematischen Wissenschaften, vol.~338, Springer-Verlag, Berlin, 2009.

\bibitem{white1991}
B.~White,
\newblock The space of minimal submanifolds for varying Riemannian metrics,
\newblock {\em Indiana Univ.\ Math.\ J.}, 40 (1991), 161--200.

%% NEW REFERENCES FOR REVOLUTIONARY APPROACH

\bibitem{mccann2020}
R.~J.~McCann,
\newblock Displacement convexity of Boltzmann's entropy characterizes the strong energy condition from general relativity,
\newblock {\em Camb.\ J.\ Math.}, 8 (2020), 609--681.

\bibitem{mondinosuhr2022}
A.~Mondino and S.~Suhr,
\newblock An optimal transport formulation of the Einstein equations of general relativity,
\newblock {\em J.\ Eur.\ Math.\ Soc.}, 25 (2023), 933--994.

\bibitem{cavallettimondino2020}
F.~Cavalletti and A.~Mondino,
\newblock Optimal transport in Lorentzian synthetic spaces, synthetic timelike Ricci curvature lower bounds and applications,
\newblock {\em Camb.\ J.\ Math.}, 12 (2024), 417--534.

\bibitem{sturmvillani2006}
K.-T.~Sturm,
\newblock On the geometry of metric measure spaces I, II,
\newblock {\em Acta Math.}, 196 (2006), 65--131, 133--177.

\bibitem{lottvilla2009}
J.~Lott and C.~Villani,
\newblock Ricci curvature for metric-measure spaces via optimal transport,
\newblock {\em Ann.\ of Math.\ (2)}, 169 (2009), 903--991.

\bibitem{braun2023}
M.~Braun,
\newblock Rényi's entropy on Lorentzian spaces. Timelike curvature-dimension conditions,
\newblock {\em J.\ Math.\ Pures Appl.}, 177 (2023), 46--128.

\bibitem{apsindex1975}
M.~F.~Atiyah, V.~K.~Patodi, and I.~M.~Singer,
\newblock Spectral asymmetry and Riemannian geometry I, II, III,
\newblock {\em Math.\ Proc.\ Cambridge Philos.\ Soc.}, 77 (1975), 43--69; 78 (1975), 405--432; 79 (1976), 71--99.

\bibitem{witten1981}
E.~Witten,
\newblock A new proof of the positive energy theorem,
\newblock {\em Comm.\ Math.\ Phys.}, 80 (1981), 381--402.

\bibitem{parkertataru1982}
T.~Parker and C.~H.~Taubes,
\newblock On Witten's proof of the positive energy theorem,
\newblock {\em Comm.\ Math.\ Phys.}, 84 (1982), 223--238.

\bibitem{gallowayling2017}
G.~J.~Galloway and E.~Ling,
\newblock Some remarks on the $C^0$-(in)extendibility of spacetimes,
\newblock {\em Ann.\ Henri Poincar\'e}, 18 (2017), 3427--3447.

\bibitem{hayward1994}
S.~A.~Hayward,
\newblock Quasilocal gravitational energy,
\newblock {\em Phys.\ Rev.\ D}, 49 (1994), 831--839.

\bibitem{kunzinger2018}
M.~Kunzinger and C.~S\"amann,
\newblock Lorentzian length spaces,
\newblock {\em Ann.\ Global Anal.\ Geom.}, 54 (2018), 399--447.

\bibitem{minguzzi2019}
E.~Minguzzi,
\newblock Causality theory for closed cone structures with applications,
\newblock {\em Rev.\ Math.\ Phys.}, 31 (2019), 1930001.

\end{thebibliography}

