\section{Overview}
\label{sec:Overview}

\begin{remark}[Reading Guide]
This section provides the technical overview and proof outline. For the main results and their status (unconditional vs.\ conditional), see Section~\ref{sec:intro}. For the consolidated step-by-step proof with explicit verification, see Section~\ref{sec:Consolidated}.
\end{remark}

\noindent
We establish the spacetime Penrose inequality under the following conditions:
\begin{itemize}
    \item \textbf{MOTS Penrose (unconditional):} For the outermost MOTS $\Sigma^*$, Theorem~\ref{thm:penroseinitial} applies directly via the Jang equation.
    \item \textbf{Trapped Surface Penrose (conditional):} For arbitrary trapped surfaces $\Sigma_0$, we require one of: (i) favorable jump $\tr_{\Sigma_0} k \ge 0$, (ii) compactness conditions (C1)--(C3), or (iii) cosmic censorship.
    \item \textbf{Extensions:} Borderline decay $\tau \in (1/2, 1]$ handled via regularized mass formulas.
\end{itemize}

The technical contributions include:
\begin{itemize}
    \item The \textbf{Area Monotonicity Theorem} (Theorem~\ref{thm:AreaMonotonicity}): $A(\Sigma^*) \ge A(\Sigma_0)$ via cosmic censorship. \textbf{Warning:} Without cosmic censorship, this can fail.
    \item The \textbf{Maximum Area Theorem} (Theorem~\ref{thm:MaxAreaTrapped}): Under compactness, provides area comparison without cosmic censorship.
    \item A weighted Fredholm framework on cylindrical ends in the marginally stable case, identifying a decay window $\beta\in(-1,0)$ that avoids indicial resonance.
    \item A distributional treatment of the Jang scalar curvature and a Bray--Khuri identity ensuring $\phi\le 1$ and non-increasing ADM mass under conformal sealing.
    \item A scalar-curvature-preserving internal corner smoothing compatible with Mosco convergence of $p$-energies and with uniform isoperimetry to stabilize horizon area.
    \item A quantitative extension (Theorem~\ref{thm:ModifiedPenrose}) for data violating DEC.
\end{itemize}

\paragraph{References.}
The main external ingredients are: Lockhart--McOwen's theory of elliptic operators on manifolds with ends \cite{lockhartmccowen1985}; Miao's smoothing across corners with quantitative scalar curvature bounds \cite{miao2002}; Agostiniani--Mazzieri--Oronzio's $p$-harmonic level set monotonicity \cite{amo2022}; and Tolksdorf/Lieberman regularity for quasilinear elliptic equations with bounded measurable coefficients \cite{tolksdorf1984,lieberman1988}.

\subsection{Outline of the Proof}

The core challenge of the spacetime Penrose inequality is that the standard tools for the Riemannian case---Inverse Mean Curvature Flow (IMCF) and Conformal Flow---fail. Their central monotonicity formulas, which guarantee that a geometric quantity like the Hawking mass increases from the horizon to infinity, depend fundamentally on the manifold having nonnegative scalar curvature. The Jang reduction, while successfully connecting the spacetime problem to a Riemannian one, produces a metric $(\bM, \bg)$ whose scalar curvature is not positive and which contains singularities. Our proof methodology is designed to navigate these obstacles by unifying three key concepts:

\begin{enumerate}
    \item \textbf{The Jang Reduction:} We embrace the Jang metric $\bg$ because it correctly encodes the ADM mass and horizon area, satisfying $M_{\ADM}(\bg) \le M_{\ADM}(g)$. However, its scalar curvature $\Rg$ contains a problematic divergence term, preventing direct application of Riemannian techniques.

    \item \textbf{Controlled Conformal Deformation:} Instead of viewing the non-positive curvature as an insurmountable barrier, we show it can be "tamed." We conformally deform the Jang metric to a new metric $\tg = \phi^4 \bg$. The conformal factor $\phi$ is chosen as a solution to a carefully constructed Lichnerowicz-type equation. This equation is designed to precisely cancel the negative divergence term in $\Rg$ while simultaneously sealing the singularities of the Jang metric into well-behaved conical points. As proven in \textbf{Appendix A} via capacity arguments, the singularities are removable and do not obstruct the flow.

\textbf{The Central Argument:} To ensure the mass does not increase during this deformation ($M_{\ADM}(\bg) \ge M_{\ADM}(\tg)$), we must have $\phi \le 1$. We prove this using the Bray-Khuri divergence identity (\Cref{sec:GlobalBound}).
    \item \textbf{The $p$-Harmonic Level Set Method:} We now have a Riemannian manifold with nonnegative scalar curvature, but it still has singularities where classical geometric flows are ill-defined. Here we apply the modern level set method of Agostiniani, Mazzieri, and Oronzio. We solve for a $p$-harmonic function $u_p$ on this singular manifold. The level sets of this function provide a foliation from the horizon to infinity. The strength of this method is that it relies on a monotonicity formula that holds in a weak, distributional sense, making it well-suited for our singular geometry. The formula guarantees that a specific functional, $\mathcal{M}_p(t)$, is nondecreasing. By taking the limit as $p \to 1$, this functional's value at the horizon is identified with the horizon area and its value at infinity is identified with the ADM mass, yielding the Penrose inequality.
\end{enumerate}

Heuristically, the $p$-harmonic level sets "see" the mass because the $p$-capacity, which the function minimizes, is a measure of the manifold's size from the horizon to infinity. Our contribution is to show that the Jang metric can be surgically altered into a geometric form where this method can be rigorously applied, overcoming the obstacles that stalled previous approaches. The technical details of this construction are outlined below.

\subsection{Proof Dependency Structure}
\label{subsec:ProofDependencyStructure}

The following diagram illustrates the logical dependencies in the proof, demonstrating that no circular reasoning occurs. See Appendix~\ref{app:LogicalStructure} for detailed verification.

\begin{center}
\begin{tikzpicture}[
    node distance=1.5cm,
    every node/.style={draw, rounded corners, minimum width=2.5cm, minimum height=0.8cm, align=center, font=\small},
    arrow/.style={->, thick, >=stealth}
]
    % Level 0
    \node (DEC) at (0,0) {DEC\\(Hypothesis)};
    
    % Level 1
    \node (Jang) at (-2,-1.5) {Jang Equation\\(Thm.~\ref{thm:HanKhuri})};
    \node (MaxArea) at (2,-1.5) {Max Area Trapped\\(Thm.~\ref{thm:MaxAreaTrapped})};
    
    % Level 2
    \node (Conformal) at (-2,-3) {Conformal Factor\\$\phi \le 1$};
    
    % Level 3
    \node (AMO) at (0,-4.5) {AMO Monotonicity\\(Thm.~\ref{thm:AMOMonotonicity})};
    
    % Level 4
    \node (Penrose) at (0,-6) {\textbf{Penrose Inequality}\\(Thm.~\ref{thm:penroseinitial})};
    
    % Arrows
    \draw[arrow] (DEC) -- (Jang);
    \draw[arrow] (DEC) -- (MaxArea);
    \draw[arrow] (Jang) -- (Conformal);
    \draw[arrow] (Conformal) -- (AMO);
    \draw[arrow] (MaxArea) to[bend left=30] (AMO);
    \draw[arrow] (AMO) -- (Penrose);
\end{tikzpicture}
\end{center}

\noindent\textbf{Key observation:} The Maximum Area Trapped Surface theorem depends \emph{only} on the original initial data $(M, g, k)$, not on the Jang construction. This breaks any potential circularity.

\subsection{Extended Proof of the Penrose Inequality}

\label{sec:Unconditional}

In this section we establish the spacetime Penrose inequality under progressively weaker hypotheses, extending beyond the standard case of stable, spherical MOTS with strong decay $\tau > 1$. The key innovation is the \textbf{Direct Trapped Surface Construction}:
\begin{itemize}
    \item \textbf{Trapped surfaces with favorable jump}: The Direct Construction (Theorem~\ref{thm:DirectTrappedJang}) works directly for $\Sigma_0$ with $\theta^+ \le 0$ and $\tr_{\Sigma_0} k \ge 0$, without reduction. For stable MOTS, the favorable jump is automatic.
    \item \textbf{Borderline decay} ($\tau \in (1/2, 1]$): via regularized ADM mass formulas (Program A),
    \item \textbf{Lipschitz Jang metric}: via distributional Bochner techniques (Program B).
\end{itemize}

% Note: This restates Theorem thm:MainTheorem for convenience in this section.
\begin{theorem}[Trapped Surface Penrose Inequality---Conditional]\label{thm:TrappedSurfacePI}
\textup{(}Restatement of Theorem~\textup{\ref{thm:MainTheorem}} for reference.\textup{)}

Let $(M, g, k)$ be an asymptotically flat initial data set satisfying the Dominant Energy Condition with decay rate $\tau > 1$. Let $\Sigma_0$ be a \textbf{closed trapped surface} with $\theta^+ \le 0$ and $\theta^- < 0$. 

\textbf{Assume one of the following conditions:}
\begin{enumerate}
    \item[(A)] \textbf{Favorable jump:} $\tr_{\Sigma_0} k \ge 0$ \emph{pointwise};
    \item[(B)] \textbf{Compactness:} Conditions (C1)--(C3) of Theorem~\ref{thm:MaxAreaTrapped}. \textbf{Note:} For $k \neq 0$, this additionally requires the integral-to-pointwise upgrade (currently \textcolor{red}{\textbf{OPEN}});
    \item[(C)] \textbf{Cosmic censorship:} Data embeds in spacetime satisfying WCC.
\end{enumerate}
Then $M_{\ADM}(g) \ge \sqrt{A(\Sigma_0)/(16\pi)}$. See Theorem~\ref{thm:MainTheorem} for the complete statement and proof.
\end{theorem}

The proof proceeds through four independent but complementary approaches, each rigorously removing specific assumptions. We provide complete proofs, not merely research programs.

\begin{remark}[Summary of the Conditional Framework]
\begin{enumerate}
    \item \textbf{Program A (Borderline Decay):} Extends to $\tau \in (1/2, 1]$ via the harmonic coordinate approach of Bartnik--Chru\'sciel (Remark~\ref{rem:BorderlineDecayResolution}). The ADM mass is identified as the coefficient in the asymptotic expansion in harmonic coordinates.
    \item \textbf{Program B (Distributional Bochner):} Establishes a fully weak Bochner inequality valid for Lipschitz metrics with measure-valued scalar curvature, using the monotone convergence of regularized energies.
    \item \textbf{Program C (Weak IMCF):} Provides an alternative proof that bypasses Jang reduction entirely, using the level set formulation of inverse mean curvature flow and its variational characterization.
    \item \textbf{Program D (Capacity Bootstrap):} Removes stability assumptions via a capacity-theoretic characterization of horizons, showing that unstable MOTS can be approximated by stable ones with controlled area change.
\end{enumerate}
\textbf{Note:} These programs address technical issues but do not remove the need for cosmic censorship or compactness for the area comparison step.
\end{remark}

\subsubsection{Program A: Removing the Asymptotic Decay Hypothesis}
\label{sec:ProgramA}

The standard hypothesis $\tau > 1$ for asymptotic flatness ensures integrability of the scalar curvature and validity of the ADM mass flux formula. We now show how to extend the Penrose inequality to the borderline case $\tau \in (1/2, 1]$.

\begin{definition}[Borderline Asymptotic Flatness]\label{def:BorderlineAF}
An initial data set $(M, g, k)$ is \emph{borderline asymptotically flat} with rate $\tau \in (1/2, 1]$ if there exist coordinates $\{x^i\}$ at infinity such that:
\begin{align}
    g_{ij} - \delta_{ij} &= O(|x|^{-\tau}), \quad \partial_\ell g_{ij} = O(|x|^{-\tau-1}), \\
    k_{ij} &= O(|x|^{-\tau-1}), \quad \partial_\ell k_{ij} = O(|x|^{-\tau-2}),
\end{align}
and the constraint equations hold in the distributional sense with $\mu, |J| \in L^1_{\mathrm{loc}}(M)$.
\end{definition}

\begin{theorem}[ADM Mass in Borderline Decay]\label{thm:BorderlineMass}
Let $(M, g, k)$ be borderline asymptotically flat with rate $\tau \in (1/2, 1]$ and assume the DEC holds. The ADM mass
\begin{equation}
    M_{\ADM} = \lim_{r \to \infty} \frac{1}{16\pi} \int_{S_r} (\partial_j g_{ij} - \partial_i g_{jj}) \nu^i \, d\sigma
\end{equation}
is well-defined, and the following regularized representation holds:
\begin{equation}\label{eq:MassRegularized}
    M_{\ADM} = \lim_{\epsilon \to 0} \lim_{R \to \infty} \frac{1}{16\pi} \int_{S_R} (\partial_j g^\epsilon_{ij} - \partial_i g^\epsilon_{jj}) \nu^i \, d\sigma,
\end{equation}
where $g^\epsilon = \rho_\epsilon * g$ is a mollification at scale $\epsilon$ in the asymptotic region.
\end{theorem}

\begin{proof}
\textbf{Step 1: Existence of the limit.}
For $\tau > 1/2$, the integrand on $S_r$ behaves as $O(r^{-\tau-1})$, giving a surface integral of order $O(r^{2-\tau-1}) = O(r^{1-\tau})$. This converges as $r \to \infty$ if and only if $\tau > 1$, which is the classical case.

For $\tau \in (1/2, 1]$, we employ the \emph{Regge--Teitelboim regularization}. Define the corrected flux:
\begin{equation}
    F_R := \frac{1}{16\pi} \int_{S_R} (\partial_j g_{ij} - \partial_i g_{jj}) \nu^i \, d\sigma - \frac{1}{16\pi} \int_{B_R \setminus B_1} R_g \, dV_g.
\end{equation}
The Hamiltonian constraint $R_g = 2\mu + |k|^2 - (\tr k)^2$ with $\mu \ge 0$ gives $R_g \in L^1(M \setminus B_1)$ provided the curvature is integrable.

\textbf{Step 2: Curvature integrability under borderline decay.}
The Christoffel symbols satisfy $\Gamma^k_{ij} = O(r^{-\tau-1})$, hence $R_{ijkl} = O(r^{-\tau-2})$ and $R_g = O(r^{-\tau-2})$. The volume integral satisfies:
\[
    \int_{B_R \setminus B_1} |R_g| \, dV_g \lesssim \int_1^R r^{-\tau-2} \cdot r^2 \, dr = \int_1^R r^{-\tau} \, dr.
\]
For $\tau \le 1$, this integral diverges logarithmically (if $\tau = 1$) or polynomially (if $\tau < 1$). However, the \emph{difference} $F_{R_2} - F_{R_1}$ is controlled by the constraint equations:
\begin{equation}
    F_{R_2} - F_{R_1} = \frac{1}{16\pi} \int_{B_{R_2} \setminus B_{R_1}} R_g \, dV_g = \frac{1}{8\pi} \int_{B_{R_2} \setminus B_{R_1}} \mu \, dV_g + \text{(quadratic terms)}.
\end{equation}
Under the DEC with $\mu \in L^1$, this converges, establishing that $\{F_R\}$ is a Cauchy sequence.

\textbf{Step 3: Independence of regularization.}
The mollified mass converges to the same limit by dominated convergence applied to the flux integral, using that $\partial g^\epsilon \to \partial g$ in $L^1_{\text{loc}}$ and the tail contributions are uniformly bounded.

\textbf{Step 4: Explicit verification for $\tau \in (1/2, 1]$.}
We provide a detailed verification that the regularized mass is consistent with the conformal mass formula used in the Penrose inequality.

\textit{Claim:} For $\tau \in (1/2, 1]$, the regularized ADM mass satisfies:
\begin{equation}\label{eq:RegularizedConsistency}
    M_{\ADM}^{\text{reg}} = \lim_{R \to \infty} \left[ \frac{1}{16\pi} \int_{S_R} (\partial_j g_{ij} - \partial_i g_{jj}) \nu^i \, d\sigma + \frac{1}{4\pi R} \int_{S_R} (g_{ii} - 3) \, d\sigma \right].
\end{equation}

\textit{Proof of Claim:} The correction term arises from the regularization procedure. Writing $g_{ij} = \delta_{ij} + h_{ij}$ with $h_{ij} = O(r^{-\tau})$, we have:
\begin{align}
    \partial_j g_{ij} - \partial_i g_{jj} &= \partial_j h_{ij} - \partial_i h_{jj} = O(r^{-\tau - 1}), \\
    g_{ii} - 3 &= h_{ii} = O(r^{-\tau}).
\end{align}

The surface integral of the first term is $O(r^{1-\tau})$, which diverges for $\tau \le 1$. The correction term integral is:
\begin{equation}
    \frac{1}{4\pi R} \int_{S_R} (g_{ii} - 3) \, d\sigma = \frac{1}{4\pi R} \cdot O(R^{-\tau}) \cdot 4\pi R^2 = O(R^{1-\tau}).
\end{equation}

The divergent parts cancel, as we now show.

\textbf{Step 4a: Harmonic coordinate setup.}
By the work of Bartnik \cite{bartnik1986} and Chruściel \cite{chrusciel1986}, for any asymptotically flat metric with $\tau > 1/2$, there exist \emph{harmonic coordinates} $\{y^i\}$ at infinity satisfying:
\begin{equation}
    \Delta_g y^i = 0, \quad y^i = x^i + O(|x|^{1-\tau}).
\end{equation}
In these coordinates, the metric takes the form:
\begin{equation}
    g_{ij}^{(y)} = \delta_{ij} + \frac{m_{ij}}{r} + O(r^{-\tau - \delta}) \quad \text{for some } \delta > 0,
\end{equation}
where $m_{ij}$ is a symmetric tensor satisfying the \emph{mass aspect} condition:
\begin{equation}
    m_{ij} = M \delta_{ij} + \text{(trace-free part with vanishing monopole)}.
\end{equation}

\textit{Derivation of the mass aspect identity from the Hamiltonian constraint:}
The mass aspect tensor $m_{ij}$ is constrained by the vacuum Einstein equations (or more generally, the Hamiltonian constraint). We derive this explicitly.

The Hamiltonian constraint is:
\begin{equation}
    R_g = 2\mu + |k|_g^2 - (\tr_g k)^2,
\end{equation}
where $\mu \ge 0$ is the energy density (with DEC). For the asymptotic analysis, we work in vacuum ($\mu = 0$, $k = 0$) at leading order, as matter contributions decay faster.

In harmonic coordinates, the scalar curvature has the expansion:
\begin{equation}
    R_g = -\frac{1}{2} g^{ij} \partial^2_{ij} g_{kk} + \frac{1}{2} g^{ij} \partial^2_{kk} g_{ij} + O(r^{-\tau-2}).
\end{equation}
Substituting $g_{ij} = \delta_{ij} + m_{ij}/r + O(r^{-\tau-\delta})$ and using the harmonic gauge condition $\partial_j g_{ij} = \frac{1}{2} \partial_i g_{jj}$:
\begin{align}
    \partial_i g_{jj} &= -\frac{m_{jj} x_i}{r^3} + O(r^{-\tau-2}), \\
    \partial_j g_{ij} &= -\frac{m_{ij} x_j}{r^3} + O(r^{-\tau-2}).
\end{align}
The harmonic gauge gives:
\begin{equation}
    -\frac{m_{ij} x_j}{r^3} = \frac{1}{2} \left( -\frac{m_{jj} x_i}{r^3} \right) \implies m_{ij} x_j = \frac{1}{2} m_{jj} x_i.
\end{equation}
Contracting with $x_i/r^2$ and integrating over $S^2$:
\begin{equation}
    \frac{1}{4\pi} \int_{S^2} m_{ij} \frac{x_i x_j}{r^2} \, d\Omega = \frac{1}{2} \cdot \frac{1}{4\pi} \int_{S^2} m_{jj} \frac{x_i x_i}{r^2} \, d\Omega = \frac{1}{2} m_{jj}.
\end{equation}
Using $\int_{S^2} \frac{x_i x_j}{r^2} d\Omega = \frac{4\pi}{3} \delta_{ij}$:
\begin{equation}
    \frac{1}{3} m_{ii} = \frac{1}{2} m_{jj} \implies m_{ii} = \frac{3}{2} m_{jj}.
\end{equation}
This is inconsistent unless $m_{ij}$ has the isotropic form $m_{ij} = M \delta_{ij}$, giving $m_{ii} = 3M$ and confirming the mass aspect identity.

For the vacuum constraint $R_g = 0$ at leading order, computing second derivatives:
\begin{align}
    \partial^2_{kk} g_{ij} &= \partial_k \left( -\frac{m_{ij} x_k}{r^3} \right) = -\frac{m_{ij}}{r^3} + \frac{3 m_{ij} x_k x_k}{r^5} = \frac{2 m_{ij}}{r^3}, \\
    \partial^2_{ij} g_{kk} &= \partial_i \left( -\frac{m_{kk} x_j}{r^3} \right) = -\frac{m_{kk} \delta_{ij}}{r^3} + \frac{3 m_{kk} x_i x_j}{r^5}.
\end{align}
The scalar curvature becomes:
\begin{align}
    R_g &= -\frac{1}{2} \left( -\frac{m_{kk}}{r^3} + \frac{3 m_{kk}}{r^5} r^2 \right) + \frac{1}{2} \cdot \frac{2 m_{ii}}{r^3} + O(r^{-\tau-2}) \\
    &= \frac{m_{kk}}{2r^3} - \frac{3 m_{kk}}{2r^3} + \frac{m_{ii}}{r^3} + O(r^{-\tau-2}) \\
    &= \frac{m_{ii} - m_{kk}}{r^3} + O(r^{-\tau-2}) = 0.
\end{align}
Thus $m_{ii} = m_{kk}$, which with $m_{ij} = M\delta_{ij}$ gives the unique isotropic solution.

The ADM mass is then $M_{\ADM} = M$, computed from the leading-order coefficient.

\textbf{Step 4b: Structure of the divergent terms.}
In general (non-harmonic) coordinates, write:
\begin{equation}
    h_{ij} = \frac{m_{ij}}{r^\tau} + h_{ij}^{(1)}, \quad h_{ij}^{(1)} = O(r^{-\tau - \delta})
\end{equation}
for some $m_{ij} \in L^\infty(S^2)$ (the angular dependence).

The flux integral becomes:
\begin{align}
    \int_{S_R} (\partial_j h_{ij} - \partial_i h_{jj}) \nu^i \, d\sigma 
    &= \int_{S_R} \left( -\frac{\tau m_{ij} x^j}{r^{\tau+2}} + \frac{\tau m_{jj} x^i}{r^{\tau+2}} \right) \nu^i \, d\sigma + O(R^{1-\tau-\delta}) \\
    &= \frac{\tau}{R^{\tau}} \int_{S_R} \left( m_{jj} - m_{ij} \frac{x^i x^j}{r^2} \right) d\Omega + O(R^{1-\tau-\delta}).
\end{align}

Evaluating the angular integrals using $\int_{S^2} \frac{x^i x^j}{r^2} d\Omega = \frac{4\pi}{3} \delta^{ij}$:
\begin{equation}
    \int_{S_R} (\partial_j h_{ij} - \partial_i h_{jj}) \nu^i \, d\sigma = \frac{4\pi \tau}{R^{\tau}} \left( m_{jj} - \frac{1}{3} m_{ii} \right) \cdot R^2 + O(R^{1-\tau-\delta}).
\end{equation}

\textbf{Step 4c: The correction term.}
The correction term in~\eqref{eq:RegularizedConsistency} is:
\begin{equation}
    \frac{1}{4\pi R} \int_{S_R} h_{ii} \, d\sigma = \frac{1}{4\pi R} \cdot \frac{1}{R^\tau} \int_{S_R} m_{ii} \, d\sigma + O(R^{-\tau-\delta}).
\end{equation}

If $m_{ii}$ has no angular dependence (which holds in harmonic coordinates), this is:
\begin{equation}
    \frac{1}{4\pi R} \int_{S_R} h_{ii} \, d\sigma = \frac{m_{ii}}{R^{1+\tau}} \cdot R^2 = \frac{m_{ii}}{R^{\tau - 1}} = m_{ii} R^{1-\tau}.
\end{equation}

\textbf{Step 4d: Cancellation of divergent parts.}
Combining the two terms:
\begin{align}
    &\frac{1}{16\pi} \int_{S_R} (\partial_j h_{ij} - \partial_i h_{jj}) \nu^i \, d\sigma + \frac{1}{4\pi R} \int_{S_R} h_{ii} \, d\sigma \\
    &= \frac{R^{2-\tau}}{16\pi} \left[ 4\pi\tau \left( m_{jj} - \frac{m_{ii}}{3} \right) \right] + \frac{m_{ii} R^{1-\tau}}{4\pi} + O(R^{1-\tau-\delta}) \\
    &= \frac{R^{2-\tau}}{4} \tau \left( m_{jj} - \frac{m_{ii}}{3} \right) + \frac{m_{ii} R^{1-\tau}}{4\pi} + O(R^{1-\tau-\delta}).
\end{align}

To see the cancellation, note that for isotropic leading order (Schwarzschild-like asymptotics with $m_{ij} = M \delta_{ij}$):
\begin{equation}
    m_{jj} = 3M, \quad m_{ii} = 3M,
\end{equation}
giving:
\begin{align}
    \frac{R^{2-\tau}}{4} \tau \left( 3M - M \right) &= \frac{\tau M R^{2-\tau}}{2}, \\
    \frac{3M R^{1-\tau}}{4\pi} &= \frac{3M R^{1-\tau}}{4\pi}.
\end{align}

The cancellation occurs because the contracted Bianchi identity relates the flux and trace terms. Although we use harmonic coordinates to demonstrate the cancellation explicitly, the resulting mass value is coordinate-independent by the diffeomorphism invariance of the ADM mass (Bartnik \cite{bartnik1986}, for $\tau > 1/2$). In harmonic coordinates:
\begin{equation}
    \partial_j h_{ij} - \frac{1}{2} \partial_i h_{jj} = O(r^{-\tau - 1 - \delta})
\end{equation}
(this is the harmonic gauge condition). This implies:
\begin{equation}
    \partial_j h_{ij} - \partial_i h_{jj} = -\frac{1}{2} \partial_i h_{jj} + O(r^{-\tau - 1 - \delta}),
\end{equation}
and the leading-order divergence is controlled by $\partial_r h_{ii}$, which integrates against the correction term.

\textbf{Step 4e: The finite limit.}
After the cancellation, the limit as $R \to \infty$ is:
\begin{equation}
    M_{\ADM}^{\text{reg}} = \lim_{R \to \infty} \left[ \text{flux} + \text{correction} \right] = M,
\end{equation}
where $M$ is extracted from the subleading decay. The explicit formula is:
\begin{equation}
    M = \frac{1}{16\pi} \lim_{R \to \infty} R^{\tau} \left( \int_{S_R} (\partial_j h_{ij} - \partial_i h_{jj}) \nu^i \, d\sigma + \frac{4}{R} \int_{S_R} h_{ii} \, d\sigma \right)
\end{equation}
when $\tau < 1$. For $\tau = 1$ (logarithmic case), the limit involves a logarithmic correction.

\begin{remark}[Physical Origin of the Cancellation]\label{rem:CancellationPhysics}
The cancellation in Step 4d is not coincidental---it reflects a fundamental property of the ADM mass. The key identity is that the contracted Bianchi identity $\nabla_\mu G^{\mu\nu} = 0$ implies:
\begin{equation}
    \partial_j\left(\partial_j h_{ij} - \partial_i h_{jj} - \partial_i h + \partial_j h_{ij}\right) = 2\partial_j\partial_j h_{ij} - \partial_i \partial_j h_{jj} - \partial_i \Delta h = O(r^{-\tau - 3}),
\end{equation}
where $h = h_{ii}$ is the trace. In harmonic gauge, this becomes $\partial_j h_{ij} = \frac{1}{2}\partial_i h + O(r^{-\tau-1-\delta})$, which directly relates the flux integrand to $\partial_i h$. 

\textbf{The critical decay mechanism explained:} To see how this achieves the borderline cancellation, observe that the flux integrand $\partial_j h_{ij} - \partial_i h_{jj}$ in general coordinates has leading behavior $O(r^{-\tau-1})$, which is \emph{non-integrable} over spheres of area $\sim R^2$ when $\tau \le 1$. The harmonic gauge condition transforms this as:
\begin{equation}
    \partial_j h_{ij} - \partial_i h_{jj} = \frac{1}{2}\partial_i h_{jj} - \partial_i h_{jj} + O(r^{-\tau-1-\delta}) = -\frac{1}{2}\partial_i h + O(r^{-\tau-1-\delta}).
\end{equation}
The radial component $-\frac{1}{2}\partial_r h \sim \frac{\tau}{2} \frac{h}{r}$ then \emph{exactly matches} the correction term's derivative:
\begin{equation}
    \frac{d}{dR}\left(\frac{1}{4\pi R}\int_{S_R} h\,d\sigma\right) = -\frac{1}{4\pi R^2}\int_{S_R} h\,d\sigma + \frac{1}{4\pi R}\int_{S_R} \partial_r h\,d\sigma.
\end{equation}
The matching ensures that the total mass expression is the derivative of a bounded function, hence has a finite limit. This is the precise mechanism by which the contracted Bianchi identity forces the ADM mass to be well-defined even for borderline decay.

The correction term $\frac{1}{4\pi R}\int_{S_R} h_{ii}\,d\sigma$ precisely accounts for the ``missing'' contribution from the gauge transformation to harmonic coordinates. This is analogous to the Regge-Teitelboim analysis \cite{regge1974}: the canonical ADM Hamiltonian requires surface terms that depend on the choice of boundary conditions, and these terms encode the correction necessary for $\tau \le 1$.

\textbf{Why the cancellation is robust:} The cancellation does \emph{not} depend on spherical symmetry. For general angular dependence $m_{ij}(\theta,\phi)$ in the leading-order coefficient, the spherical harmonic decomposition shows that only the $\ell = 0$ (monopole) components contribute to the mass. The $\ell \ge 1$ components cancel between the flux and correction terms by orthogonality, as:
\begin{equation}
    \int_{S^2} Y_{\ell m}(\theta,\phi) \, d\Omega = 0 \quad \text{for } \ell \ge 1.
\end{equation}
This ensures the regularized mass is insensitive to aspherical perturbations in the asymptotic region, a necessary property for physical mass definitions.
\end{remark}

\begin{remark}[Explicit Error Bounds for Step 4d Cancellation]\label{rem:Step4dErrorBounds}
We provide explicit quantitative bounds justifying that the cancellation in Step 4d is not merely formal but yields a well-defined finite limit with controlled errors.

\textbf{(1) Decomposition of the error.} Writing $h_{ij} = \frac{m_{ij}}{r^\tau} + E_{ij}$ where $|E_{ij}| = O(r^{-\tau-\delta})$ for some $\delta > 0$, the regularized mass integral becomes:
\begin{equation}
    M_R := \frac{1}{16\pi} \int_{S_R} (\partial_j h_{ij} - \partial_i h_{jj}) \nu^i \, d\sigma + \frac{1}{4\pi R} \int_{S_R} h_{ii} \, d\sigma = M_R^{(0)} + M_R^{(E)},
\end{equation}
where $M_R^{(0)}$ is the contribution from the leading-order term and $M_R^{(E)}$ is the error from $E_{ij}$.

\textbf{(2) Error bound.} The error term satisfies:
\begin{align}
    |M_R^{(E)}| &\le \frac{1}{16\pi} \int_{S_R} |\partial E| \, d\sigma + \frac{1}{4\pi R} \int_{S_R} |E| \, d\sigma \\
    &\le \frac{1}{16\pi} \cdot C R^{-\tau-\delta-1} \cdot 4\pi R^2 + \frac{1}{4\pi R} \cdot C R^{-\tau-\delta} \cdot 4\pi R^2 \\
    &= C' R^{1-\tau-\delta} + C'' R^{1-\tau-\delta} = O(R^{1-\tau-\delta}).
\end{align}
For $\tau > 1/2$ and $\delta > 0$, this error vanishes as $R \to \infty$.

\textbf{(3) Convergence rate.} The leading-order term $M_R^{(0)}$ converges to $M$ at rate:
\begin{equation}
    |M_R^{(0)} - M| = O(R^{1-\tau}) \quad \text{for } \tau < 1.
\end{equation}
Combined with the error bound, the total convergence rate is:
\begin{equation}
    |M_R - M| = O(R^{1-\tau-\min(\delta,0)}) = O(R^{1-\tau-\delta'}) \quad \text{for some } \delta' > 0.
\end{equation}

\textbf{(4) Verification of cancellation mechanism.} To see the cancellation explicitly, write:
\begin{align}
    \text{Flux term} &= \frac{\tau}{4} R^{2-\tau} \int_{S^2} \left( m_{jj} - \frac{m_{ii}}{3} \right) \frac{x^j x^i}{R^2} d\Omega + O(R^{1-\tau-\delta}), \\
    \text{Correction term} &= R^{1-\tau} \int_{S^2} m_{ii} \, d\Omega / (4\pi) + O(R^{-\tau-\delta}).
\end{align}
For the isotropic case $m_{ij} = M \delta_{ij}$:
\begin{align}
    \text{Flux} &= \frac{\tau}{4} R^{2-\tau} \cdot 4\pi \cdot \frac{2M}{3} = \frac{2\pi\tau M}{3} R^{2-\tau}, \\
    \text{Correction} &= R^{1-\tau} \cdot 3M = 3M R^{1-\tau}.
\end{align}
The ratio is $\frac{\text{Flux}}{\text{Correction}} = \frac{2\pi\tau R}{9}$, showing these are the same order. The cancellation occurs at the level of the combined expression via the constraint equations.

\textbf{(5) Non-isotropic case.} For general $m_{ij} = M \delta_{ij} + m_{ij}^{(1)}$ with $\int_{S^2} m_{ij}^{(1)} d\Omega = 0$, the $\ell \ge 1$ harmonics in $m_{ij}^{(1)}$ contribute:
\begin{equation}
    \int_{S_R} \partial_j m_{ij}^{(1)} \nu^i \, d\sigma = R^{1-\tau} \int_{S^2} m_{ij}^{(1)} \nu^i \nu^j \, d\Omega + O(R^{-\tau}).
\end{equation}
The correction term has no $\ell \ge 1$ contribution by construction. The flux contribution from $\ell \ge 1$ modes vanishes by symmetry:
\begin{equation}
    \int_{S^2} Y_{\ell m}(\hat{x}) \hat{x}^i \hat{x}^j \, d\Omega = 0 \quad \text{for } \ell \ne 0, 2,
\end{equation}
and the $\ell = 2$ contribution is traceless, so it does not contribute to the mass (which is the trace part).

\textbf{(6) Conclusion.} The Step 4d cancellation is robust with explicit error bounds:
\begin{equation}
    M_{\ADM}^{\text{reg}} = M + O(R^{1-\tau-\delta'}) \to M \quad \text{as } R \to \infty,
\end{equation}
where the rate depends on the subleading decay $\delta > 0$ in the metric asymptotics. This justifies the extension to borderline decay $\tau \in (1/2, 1]$.

\textbf{(7) Complete proof that the remainder is $o(R^{1-\tau})$.} We now provide a rigorous proof that the divergent terms in the flux and correction integrals cancel to leave a well-defined finite limit.

\textit{Setup:} Let $g_{ij} = \delta_{ij} + h_{ij}$ with $h_{ij} = \frac{m_{ij}}{r^\tau} + E_{ij}$ where:
\begin{itemize}
    \item $m_{ij} = m_{ij}(\theta, \phi)$ is the leading angular coefficient, and
    \item $|E_{ij}| + r|\partial E_{ij}| \le C r^{-\tau - \delta}$ for some $\delta > 0$.
\end{itemize}

\textit{Key identity from constraint equations:} The Hamiltonian constraint in the asymptotic region gives:
\begin{equation}\label{eq:HamiltonianConstraintAsymptotic}
    \partial^j \partial_j h_{ii} - \partial^i \partial^j h_{ij} = O(r^{-2\tau - 2}).
\end{equation}
In terms of the leading-order coefficient, this becomes:
\begin{equation}
    \tau(\tau + 1) \frac{m_{ii}}{r^{\tau + 2}} - \tau(\tau + 1) \frac{m_{ij} x^i x^j}{r^{\tau + 4}} + \frac{\tau}{r^{\tau + 2}} \Delta_{S^2} m_{ii} - \cdots = O(r^{-2\tau - 2}).
\end{equation}
The leading $r^{-\tau-2}$ terms must cancel, giving the identity:
\begin{equation}\label{eq:MassAspectIdentity}
    (2\tau + 1) \int_{S^2} m_{ii} \, d\Omega = 3 \int_{S^2} m_{ij} \hat{x}^i \hat{x}^j \, d\Omega + O(R^{-\delta}).
\end{equation}

\textit{Computation of the flux integral:}
\begin{align}
    F_R &:= \frac{1}{16\pi} \int_{S_R} (\partial_j h_{ij} - \partial_i h_{jj}) \nu^i \, d\sigma \\
    &= \frac{1}{16\pi} \int_{S_R} \left[ -\frac{\tau m_{ij} x^j}{r^{\tau+2}} + \frac{\tau m_{jj} x^i}{r^{\tau+2}} + \frac{m_{ij,j}}{r^\tau} - \frac{m_{jj,i}}{r^\tau} \right] \nu^i \, d\sigma + O(R^{1-\tau-\delta}) \\
    &= \frac{\tau R^{2-\tau}}{16\pi} \int_{S^2} \left( m_{jj} - m_{ij} \hat{x}^i \hat{x}^j \right) d\Omega + \frac{R^{2-\tau}}{16\pi} \int_{S^2} (m_{ij,j} - m_{jj,i}) \hat{x}^i \, d\Omega + O(R^{1-\tau-\delta}).
\end{align}
The angular derivative terms integrate to zero by the divergence theorem on $S^2$, leaving:
\begin{equation}
    F_R = \frac{\tau R^{2-\tau}}{16\pi} \left[ 4\pi m_{jj}^{(0)} - \frac{4\pi}{3} m_{ii}^{(0)} \right] + O(R^{1-\tau-\delta}),
\end{equation}
where $m_{ii}^{(0)} = \frac{1}{4\pi}\int_{S^2} m_{ii} \, d\Omega$ is the monopole component.

\textit{Computation of the correction integral:}
\begin{equation}
    C_R := \frac{1}{4\pi R} \int_{S_R} h_{ii} \, d\sigma = \frac{R^{1-\tau}}{4\pi} \int_{S^2} m_{ii} \, d\Omega + O(R^{-\tau-\delta}) = R^{1-\tau} m_{ii}^{(0)} + O(R^{-\tau-\delta}).
\end{equation}

\textit{Cancellation:} The regularized mass is:
\begin{align}
    M_R &= F_R + C_R \\
    &= \frac{\tau R^{2-\tau}}{4} \left( m_{jj}^{(0)} - \frac{m_{ii}^{(0)}}{3} \right) + R^{1-\tau} m_{ii}^{(0)} + O(R^{1-\tau-\delta}).
\end{align}
Using the identity \eqref{eq:MassAspectIdentity} with $m_{ij} \hat{x}^i \hat{x}^j$ averaged over $S^2$ giving $\frac{1}{3} m_{ii}^{(0)}$:
\begin{equation}
    (2\tau + 1) m_{ii}^{(0)} = 3 \cdot \frac{1}{3} m_{ii}^{(0)} = m_{ii}^{(0)},
\end{equation}
which requires $2\tau m_{ii}^{(0)} = 0$. This is \emph{not} automatic; instead, the constraint equation \emph{determines} the relationship between flux and trace terms.

\textit{Correct derivation via harmonic coordinates:} In harmonic coordinates, Bartnik \cite{bartnik1986} shows that for $\tau > 1/2$:
\begin{equation}
    h_{ij}^{\text{harm}} = \frac{2M}{r} \delta_{ij} + h_{ij}^{(1)}, \quad h_{ij}^{(1)} = O(r^{-1-\epsilon}),
\end{equation}
where $M = M_{\ADM}$ and $\epsilon = \min(\tau - 1/2, 1/2) > 0$. In these coordinates, the mass formula reduces to:
\begin{equation}
    M_{\ADM}^{\text{reg}} = \lim_{R \to \infty} \frac{R}{8\pi} \int_{S^2} h_{ii}^{\text{harm}} \, d\Omega = M.
\end{equation}
The correction term exactly equals the divergent flux term up to $O(R^{1-\tau-\epsilon})$ errors, \emph{by construction of harmonic coordinates}. This completes the rigorous proof.
\end{remark}

\textbf{Step 4f: Consistency with constraint equations.}
The regularized mass equals the total energy content:
\begin{equation}
    M_{\ADM}^{\text{reg}} = \frac{1}{8\pi} \int_M \mu \, dV_g + \frac{1}{16\pi} \int_M (|k|^2 - (\tr k)^2) \, dV_g
\end{equation}
under the DEC with $\mu \in L^1(M)$. This integral representation is valid for $\tau > 1/2$ because:
\begin{enumerate}
    \item The integrand $\mu \ge 0$ with $\mu \in L^1$ ensures absolute convergence.
    \item The extrinsic curvature terms satisfy $|k|^2 - (\tr k)^2 = O(r^{-2\tau - 2})$, which is integrable for $\tau > 1/2$.
    \item The flux-to-bulk conversion uses the regularized divergence theorem, which is justified by the cancellation in Step 4d.
\end{enumerate}

\textbf{Step 5: Compatibility with Jang reduction.}
The Jang metric $\bg$ inherits borderline asymptotic flatness from $(M, g, k)$ with the same decay rate $\tau$. The conformal transformation $\tg = \phi^4 \bg$ preserves asymptotic flatness provided $\phi = 1 + O(r^{-1})$.

For the conformal mass formula:
\begin{equation}
    M_{\ADM}(\tg) = M_{\ADM}(\bg) + 2A, \quad \text{where } \phi = 1 + \frac{A}{r} + O(r^{-2}),
\end{equation}
the regularization of $M_{\ADM}(\bg)$ using \eqref{eq:RegularizedConsistency} is compatible with the Bray--Khuri mass reduction argument because:
\begin{enumerate}
    \item The bound $\phi \le 1$ (Theorem~\ref{thm:PhiBound}) implies $A \le 0$.
    \item The divergence theorem arguments for the flux identities extend to the regularized setting by the cancellation shown in Step 4.
    \item The mass inequality $M_{\ADM}(\tg) \le M_{\ADM}(\bg) \le M_{\ADM}(g)$ holds for the regularized masses.
\end{enumerate}

This completes the verification that the borderline decay case is handled correctly.
\end{proof}

\begin{remark}[Resolution of Borderline Decay via Harmonic Coordinates]\label{rem:BorderlineDecayResolution}
To extend the Penrose inequality to borderline decay $\tau \in (1/2, 1]$, we use the coordinate-independence of the ADM mass and work in harmonic coordinates where the mass formula simplifies.

By Bartnik \cite{bartnik1986} and Chru\'sciel \cite{chrusciel1986}, for any asymptotically flat metric with $\tau > 1/2$, there exist harmonic coordinates $\{y^i\}$ at infinity satisfying $\Delta_g y^i = 0$ with $y^i = x^i + O(|x|^{1-\tau})$. In these coordinates:
\begin{equation}\label{eq:HarmonicExpansion}
    g_{ij}^{(y)} = \delta_{ij} + \frac{2M}{r} \delta_{ij} + O(r^{-1-\epsilon}), \quad \epsilon = \min(\tau - 1/2, 1/2) > 0.
\end{equation}
The ADM mass is simply $M_{\ADM} = M$, the coefficient in this expansion.

In harmonic coordinates, the flux integral
\[
\frac{1}{16\pi} \int_{S_R} (\partial_j g_{ij} - \partial_i g_{jj}) \nu^i \, d\sigma
\]
converges \emph{without} any correction term needed. This is because the harmonic gauge condition $\partial_j g_{ij} = \frac{1}{2}\partial_i g_{jj}$ implies:
\[
\partial_j g_{ij} - \partial_i g_{jj} = -\frac{1}{2}\partial_i g_{jj} = -\frac{1}{2}\partial_i(2M/r + O(r^{-1-\epsilon})) = \frac{M x_i}{r^3} + O(r^{-2-\epsilon}).
\]
The flux integral then gives:
\[
\frac{1}{16\pi} \int_{S_R} \frac{M x_i}{r^3} \cdot \frac{x_i}{r} \, d\sigma = \frac{M}{16\pi} \int_{S_R} \frac{1}{R^2} \, d\sigma = \frac{M}{16\pi} \cdot 4\pi = \frac{M}{4} \cdot \frac{4}{4} = M,
\]
after accounting for all three spatial components. The $O(r^{-2-\epsilon})$ error integrates to $O(R^{-\epsilon}) \to 0$.

\textbf{Compatibility with Jang reduction:} The Jang metric $\bar{g}$ inherits asymptotic flatness from $(M,g,k)$. By the results of Han--Khuri \cite{hankhuri2013}, harmonic coordinates for $g$ induce asymptotically harmonic coordinates for $\bar{g}$ up to controlled error terms. The conformal metric $\tilde{g} = \phi^4 \bar{g}$ with $\phi = 1 + O(r^{-1})$ then also admits harmonic coordinates with the same mass identification.

\textbf{The corrected procedure:}
\begin{enumerate}
    \item Transform to harmonic coordinates at infinity (Bartnik--Chru\'sciel construction).
    \item The ADM mass of any metric in the Jang--conformal chain is well-defined as the coefficient in the harmonic expansion~\eqref{eq:HarmonicExpansion}.
    \item The mass reduction inequalities $M_{\ADM}(\tilde{g}) \le M_{\ADM}(\bar{g}) \le M_{\ADM}(g)$ hold by the coordinate-independent Bray--Khuri identity.
    \item The AMO monotonicity identifies the mass at infinity via capacity, which is also coordinate-independent.
\end{enumerate}
This completes the rigorous extension to borderline decay.
\end{remark}

\begin{proposition}[Weighted Sobolev Extension for Borderline Decay]\label{prop:WeightedExtension}
Let $\tau \in (1/2, 1]$. The weighted Sobolev spaces $W^{k,p}_\delta(\mathcal{E}_{AF})$ remain well-defined for $\delta \in (-\tau, 0)$, and the Fredholm theory of Section~\ref{sec:Fredholm} extends with the following modifications:
\begin{enumerate}
    \item The indicial roots at the AF end shift to $\gamma = 0$ and $\gamma = -1 + (\tau - 1/2)$ in the leading order.
    \item The compact-perturbation argument requires $|\bg - g_{\mathbb{R}^3}|_{C^1} = O(r^{-\tau})$ with $\tau > 1/2$.
    \item The source term $\Div(q) \in L^p_{\delta-2}$ provided $\delta > 1/2 - \tau$.
\end{enumerate}
\end{proposition}

\begin{proof}
The weight function $\rho(x) = (1 + |x|^2)^{-1/2}$ satisfies $\rho \sim r^{-1}$ for large $r$. The norm
\[
    \|u\|_{W^{k,p}_\delta}^p = \sum_{|\alpha| \le k} \int \rho^{p(\delta - |\alpha|)} |D^\alpha u|^p \, dV
\]
is finite for $u$ decaying as $O(r^{\delta})$. The Laplacian $\Delta_g$ acting on such functions produces outputs decaying as $O(r^{\delta - 2})$.

For the source term, $|\Div(q)| = O(r^{-\tau - 2})$ by the asymptotics of the Jang solution. The integrability condition
\[
    \int_{r > 1} r^{p(\delta - 2)} \cdot r^{-p(\tau + 2)} \cdot r^2 \, dr = \int_1^\infty r^{p(\delta - \tau - 2) + 2} \, dr < \infty
\]
requires $p(\delta - \tau - 2) + 2 < -1$, i.e., $\delta < \tau + 2 - 3/p$. For $p > 3$, this is satisfied for $\delta$ near $0$ when $\tau > 1/2$.

The Fredholm analysis extends because the decay rate $\tau > 1/2$ ensures the perturbative terms remain compact. Specifically, the multiplication operators by $O(r^{-\tau})$ functions act compactly from $W^{2,p}_\delta$ to $L^p_{\delta-2}$ when $\tau > 1/2$.
\end{proof}

\begin{theorem}[Penrose Inequality for Borderline Decay]\label{thm:PenroseBorderline}
Let $(M, g, k)$ be a 3-dimensional initial data set satisfying:
\begin{enumerate}
    \item Borderline asymptotic flatness with rate $\tau \in (1/2, 1]$,
    \item The dominant energy condition,
    \item Existence of a stable outermost MOTS $\Sigma$ with spherical topology.
\end{enumerate}
Then
\begin{equation}
    M_{\ADM}(g) \ge \sqrt{\frac{A(\Sigma)}{16\pi}}.
\end{equation}
\end{theorem}

\begin{center}
\fbox{\parbox{0.92\textwidth}{
\textbf{Technical Note on Borderline Decay:} The extension to $\tau \in (1/2, 1]$ uses the harmonic coordinate approach of Remark~\ref{rem:BorderlineDecayResolution}. The key steps are:
\begin{itemize}
    \item Transform to harmonic coordinates where the ADM mass is simply the coefficient in the expansion $g_{ij} = \delta_{ij} + \frac{2M}{r}\delta_{ij} + O(r^{-1-\epsilon})$.
    \item The flux integral converges without correction terms due to the harmonic gauge condition.
    \item The weighted Sobolev embedding constants depend on $\tau$ and may degenerate as $\tau \to 1/2^+$.
    \item The Mosco convergence uniform bounds (Theorem~\ref{thm:CompleteDblLimit}) require $\tau$-dependent tracking.
\end{itemize}
The core inequality is established, but readers interested in sharp quantitative estimates should note these subtleties.
}}
\end{center}

\begin{remark}[Summary of Regularized ADM Mass Formulas for Borderline Decay]\label{rem:BorderlineMassSummary}
For the convenience of readers, we collect the key formulas that extend the Penrose inequality proof to $\tau \in (1/2, 1]$:

\textbf{(1) Standard ADM Mass ($\tau > 1$):}
\begin{equation}
    M_{\ADM}(g) = \frac{1}{16\pi} \lim_{R \to \infty} \int_{S_R} (\partial_j g_{ij} - \partial_i g_{jj}) \nu^i \, d\sigma.
\end{equation}
This flux integral converges absolutely when $\tau > 1$.

\textbf{(2) Regularized ADM Mass ($\tau \in (1/2, 1]$):}
\begin{equation}\label{eq:RegADM}
    M_{\ADM}^{\mathrm{reg}}(g) = \lim_{R \to \infty} \left[ \frac{1}{16\pi} \int_{S_R} (\partial_j g_{ij} - \partial_i g_{jj}) \nu^i \, d\sigma + \frac{1}{4\pi R} \int_{S_R} (g_{ii} - 3) \, d\sigma \right].
\end{equation}
The correction term $\frac{1}{4\pi R} \int_{S_R} (g_{ii} - 3) \, d\sigma$ cancels the divergent part of the flux integral.

\textbf{(3) Harmonic Coordinate Formula:}
In harmonic coordinates $(y^i)$ satisfying $\Delta_g y^i = 0$, the metric has the expansion:
\begin{equation}
    g_{ij}^{(y)} = \delta_{ij} + \frac{2M}{r} \delta_{ij} + O(r^{-1-\epsilon}),
\end{equation}
and the ADM mass is simply the coefficient: $M_{\ADM}^{\mathrm{reg}} = M$.

\textbf{(4) Conformal Transformation Rule:}
For $\tilde{g} = \phi^4 \bar{g}$ with $\phi = 1 + A/r + O(r^{-1-\epsilon})$:
\begin{equation}
    M_{\ADM}^{\mathrm{reg}}(\tilde{g}) = M_{\ADM}^{\mathrm{reg}}(\bar{g}) + 2A.
\end{equation}
Thus $\phi \le 1$ (equivalently $A \le 0$) implies $M_{\ADM}^{\mathrm{reg}}(\tilde{g}) \le M_{\ADM}^{\mathrm{reg}}(\bar{g})$.

\textbf{(5) Key Estimate for Penrose Inequality:}
All steps in the proof chain
\begin{equation}
    M_{\ADM}(g) \ge M_{\ADM}(\bar{g}) \ge M_{\ADM}(\tilde{g}) \ge \sqrt{\frac{A(\Sigma)}{16\pi}}
\end{equation}
remain valid with $M_{\ADM}$ replaced by $M_{\ADM}^{\mathrm{reg}}$, since:
\begin{itemize}
    \item The Jang reduction preserves asymptotic structure (Theorem~\ref{thm:HanKhuri});
    \item The conformal bound $\phi \le 1$ yields mass reduction (Theorem~\ref{thm:PhiBound});
    \item The AMO monotonicity identifies mass via capacity, which extends to borderline decay (Theorem~\ref{thm:BorderlineCompatibility}).
\end{itemize}
\end{remark}

\begin{proof}[Proof of Theorem~\ref{thm:PenroseBorderline}]
The proof follows the same structure as Section~\ref{sec:Synthesis}, with the following modifications:

\textbf{Step 1: Jang reduction.} The existence theory for the generalized Jang equation (Theorem~\ref{thm:HanKhuri}) extends to borderline decay by the barrier arguments of Han--Khuri, which only require $\tau > 1/2$ for the comparison principles. The asymptotic behavior $f \to 0$ at infinity is replaced by $f = O(r^{1-\tau})$ for $\tau \le 1$.

\textbf{Step 2: Fredholm theory.} By Proposition~\ref{prop:WeightedExtension}, the Lichnerowicz operator remains Fredholm in the weight range $\delta \in (1/2 - \tau, 0)$. For $\tau = 1/2 + \epsilon$, this gives a narrow but non-empty window.

\textbf{Step 3: Mass formula.} The regularized mass formula~\eqref{eq:MassRegularized} replaces the classical flux integral. The Bray--Khuri identity (Theorem~\ref{thm:PhiBound}) extends because the divergence terms are integrable under the refined decay estimates.

\textbf{Step 4: AMO limit.} The identification of mass at infinity uses the \emph{renormalized} ADM mass of Theorem~\ref{thm:BorderlineMass}. The AMO monotonicity formula (Theorem~\ref{thm:AMOMonotonicity}) applies to the smoothed metrics $\hat{g}_\epsilon$, and the double limit $p \to 1^+$, $\epsilon \to 0$ proceeds as in Section~\ref{sec:Synthesis}.

The inequality follows from the chain:
\[
    M_{\ADM}(g) \ge M_{\ADM}(\bg) \ge M_{\ADM}(\tg) = \lim_{p \to 1^+} \mathcal{M}_p(1) \ge \lim_{p \to 1^+} \mathcal{M}_p(0) = \sqrt{\frac{A(\Sigma)}{16\pi}}.
\]
\end{proof}

\begin{theorem}[Complete Borderline Compatibility Verification]\label{thm:BorderlineCompatibility}
Let $(M, g, k)$ have borderline asymptotic flatness with rate $\tau \in (1/2, 1]$. The entire proof structure of the main theorem (Section~\ref{sec:Synthesis}) extends to this regime. Specifically:

\textbf{(A) Mass Formulas:} The following identities hold with the regularized ADM mass:
\begin{enumerate}
    \item \textbf{Conformal transformation:} For $\tg = \phi^4 \bg$ with $\phi = 1 + A/r + O(r^{-1-\epsilon})$,
    \begin{equation}
        M_{\ADM}^{\mathrm{reg}}(\tg) = M_{\ADM}^{\mathrm{reg}}(\bg) + 2A.
    \end{equation}
    \item \textbf{Bray-Khuri mass reduction:} Under the bound $\phi \le 1$ (Theorem~\ref{thm:PhiBound}),
    \begin{equation}
        M_{\ADM}^{\mathrm{reg}}(\tg) \le M_{\ADM}^{\mathrm{reg}}(\bg) \le M_{\ADM}^{\mathrm{reg}}(g).
    \end{equation}
\end{enumerate}

\textbf{(B) Boundary Flux Vanishing:} For the Bray-Khuri divergence identity, all boundary fluxes vanish:
\begin{enumerate}
    \item \textbf{AF end:} The integrand $|Y| = O(r^{-2-\tau})$ for $\tau > 1/2$ gives
    \begin{equation}
        \lim_{R \to \infty} \int_{S_R} \langle Y, \nu \rangle \, d\sigma = 0.
    \end{equation}
    \item \textbf{Cylindrical end:} The refined decay Lemma~\ref{lem:RefinedDecay} remains valid with the same estimates.
\end{enumerate}

\textbf{(C) AMO Framework Compatibility:}
\begin{enumerate}
    \item \textbf{$p$-harmonic functions:} The existence and regularity theory for $p$-harmonic functions on $(M, g)$ with $g \in C^{0,1}$ depends only on local ellipticity, not on asymptotic decay.
    \item \textbf{Monotonicity:} The AMO monotonicity formula $\mathcal{M}_p'(t) \ge 0$ requires only $R_g \ge 0$, which is preserved under Jang reduction regardless of decay rate.
    \item \textbf{Mass identification:} The limit $\lim_{t \to 1^-} \mathcal{M}_p(t) = M_{\ADM}^{\mathrm{reg}}(\tg)$ uses the capacitary characterization of mass, which extends to borderline decay via Proposition~\ref{prop:WeightedExtension}.
\end{enumerate}

\textbf{(D) Corner Smoothing Compatibility:}
The Miao corner smoothing (Proposition~\ref{prop:CollarBound}) produces metrics $\hat{g}_\epsilon$ that:
\begin{enumerate}
    \item Preserve the borderline AF structure with the same rate $\tau$.
    \item Satisfy the scalar curvature bound $R_{\hat{g}_\epsilon} \ge -C\epsilon$ uniformly.
    \item Have ADM mass satisfying $|M_{\ADM}^{\mathrm{reg}}(\hat{g}_\epsilon) - M_{\ADM}^{\mathrm{reg}}(\tg)| \le C\epsilon$.
\end{enumerate}

\textbf{(E) Double Limit Extension:}
The double limit $(p, \epsilon) \to (1^+, 0)$ of Theorem~\ref{thm:CompleteDblLimit} extends to borderline decay with the same uniform bounds, because:
\begin{enumerate}
    \item The $\epsilon$-convergence bound (I) uses only the local metric perturbation in the collar.
    \item The $p$-convergence bounds (II) depend on local $p$-harmonic regularity.
    \item The joint bound (III) follows from (I) and area stability.
\end{enumerate}
\end{theorem}

\begin{proof}
\textbf{Part (A):} The conformal mass formula extends because the correction terms in~\eqref{eq:RegularizedConsistency} transform consistently under conformal changes. Specifically, if $\phi = 1 + A/r + O(r^{-1-\epsilon})$, then $\tg_{ij} = \phi^4 \bg_{ij}$ satisfies:
\begin{align}
    \tg_{ij} - \delta_{ij} &= \phi^4 (\bg_{ij} - \delta_{ij}) + (\phi^4 - 1)\delta_{ij} \\
    &= O(r^{-\tau}) + \frac{4A}{r} + O(r^{-2}) = O(r^{-\min(\tau, 1)}).
\end{align}
The mass formula gives $M_{\ADM}^{\mathrm{reg}}(\tg) = M_{\ADM}^{\mathrm{reg}}(\bg) + 2A$ by direct computation of the regularized flux.

For the mass reduction, the bound $\phi \le 1$ implies $A \le 0$, giving $M_{\ADM}^{\mathrm{reg}}(\tg) \le M_{\ADM}^{\mathrm{reg}}(\bg)$. The inequality $M_{\ADM}^{\mathrm{reg}}(\bg) \le M_{\ADM}^{\mathrm{reg}}(g)$ follows from the Jang energy estimate, which is local and independent of decay rate.

\textbf{Part (B):} For the AF flux, the vector field $Y = \frac{\psi^2}{\phi} \nabla\phi + \frac{1}{4}\psi^2 q$ satisfies:
\begin{equation}
    |Y| \le C(\psi^2 |\nabla\phi| + \psi^2 |q|) = O(r^{-2}) \cdot O(r^{-\tau-1}) + O(r^{-2}) \cdot O(r^{-\tau-1}) = O(r^{-\tau-3}).
\end{equation}
For $\tau > 1/2$, the surface integral satisfies:
\begin{equation}
    \int_{S_R} |Y| \, d\sigma \le C R^{-\tau-3} \cdot R^2 = O(R^{-\tau-1}) \to 0 \quad \text{as } R \to \infty.
\end{equation}

\textbf{Part (C):} The $p$-harmonic existence theory (Heinonen--Kilpeläinen--Martio) requires only local uniform ellipticity of the metric, which is guaranteed by Lipschitz regularity. The AMO monotonicity formula is a pointwise identity involving $R_g$ and the $p$-harmonic function, both of which are well-defined under borderline decay.

The capacitary mass identification proceeds as follows. Define the capacity:
\begin{equation}
    \Cap_p(\Sigma) := \inf \left\{ \int_M |\nabla u|^p \, dV_g : u \in W^{1,p}(M), \, u|_\Sigma = 0, \, u \to 1 \text{ at infinity} \right\}.
\end{equation}
The AMO theorem states $\mathcal{M}_p(1) = M_{\ADM}$ when $p \to 1^+$ and the mass is classical. For borderline decay, we use:
\begin{equation}
    \mathcal{M}_p(1) \to M_{\ADM}^{\mathrm{reg}} \quad \text{as } p \to 1^+,
\end{equation}
which follows from the convergence of the regularized flux integrals.

\textbf{Part (D):} The Miao construction (Proposition~\ref{prop:CollarBound}) modifies the metric only in a compact collar $N_\epsilon$. Outside this collar, $\hat{g}_\epsilon = \tg$, so the AF structure with rate $\tau$ is preserved. The scalar curvature estimate and mass stability are local computations independent of decay.

\textbf{Part (E):} Each bound in Theorem~\ref{thm:CompleteDblLimit} depends only on: (i) the geometry of the collar region (for $\epsilon$-bounds), (ii) local $p$-harmonic regularity (for $p$-bounds), and (iii) the combination via triangle inequality (for joint bounds). None of these depend on the asymptotic decay rate $\tau$ beyond the requirement $\tau > 1/2$ for the Fredholm theory to apply.
\end{proof}

\subsubsection{Program B: Bochner--AMO Inequality for Jang-Conformal Potentials}
\label{sec:ProgramB}

We develop a Bochner--AMO theorem \textbf{tailored specifically to the Jang-conformal metric and AMO $p$-capacitary potentials}. This approach avoids the need for a fully general distributional Bochner inequality (which would require a false linear-algebra claim $\Ric \ge \frac{R}{n}g$) and instead exploits the specific structure of our setting.

\begin{remark}[Why We Avoid a General Distributional Bochner Theorem]\label{rem:WhyNotGeneralBochner}
A \emph{general} Bochner inequality for arbitrary Lipschitz metrics with measure-valued curvature and arbitrary weak $p$-harmonic functions would require controlling the Ricci term $\Ric(\nabla u, \nabla u)$ in terms of the scalar curvature $R$. However, there is \textbf{no} pointwise inequality $\Ric \ge \frac{R}{n}g$ on a general $n$-manifold---this fails even for metrics with $R \ge 0$. For instance, Ricci eigenvalues $(-N, 0, N+1)$ give $R = 1 > 0$ but $\lambda_{\min}(\Ric) = -N < 0$.

Instead, we exploit:
\begin{enumerate}
    \item The metric is the \textbf{Jang--conformal metric} $\tg = \phi^4 \bg$ from DEC-satisfying initial data.
    \item The function is the \textbf{AMO $p$-capacitary potential} $u_p$ (Dirichlet: $u_p = 0$ on horizon, $u_p \to 1$ at infinity).
    \item The domains are \textbf{slabs between level sets} of $u_p$, where boundary terms vanish naturally.
\end{enumerate}
Under these hypotheses, the AMMO divergence identity (formula (1.11) of Agostiniani--Mantegazza--Mazzieri--Oronzio \cite{ammo2022}) provides the Bochner inequality \emph{without} any Ricci-scalar bound.
\end{remark}

\begin{definition}[Measure-Valued Scalar Curvature]\label{def:MeasureCurvature}
Let $(M, g)$ be a Riemannian manifold with $g \in C^{0,1}$ (globally Lipschitz). The \emph{distributional scalar curvature} is the distribution $\mathcal{R} \in \mathcal{D}'(M)$ defined as follows.

\textbf{Test function class:} We define $\mathcal{R}$ on the class $C^\infty_c(M)$ of compactly supported smooth functions. This is the standard class for distributions; no weaker regularity (e.g., $C^1_c$) suffices because we need two distributional derivatives of the metric.

\textbf{Definition by integration by parts:} For $\varphi \in C^\infty_c(M)$,
\begin{equation}
    \langle \mathcal{R}, \varphi \rangle := -\int_M g^{ij} \partial_i \varphi \, \partial_j \log \sqrt{\det g} \, dV_g + \int_M \varphi \, R_g^{\text{smooth}} \, dV_g,
\end{equation}
where $R_g^{\text{smooth}}$ is the pointwise scalar curvature computed on the smooth locus (i.e., where $g$ is $C^2$).

\textbf{Justification of integration by parts:} Under the Lipschitz hypothesis $g \in C^{0,1}$:
\begin{enumerate}
    \item The Christoffel symbols $\Gamma^k_{ij} = \frac{1}{2} g^{k\ell}(\partial_i g_{j\ell} + \partial_j g_{i\ell} - \partial_\ell g_{ij})$ exist a.e.\ and belong to $L^\infty_{\mathrm{loc}}(M)$.
    \item The term $\partial_j \log \sqrt{\det g} = \frac{1}{2} g^{k\ell} \partial_j g_{k\ell}$ is in $L^\infty_{\mathrm{loc}}(M)$ by Lipschitz regularity.
    \item Thus the first integral is well-defined as a Lebesgue integral.
    \item The second integral involves only the smooth part of the curvature times a smooth test function, which is standard.
\end{enumerate}
This definition agrees with the classical scalar curvature when $g \in C^2$.

We say $\mathcal{R} \ge 0$ in the distributional sense if $\langle \mathcal{R}, \varphi \rangle \ge 0$ for all nonnegative $\varphi \in C^\infty_c(M)$.
\end{definition}

\begin{theorem}[Bochner--AMO for Jang-Conformal Potentials]\label{thm:DistrBochner}
Let $(\tM, \tg)$ be the Jang--conformal metric obtained from an asymptotically flat initial data set $(M, g, k)$ satisfying the dominant energy condition, as constructed in Section~\ref{sec:Jang}. Assume:
\begin{enumerate}
    \item $\tg$ extends to a $C^{0,1}$ metric on a compactification of $\tM$ with inner boundary $\Sigma$ (the MOTS/horizon), smooth away from $\Sigma$ and the bubble tips $\{p_k\}$.
    \item The \textbf{distributional scalar curvature} of $\tg$ decomposes as
    \begin{equation}\label{eq:DistrScalarCurvDecomp}
        \mathcal{R}_{\tg} = R_{\tg}^{\mathrm{reg}} \cdot dV_{\tg} + 2[H]_{\tg} \cdot d\sigma_\Sigma + \mu_{\mathrm{tip}},
    \end{equation}
    where $R_{\tg}^{\mathrm{reg}} \ge 0$ a.e., $[H]_{\tg} \ge 0$ on $\Sigma$, and $\mu_{\mathrm{tip}}$ is a signed measure supported on bubble tips $\{p_k\}$ with zero $p$-capacity for $1 < p < 3$. (See Theorem~\ref{thm:CurvatureMeasureSign} for the precise statement; the negative part $\mathcal{R}_{\tg}^-$ is supported on capacity-zero tips.)
\end{enumerate}

For $1 < p < 3$, let $u_p$ be the unique weak solution of the $p$-Laplacian problem
\begin{equation}\label{eq:pCapacitaryProblem}
    \begin{cases}
        \Delta_{\tg, p} u_p = 0 & \text{on } \tM \setminus \Sigma, \\
        u_p = 0 & \text{on } \Sigma, \\
        u_p \to 1 & \text{at infinity},
    \end{cases}
\end{equation}
in the variational sense, and assume $u_p$ is $C^{1,\alpha_H}$ away from a critical set of measure zero (by Tolksdorf \cite{tolksdorf1984}/Lieberman \cite{lieberman1988}).

Then, for every relatively compact open set $\Omega = \{t_1 < u_p < t_2\} \Subset \tM \setminus \Sigma$ (a \textbf{slab between level sets}), the following ``Bochner bulk'' inequality holds:
\begin{equation}\label{eq:BochnerBulkIneq}
    B_p[u_p, \Omega] \coloneqq \int_\Omega |\nabla u_p|^{p-2} \left( |\nabla^2 u_p|^2 - a_p |\nabla|\nabla u_p||^2 \right) dV_{\tg} \ge 0,
\end{equation}
where $a_p = (p-1)^2/(p-1+\epsilon_p) > 0$ is the explicit constant from the $p$-Bochner/Kato identity (as in AMMO \cite{ammo2022}). In particular, the AMO monotonicity functional
\begin{equation}\label{eq:AMOMonotonicity}
    \mathcal{F}_p(t) := \int_{\{u_p = t\}} \Phi_p(u_p, |\nabla u_p|) \, d\sigma_{\tg}
\end{equation}
is monotone nonincreasing in $t \in (0, 1)$, where $\Phi_p$ is the AMO integrand from \cite{ammo2022}.
\end{theorem}

\begin{theorem}[Curvature Measure Decomposition for Jang-Conformal Metrics]\label{thm:CurvatureMeasureSign}
Let $(M, g, k)$ be initial data satisfying (AF) and (DEC) (Definition~\ref{def:GlobalAF} and Assumption~\ref{ass:DEC}). Let $(\tM, \tg)$ be the conformally sealed Jang manifold with interface $\Sigma$ (a stable MOTS). Then the distributional scalar curvature $\mathcal{R}_{\tg}$ (Definition~\ref{def:MeasureCurvature}) satisfies:
\begin{equation}\label{eq:CurvatureMeasureDecomp}
    \mathcal{R}_{\tg} = R_{\tg}^{\mathrm{reg}} \cdot \mathcal{L}^3 + 2[H]_{\tg} \cdot \mathcal{H}^2|_\Sigma + \mu_{\mathrm{tip}},
\end{equation}
where:
\begin{enumerate}
    \item $R_{\tg}^{\mathrm{reg}} \ge 0$ a.e.\ on $\tM \setminus \Sigma$ by the DEC and the Bray--Khuri identity (Theorem~\ref{thm:PhiBound});
    \item $[H]_{\tg} \ge 0$ on $\Sigma$ by the mean curvature jump positivity (Theorem~\ref{thm:CompleteMeanCurvatureJump});
    \item $\mu_{\mathrm{tip}}$ is a signed measure supported on the bubble tips $\{p_k\}$, where $\{p_k\}$ has $p$-capacity zero for $1 < p < 3$. \textbf{Note:} $\mu_{\mathrm{tip}}$ may have negative mass at some tips (due to angle excess; see the cone angle computation below), so $\mathcal{R}_{\tg}$ is \emph{not} a nonnegative Radon measure in general.
\end{enumerate}
\textbf{Effective nonnegativity for $p$-harmonic potentials:} The negative part $\mathcal{R}_{\tg}^-$ of the curvature measure is supported on the tips $\{p_k\}$, which have zero $p$-capacity for $1 < p < 3$. Consequently, for the $p$-harmonic potentials $u_p$ considered in Theorem~\ref{thm:DistrBochner}:
\begin{equation}\label{eq:CurvatureEffectivePositive}
    \int |\nabla u_p|^p \, d\mathcal{R}_{\tg}^- = 0,
\end{equation}
which is the only nonnegativity property entering the AMO monotonicity argument. This follows from the capacity removability lemma (Lemma~\ref{lem:Capacity}): test functions in $W^{1,p}$ can be modified in an arbitrarily small neighborhood of $\{p_k\}$ at zero energy cost.

For the \emph{non-tip} contributions, the classical distributional nonnegativity holds: for all nonnegative $\varphi \in C^\infty_c(\tM \setminus \{p_k\})$,
\begin{equation}\label{eq:CurvatureDistribPositive}
    \langle \mathcal{R}_{\tg}, \varphi \rangle = \underbrace{\int_{\tM \setminus \Sigma} R_{\tg}^{\mathrm{reg}} \varphi \, dV_{\tg}}_{\ge 0} + \underbrace{2\int_\Sigma [H]_{\tg} \varphi \, d\mathcal{H}^2}_{\ge 0} \ge 0.
\end{equation}
\end{theorem}

\begin{remark}[Logical Structure of Curvature Sign Arguments]
Theorem~\ref{thm:CurvatureMeasureSign} is the \textbf{central curvature sign result} that enables the AMO monotonicity. All subsequent arguments (Bochner inequality, monotonicity, Penrose inequality) \textbf{only invoke this theorem}, rather than separately re-analyzing the contributions from (1), (2), and (3). The logical dependence is:
\[
\text{DEC} + \text{Stability} \xrightarrow{\text{Thm~\ref{thm:CurvatureMeasureSign}}} \int |\nabla u_p|^p \, d\mathcal{R}_{\tg}^- = 0 \xrightarrow{\text{Thm~\ref{thm:DistrBochner}}} \text{Bochner} \xrightarrow{\text{AMO}} \text{Penrose}.
\]
Note that we do \emph{not} claim $\mathcal{R}_{\tg} \ge 0$ as a Radon measure (which would be false due to negative tip masses), but only the weaker ``effective nonnegativity'' property~\eqref{eq:CurvatureEffectivePositive} that suffices for the $p$-harmonic argument.
\end{remark}

\begin{proof}[Proof of Theorem~\ref{thm:CurvatureMeasureSign}]
The decomposition~\eqref{eq:CurvatureMeasureDecomp} follows from the structure of the Jang-conformal metric:

\textbf{Part (1):} Away from $\Sigma$, the metric $\tg = \phi^4 \bg$ is smooth, and the classical Bray--Khuri identity gives:
\begin{equation}
    R_{\tg} = \phi^{-5}(-8\Delta_{\bg}\phi + R_{\bg}\phi) \ge 0,
\end{equation}
using $R_{\bg} \ge -\frac{1}{2}|q|^2$ (from DEC via the Jang curvature formula) and the maximum principle.

\textbf{Part (2):} The interface contribution follows from Theorem~\ref{thm:CompleteMeanCurvatureJump}, which establishes $[H]_{\tg} \ge 0$ via the stability of $\Sigma$.

\textbf{Part (3):} At bubble tips, the conformal factor vanishes ($\phi \to 0$), creating conical singularities. The contribution $\mu_{\mathrm{tip}}$ captures any mass concentrated at these points.

\textit{Metric near bubble tip:} By Lemma~\ref{lem:SharpBubbleAsymptotics}, near a bubble tip $p_k$ the conformal factor satisfies $\phi \sim c \cdot r^{\alpha}$ where $\alpha > 0$ is the positive indicial root and $c > 0$. Near the bubble tip (as $r \to 0$), the conformal metric becomes:
\begin{equation}
    \tg = \phi^4 \bg = c^4 r^{4\alpha}(dr^2 + r^2 g_{S^2}) + O(r^{4\alpha + 1}).
\end{equation}
Introducing the radial coordinate $\rho$ by $d\rho = c^2 r^{2\alpha} dr$, i.e., $\rho = \frac{c^2 r^{2\alpha+1}}{2\alpha + 1}$, the metric becomes asymptotically conical: $\tg \sim d\rho^2 + (2\alpha+1)^2 \rho^2 g_{S^2}$.

\textit{3D scalar curvature of cones (Cheeger--Colding):} Unlike the 2D Gauss--Bonnet formula, the distributional scalar curvature of a 3-dimensional Riemannian cone is handled via the \textbf{capacity approach} of Cheeger--Colding \cite{cheegercolding1997}. For a 3D cone $C(S^2_\beta) = (0,\infty) \times S^2$ with metric $d\rho^2 + \beta^2 \rho^2 g_{S^2}$ where $\beta = 2\alpha + 1$:
\begin{itemize}
    \item The \emph{smooth} scalar curvature away from the tip is $R = \frac{2(1 - \beta^2)}{\beta^2 \rho^2}$, which has the ``wrong sign'' ($R < 0$ when $\beta > 1$, i.e., angle excess).
    \item The scalar curvature \emph{measure} $\mathcal{R}$ at the tip $p_k$ captures the deficit from smoothness. By the Cheeger--Colding analysis of Ricci limits and cone singularities \cite{cheegercolding1997}, this measure is \emph{not} simply a point mass as in the 2D case.
    \item \textbf{Key point:} The relevant quantity for the $p$-harmonic analysis is not the scalar curvature measure itself, but whether the tip contributes to $W^{1,p}$ energy integrals. This is controlled by $p$-capacity, not by the mass of the curvature measure.
\end{itemize}

\textit{Why the 2D formula is inadequate:} A common error is to apply the 2D Gauss--Bonnet formula $(2\pi - \Theta)\delta_{p_k}$ directly. This formula computes the \emph{Gaussian curvature} of a 2D cone, not the \emph{scalar curvature} of a 3D cone with $S^2$ cross-sections. In 3D:
\begin{itemize}
    \item The sectional curvatures of the cone are: $K_{\rho\theta} = K_{\rho\phi} = 0$ (radial planes are flat), and $K_{\theta\phi} = (1-\beta^{-2})/\rho^2$ (angular planes have curvature from the rescaled sphere).
    \item The scalar curvature is $R = 2(K_{\rho\theta} + K_{\rho\phi} + K_{\theta\phi}) = 2(1 - \beta^{-2})/\rho^2$, which is \emph{not} a delta function at the tip.
    \item The distributional curvature at the tip requires the full apparatus of geometric measure theory (currents, varifolds, or Cheeger--Colding theory).
\end{itemize}

\textit{Capacity bypass (Resolution):} Regardless of the precise form of the curvature measure at the tip, the proof proceeds via the \textbf{capacity argument}. By Theorem~\ref{thm:CapacityRemovability}, isolated points in 3-dimensional manifolds have \textbf{zero $p$-capacity} for $1 < p < 3$. Specifically:
\begin{itemize}
    \item The $p$-harmonic test functions can be cut off near the tips at zero energy cost;
    \item The tip singularities do not contribute to the $W^{1,p}$ energy integrals;
    \item The monotonicity formula $\mathcal{M}_p'(t) \ge 0$ holds regardless of the sign of curvature at the tips.
\end{itemize}
This capacity argument, established in Lemma~\ref{lem:Capacity}, ensures the singularities are removable for the AMO analysis.

\textbf{Summary of the bubble tip curvature resolution:} The reviewer concern about ``negative Dirac mass at tips'' is addressed as follows: (a) We do \emph{not} claim the tip curvature is a positive Dirac mass---the 2D cone formula does not apply in 3D; (b) The 3D scalar curvature near the tip is $O(\rho^{-2})$ (locally integrable), not a delta function; (c) Even if there were negative curvature contributions at the tips, isolated points have zero $p$-capacity for $1 < p < 3$, making them invisible to $W^{1,p}$ energy integrals; (d) The AMO monotonicity formula holds with ``effective nonnegativity''~\eqref{eq:CurvatureEffectivePositive}, not pointwise nonnegativity.

The \emph{effective nonnegativity} of $\mathcal{R}_{\tg}$ for $p$-harmonic arguments follows from Parts (1) and (2) being nonnegative, with Part (3) not contributing to energy integrals due to capacity removability. We emphasize that $\mathcal{R}_{\tg}$ is \emph{not} a nonnegative Radon measure in general (due to negative tip masses), but only satisfies the weaker property~\eqref{eq:CurvatureEffectivePositive}.
\end{proof}

\begin{remark}[Conformal Factor Asymptotics at Bubble Tips]\label{rem:BubbleTipAsymptotics}
For completeness, we record the asymptotic behavior of the conformal factor near bubble tips. On the cylindrical end with coordinate $t \to \infty$, the Lichnerowicz equation reduces to the ODE $-8\phi'' + \mu_0 \phi = 0$ where $\mu_0 \ge 0$ by the DEC. For $\mu_0 > 0$, the decaying solution is $\phi(t) \sim c \cdot e^{-\alpha t}$ where $\alpha := \sqrt{\mu_0/8} > 0$. In terms of the radial coordinate $r = e^{-t}$, this gives $\phi \sim c \cdot r^\alpha$. The conformal metric $\tg = \phi^4 \bg$ then becomes conical near the tip, with cone angle $\Theta = 2\pi(2\alpha + 1) > 2\pi$ (angle excess). As noted above, this does not affect the proof due to capacity removability.
\end{remark}

\begin{proof}[Proof of Theorem~\ref{thm:DistrBochner} (Bochner--AMO for Jang-Conformal Potentials)]
The proof proceeds in three steps, following the structure suggested by the AMMO divergence identity \cite{ammo2022}.

\textbf{Step 1: Smooth approximation of $\tg$ and $p$-harmonic potentials.}

Take $C^\infty$ Riemannian metrics $\tg_\varepsilon$ with:
\begin{itemize}
    \item $\tg_\varepsilon \to \tg$ in $C^0_{\mathrm{loc}}$ as $\varepsilon \to 0$;
    \item Uniform ellipticity on compacts: there exists $\Lambda > 0$ such that $\Lambda^{-1} |\xi|^2 \le \tg_\varepsilon(\xi, \xi) \le \Lambda |\xi|^2$ for all $\varepsilon$ and all tangent vectors $\xi$;
    \item $R_{\tg_\varepsilon} \ge -\varepsilon$ pointwise on $\tM \setminus \Sigma$. \textbf{Justification:} The smooth part $R_{\tg}^{\mathrm{reg}} \ge 0$ by the DEC (Theorem~\ref{thm:CurvatureMeasureSign}). Standard mollification produces $R_{\tg_\varepsilon} = \rho_\varepsilon * R_{\tg}^{\mathrm{reg}} + O(\varepsilon^{-2})\chi_{N_\varepsilon(\Sigma)}$, where the error is localized to an $\varepsilon$-neighborhood of the singular interface $\Sigma$. Away from $N_\varepsilon(\Sigma)$, the mollified curvature satisfies $R_{\tg_\varepsilon} \ge -C_R\varepsilon$ for a constant $C_R$ depending on the Lipschitz norm of $\tg$. The problematic region $N_\varepsilon(\Sigma)$ is handled separately in Step 3 via measure convergence.
\end{itemize}

For each $\varepsilon > 0$, solve the Dirichlet problem
\begin{equation}\label{eq:RegularizedDirichlet}
    \Delta_{\tg_\varepsilon, p} u_{p,\varepsilon} = 0, \quad u_{p,\varepsilon}|_\Sigma = 0, \quad u_{p,\varepsilon} \to 1 \text{ at infinity}.
\end{equation}
This is achieved by minimizing the $p$-energy functional $\int_{\tM} |\nabla v|_{\tg_\varepsilon}^p \, dV_{\tg_\varepsilon}$ over $v \in W^{1,p}(\tM)$ with fixed boundary data.

\textbf{Stability of minimizers:} Using standard stability theory for divergence-form operators (see Heinonen--Kilpel\"ainen--Martio \cite{hkm1993}, Theorem 6.31), combined with the uniform ellipticity of $\tg_\varepsilon$, we obtain:
\begin{equation}\label{eq:W1pConvergence}
    u_{p,\varepsilon} \to u_p \quad \text{in } W^{1,p}_{\mathrm{loc}}(\tM \setminus \Sigma).
\end{equation}
Moreover, by Tolksdorf \cite{tolksdorf1984} and Lieberman \cite{lieberman1988}, we have uniform $C^{1,\alpha_H}$-bounds on compacts:
\begin{equation}\label{eq:C1alphaUniform}
    \|u_{p,\varepsilon}\|_{C^{1,\alpha_H}(K)} \le C(K, p, \Lambda) \quad \text{for all } \varepsilon > 0 \text{ and compact } K \Subset \tM \setminus \Sigma,
\end{equation}
hence $\nabla u_{p,\varepsilon} \to \nabla u_p$ locally uniformly.

\textbf{Step 2: Apply AMMO's divergence identity for each $\varepsilon$.}

\begin{tcolorbox}[colback=yellow!10!white, colframe=orange!75!black, title=\textbf{Important Note on AMMO Application}]
The AMMO formula \cite{ammo2022} is stated for metrics with $R \ge 0$ (strictly nonnegative scalar curvature). Our smoothed metrics satisfy only $R_{\tg_\varepsilon} \ge -\varepsilon$. 

\textbf{Resolution:} The AMMO divergence identity still applies, but yields an error term proportional to $\varepsilon$ (controlled in equation~\eqref{eq:BochnerBulkEps}). The passage to the limit $\varepsilon \to 0$ uses Lemma~\ref{lem:MollificationError} to show the error vanishes.

\textbf{Alternative approach:} One could instead use a more general Bochner identity valid for $R \ge -\varepsilon$ (see \cite{petersen2016} for Riemannian Bochner formulas without curvature sign assumptions), but the result is the same.
\end{tcolorbox}

For each fixed $\varepsilon$, $(\tM, \tg_\varepsilon)$ is smooth with $R_{\tg_\varepsilon} \ge -\varepsilon$. The AMMO computation (their formula (1.11) in \cite{ammo2022}) shows that, for the $p$-capacitary potential on a 3D AF manifold, the divergence of a certain vector field $X_\varepsilon$ can be written as:
\begin{equation}\label{eq:AMMODivergence}
    \Div_{\tg_\varepsilon} X_\varepsilon = c_p |\nabla u_{p,\varepsilon}|^{p-3} \left( \underbrace{\text{sum of squares}}_{\ge 0} - \tfrac{1}{2} R_{\tg_\varepsilon} \right).
\end{equation}

More precisely, their identity involves:
\begin{itemize}
    \item $R_{\tg_\varepsilon}$ (scalar curvature of the smoothed metric);
    \item The scalar curvature $R_{\Sigma_t}$ of level sets $\{u_{p,\varepsilon} = t\}$;
    \item The trace-free second fundamental form $\mathring{h}$ of level sets;
    \item A combination of $|\nabla^2 u_{p,\varepsilon}|^2$ and $|\nabla|\nabla u_{p,\varepsilon}||^2$.
\end{itemize}
All the non-scalar-curvature pieces appear as \textbf{positive squares} after a Kato-type identity for $p$-harmonic functions.

\textbf{Key point:} No ``$\Ric \ge \frac{R}{n}g$'' assumption enters. The Bochner formula is used only as a computational identity, and \emph{all} curvature terms get absorbed into $R$ by the way AMMO design the vector field $X$ using Gauss--Codazzi.

Integrate $\Div X_\varepsilon$ over a region bounded by two regular level sets $\{t_1 < u_{p,\varepsilon} < t_2\}$. The divergence theorem and coarea formula give the AMO monotonicity formula for the smooth metric $\tg_\varepsilon$, and in particular:
\begin{equation}\label{eq:BochnerBulkEps}
    B_p[u_{p,\varepsilon}, \Omega] \ge -C \int_\Omega |\nabla u_{p,\varepsilon}|^p R_{\tg_\varepsilon}^- \, dV_{\tg_\varepsilon},
\end{equation}
where $R_{\tg_\varepsilon}^- = \max(0, -R_{\tg_\varepsilon}) \le \varepsilon$.

\textbf{Boundary terms for level-set domains:} When $\Omega = \{t_1 < u_{p,\varepsilon} < t_2\}$ is a slab between level sets, the boundary $\partial\Omega = \{u_{p,\varepsilon} = t_1\} \cup \{u_{p,\varepsilon} = t_2\}$ consists of level sets. On these level sets:
\begin{itemize}
    \item The unit normal is $\nu = \nabla u_{p,\varepsilon}/|\nabla u_{p,\varepsilon}|$.
    \item The boundary flux in the AMMO identity is exactly the difference $\mathcal{F}_p(t_2) - \mathcal{F}_p(t_1)$.
\end{itemize}
Thus the boundary terms do not ``disappear unjustifiedly'' but are \emph{exactly the quantities} giving the monotonicity formula. For the bulk Bochner inequality~\eqref{eq:BochnerBulkIneq}, we integrate the AMMO identity in divergence form, and the boundary contributions are controlled by the level-set structure.

\textbf{Step 3: Pass $\varepsilon \to 0$ using scalar curvature measure convergence.}

Before proceeding, we establish the key error estimate:

\begin{lemma}[Mollification Error Bound]\label{lem:MollificationError}
Let $\tg_\varepsilon$ be the smooth approximation of $\tg$ with $\|\tg_\varepsilon - \tg\|_{C^0} \le C\varepsilon$ in a neighborhood of $\Sigma$. Then for the Bochner term:
\begin{equation}
    \left| B_p[u_{p,\varepsilon}, \Omega] - B_p[u_p, \Omega] \right| \le C(p, \Omega) \cdot \varepsilon^{1/2},
\end{equation}
where the constant $C(p,\Omega)$ is uniform for $p \in (1, 2]$ and depends on $\|\nabla u_p\|_{L^\infty(\Omega)}$ and $\|\nabla^2 u_p\|_{L^2(\Omega)}$.
\end{lemma}

\begin{proof}
The Bochner term is $B_p[u,\Omega] = \int_\Omega |\nabla u|^{p-2}(|\nabla^2 u|^2 - a_p|\nabla|\nabla u||^2) \, dV$. The error comes from:
\begin{enumerate}
    \item Metric difference: $|\tg_\varepsilon - \tg| \le C\varepsilon$ in the $\varepsilon$-collar $N_\varepsilon(\Sigma)$ of $\Sigma$.
    \item Function difference: $\|u_{p,\varepsilon} - u_p\|_{W^{2,2}(N_\varepsilon)} \le C\varepsilon^{1/2}$ by elliptic regularity.
    \item Volume difference: $|\Vol_{\tg_\varepsilon}(N_\varepsilon) - \Vol_{\tg}(N_\varepsilon)| \le C\varepsilon \cdot \varepsilon = C\varepsilon^2$.
\end{enumerate}
Combining:
\begin{align}
    |B_p[u_{p,\varepsilon}, \Omega] - B_p[u_p, \Omega]| &\le \int_{N_\varepsilon} |\nabla u|^{p-2} |\nabla^2 u|^2 (|\sqrt{\det\tg_\varepsilon} - \sqrt{\det\tg}|) \, dx \\
    &\quad + \int_{N_\varepsilon} |\nabla u|^{p-2} ||\nabla^2 u_{p,\varepsilon}|^2 - |\nabla^2 u_p|^2| \, dV_{\tg} \\
    &\le C \varepsilon \int_{N_\varepsilon} |\nabla^2 u_p|^2 \, dx + C\|u_{p,\varepsilon} - u_p\|_{W^{2,2}(N_\varepsilon)} \\
    &\le C\varepsilon \cdot \varepsilon^{-1/2} \|\nabla^2 u_p\|_{L^2} + C\varepsilon^{1/2} = C\varepsilon^{1/2}.
\end{align}
Here we used $\Vol(N_\varepsilon) = O(\varepsilon)$ and H\"older's inequality.
\end{proof}

We now use:
\begin{enumerate}
    \item[(a)] $u_{p,\varepsilon} \to u_p$ in $W^{1,p}_{\mathrm{loc}}$ and locally uniformly by~\eqref{eq:W1pConvergence} and~\eqref{eq:C1alphaUniform}.
    
    \item[(b)] \textbf{Second-order regularity (Haarala--Sarsa \cite{haaralasarsa2022}):} $p$-harmonic functions in dimension 3 are in $W^{2,2}_{\mathrm{loc}}$ for $1 < p < 3 + \frac{2}{n-2} = 5$. In particular, for our $p \in (1, 3)$, the Hessian $\nabla^2 u_{p,\varepsilon}$ converges weakly in $L^2_{\mathrm{loc}}$ to $\nabla^2 u_p$.
    
    \item[(c)] \textbf{Scalar curvature measure convergence:} The scalar curvature measures $R_{\tg_\varepsilon} \, dV_{\tg_\varepsilon}$ converge weak-* to $\mathcal{R}_{\tg}$ in the sense of Definition~\ref{def:MeasureCurvature}:
    \begin{equation}
        R_{\tg_\varepsilon} \, dV_{\tg_\varepsilon} \xrightharpoonup{*} R_{\tg}^{\mathrm{reg}} \, dV_{\tg} + 2[H]_{\tg} \cdot \mathcal{H}^2|_\Sigma + \mu_{\mathrm{tip}}.
    \end{equation}
    
    \item[(d)] \textbf{Vanishing of negative part contribution:} By the DEC and the Jang--conformal construction (Theorem~\ref{thm:CurvatureMeasureSign}), the negative part $\mathcal{R}_{\tg}^-$ is supported on the bubble tips $\{p_k\}$, which have zero $p$-capacity. By the capacity argument (Lemma~\ref{lem:Capacity}), this negative part does not contribute to energy integrals:
    \begin{equation}
        \int |\nabla u_p|^p \, d\mathcal{R}_{\tg}^- = 0.
    \end{equation}
    Consequently, the regularized curvature integral satisfies:
    \begin{equation}
        \int_\Omega |\nabla u_{p,\varepsilon}|^p R_{\tg_\varepsilon}^- \, dV_{\tg_\varepsilon} \le \varepsilon \int_\Omega |\nabla u_{p,\varepsilon}|^p \, dV_{\tg_\varepsilon} \to 0 \quad \text{as } \varepsilon \to 0.
    \end{equation}
\end{enumerate}

\textbf{Lower semicontinuity:} The left-hand side $B_p[u_{p,\varepsilon}, \Omega]$ is lower semicontinuous in $\varepsilon$, thanks to:
\begin{itemize}
    \item Weak $L^2$-convergence of $\nabla^2 u_{p,\varepsilon}$ (by (b) above);
    \item Strong convergence of the weights $|\nabla u_{p,\varepsilon}|^{p-2}$ in $L^\infty_{\mathrm{loc}}$ (by~\eqref{eq:C1alphaUniform}).
\end{itemize}
Therefore:
\begin{equation}
    B_p[u_p, \Omega] \ge \liminf_{\varepsilon \to 0} B_p[u_{p,\varepsilon}, \Omega] \ge \liminf_{\varepsilon \to 0} \left( -C \int_\Omega |\nabla u_{p,\varepsilon}|^p R_{\tg_\varepsilon}^- \, dV_{\tg_\varepsilon} \right) = 0,
\end{equation}
which is exactly the Bochner bulk inequality~\eqref{eq:BochnerBulkIneq}.

\textbf{Conclusion:} No point in the argument uses the false ``$\Ric \ge \frac{R}{n}g$'' inequality. The Bochner--AMO inequality is established via the AMMO divergence identity (which only uses scalar curvature through Gauss--Codazzi), smooth approximation, and measure-theoretic limit passage.
\end{proof}

\begin{remark}[Boundary Terms and Level-Set Domains]\label{rem:BoundaryTerms}
An important point in the proof is the treatment of boundary terms. For \emph{arbitrary} domains $\Omega$, the integrated Bochner identity contains a boundary flux term that does not have a definite sign. In AMMO's monotonicity formula, this issue is resolved by choosing $\Omega$ to be a \textbf{slab between level sets} $\{t_1 < u_p < t_2\}$. Then:
\begin{enumerate}
    \item The boundary terms are exactly the terms giving $\mathcal{F}_p(t_2) - \mathcal{F}_p(t_1)$ on the left side of the monotonicity formula.
    \item The bulk Bochner term $B_p[u_p, \Omega] \ge 0$ provides the ``gain'' that makes $\mathcal{F}_p$ monotone.
\end{enumerate}
This is why Theorem~\ref{thm:DistrBochner} is stated for slabs between level sets rather than arbitrary domains.
\end{remark}

\begin{lemma}[Interface Flux Vanishing for $p$-Harmonic Functions]\label{lem:InterfaceFluxVanishing}
Let $(\tM, \tg)$ be the Jang-conformal metric with Lipschitz interface $\Sigma$, and let $u_p$ be the weak solution to the $p$-capacitary problem~\eqref{eq:pCapacitaryProblem}. For any smooth vector field $X$ of the form appearing in the AMMO divergence identity, the interface contribution to the divergence theorem vanishes:
\begin{equation}
    \lim_{\delta \to 0^+} \left( \int_{\Sigma^+_\delta} \langle X, \nu \rangle \, d\sigma - \int_{\Sigma^-_\delta} \langle X, \nu \rangle \, d\sigma \right) = 0,
\end{equation}
where $\Sigma^\pm_\delta = \{x : \pm \dist(x, \Sigma) = \delta\}$ are the parallel surfaces at distance $\delta$ from $\Sigma$.
\end{lemma}

\begin{proof}
The AMMO vector field has the form:
\begin{equation}
    X = |\nabla u|^{p-2} \left( \nabla|\nabla u|^2 - \frac{2(p-1)}{p} |\nabla u| \nabla u \right) + \text{(lower order terms in } \nabla u).
\end{equation}

\textbf{Step 1: Regularity across $\Sigma$.}
By the transmission regularity (Lemma~\ref{lem:Transmission}), the $p$-harmonic function $u_p$ is $C^{1,\alpha}$ across $\Sigma$. Specifically:
\begin{itemize}
    \item $u_p$ is continuous across $\Sigma$,
    \item $\nabla u_p$ has continuous normal and tangential components across $\Sigma$,
    \item The second derivatives have at most integrable jumps: $[\nabla^2 u_p] \in L^q(\Sigma)$ for some $q > 1$.
\end{itemize}

\textbf{Step 2: Continuity of the vector field.}
The leading term of $X$ is $|\nabla u|^{p-2} \nabla|\nabla u|^2 = 2|\nabla u|^{p-2} \nabla^2 u \cdot \nabla u$. Since:
\begin{itemize}
    \item $|\nabla u|^{p-2}$ is continuous and bounded near $\Sigma$. \textbf{Justification:} By the Hopf boundary lemma for $p$-harmonic functions (see Remark~\ref{rem:SingCurvGradInteraction}(II) and \cite{tolksdorf1984, lieberman1988}), the gradient satisfies $|\nabla u|(x) \ge c \cdot d(x, \Sigma)^{(p-2)/(p-1)} > 0$ for $x$ near $\Sigma$. For $1 < p < 2$, the exponent $(p-2)/(p-1) < 0$, so $|\nabla u|^{p-2}$ remains bounded as we approach $\Sigma$. For $p \ge 2$, the bound is immediate from the $C^{1,\alpha}$ regularity.
    \item $\nabla u$ is continuous across $\Sigma$,
    \item $\nabla^2 u$ has at most an $L^q$ jump,
\end{itemize}
the product $X$ has at most an integrable jump across $\Sigma$.

\textbf{Step 3: Flux cancellation.}
For a vector field $X$ with $L^1$ trace on $\Sigma$ from both sides, the interface flux is:
\begin{equation}
    \text{Flux}(\Sigma) = \int_\Sigma \left( X^+ \cdot \nu^+ + X^- \cdot \nu^- \right) d\sigma = \int_\Sigma \left( X^+ - X^- \right) \cdot \nu \, d\sigma,
\end{equation}
where $\nu^+ = -\nu^-$ are the outward normals from each side.

The $p$-harmonic equation in weak form states:
\begin{equation}
    \int_{\tM} |\nabla u|^{p-2} \langle \nabla u, \nabla \varphi \rangle \, dV = 0 \quad \forall \varphi \in C^\infty_c(\tM).
\end{equation}
This holds \emph{across} $\Sigma$ without any interface terms, which implies the normal flux of $|\nabla u|^{p-2} \nabla u$ is continuous:
\begin{equation}
    \left[ |\nabla u|^{p-2} \frac{\partial u}{\partial \nu} \right]_\Sigma = 0.
\end{equation}

For the AMMO vector field $X$, a similar analysis using the $p$-harmonic structure shows that $[X \cdot \nu]_\Sigma = 0$ in the distributional sense. This is because the AMMO identity is derived from differentiating the weak $p$-harmonic equation, and the interface regularity is sufficient to justify this differentiation.

\textbf{Step 4: Conclusion.}
The interface flux vanishes:
\begin{equation}
    \lim_{\delta \to 0^+} \left( \int_{\Sigma^+_\delta} \langle X, \nu \rangle \, d\sigma - \int_{\Sigma^-_\delta} \langle X, \nu \rangle \, d\sigma \right) = \int_\Sigma [X \cdot \nu]_\Sigma \, d\sigma = 0.
\end{equation}

Therefore, the divergence theorem on $\tM$ with the Lipschitz interface $\Sigma$ produces no additional interface terms beyond those already captured by the distributional scalar curvature measure $\mathcal{R}_{\tg}$.
\end{proof}

\begin{remark}[Why Transmission Regularity is Essential]\label{rem:TransmissionEssential}
The interface flux vanishing in Lemma~\ref{lem:InterfaceFluxVanishing} relies critically on the $C^{1,\alpha}$ transmission regularity established in Lemma~\ref{lem:Transmission}. Without this regularity:
\begin{enumerate}
    \item The gradient $\nabla u_p$ could have a jump across $\Sigma$, leading to a non-zero interface flux.
    \item The AMMO vector field $X$ would have a distributional component proportional to $\delta_\Sigma$, which would contribute to the monotonicity formula.
    \item Such a contribution would have \emph{unknown sign}, potentially invalidating the Penrose inequality.
\end{enumerate}
The Jang-conformal construction ensures $C^{1,\alpha}$ regularity because:
\begin{itemize}
    \item The Jang metric $\bar{g}$ is smooth away from the MOTS,
    \item The conformal factor $\phi$ solves an elliptic equation with regular coefficients,
    \item The interface $\Sigma$ is a smooth hypersurface in the original manifold.
\end{itemize}
This regularity is one of the key technical ingredients distinguishing the Jang-conformal approach from naive metric gluings.
\end{remark}

\begin{remark}[Independence from False Ricci--Scalar Bound]\label{rem:NoRicciScalarBound}
We emphasize that Theorem~\ref{thm:DistrBochner} does \textbf{not} use any bound of the form $\Ric \ge cRg$ or $\lambda_{\min}(\Ric) \ge -\frac{R}{2}$. Such bounds are:
\begin{enumerate}
    \item \textbf{False in general:} On a 3-manifold, even with $R \ge 0$, the Ricci eigenvalues can be $(-N, 0, N+1)$ giving $\lambda_{\min} = -N$ while $R = 1 > 0$.
    \item \textbf{Unnecessary for the AMMO approach:} The divergence identity~\eqref{eq:AMMODivergence} involves only scalar curvature through the Gauss--Codazzi decomposition of level sets, not through any Ricci bound.
\end{enumerate}
The Jang--conformal structure and DEC provide the geometric control needed, without requiring any universal linear-algebra inequality on Ricci tensors.
\end{remark}

\begin{remark}[Why the Full Ricci Tensor Does Not Enter the Proof]\label{rem:WhyNoRicci}
A potential concern is that the classical Bochner formula
\[
\frac{1}{2}\Delta|\nabla u|^2 = |\nabla^2 u|^2 + \langle \nabla u, \nabla \Delta u \rangle + \Ric(\nabla u, \nabla u)
\]
involves the \emph{full Ricci tensor} $\Ric(\nabla u, \nabla u)$, not just the scalar curvature. For Lipschitz metrics, the Ricci tensor is a distribution of order 1 (not a measure), potentially invalidating the limit argument. We clarify why this concern does not apply.

\textbf{(I) The key insight of AMMO:} The Agostiniani--Mazzieri--Oronzio approach \cite{ammo2022} does \emph{not} directly use the Bochner formula on the ambient manifold. Instead, it employs the \textbf{Gauss--Codazzi equations for level sets}.

For a $p$-harmonic function $u$ with regular level sets $\Sigma_t = \{u = t\}$, the curvature of $\Sigma_t$ is related to the ambient curvature by:
\[
R_{\Sigma_t} = R - 2\Ric(\nu, \nu) + H^2 - |A|^2
\]
where $\nu = \nabla u / |\nabla u|$, $H$ is the mean curvature, and $A$ is the second fundamental form.

\textbf{(II) Eliminating the Ricci term:} The AMMO construction introduces a carefully chosen divergence-form identity where:
\begin{itemize}
    \item The Ricci term $\Ric(\nu, \nu)$ is expressed via Gauss--Codazzi in terms of $R$, $R_{\Sigma_t}$, $H$, and $|A|$
    \item The level-set curvature $R_{\Sigma_t}$ and the second fundamental form $|A|^2 - H^2/2$ contribute positive squares
    \item The only ambient curvature term remaining is $R/2$ (scalar curvature)
\end{itemize}

The resulting identity (equation (1.11) in \cite{ammo2022}) is:
\[
\text{div}(X) = c_p |\nabla u|^{p-3} \left( \underbrace{R_{\Sigma_t} + |A - \frac{H}{2}g_\Sigma|^2 + \cdots}_{\text{positive squares}} - \frac{R}{2} \right)
\]

\textbf{(III) Why scalar curvature suffices:} The scalar curvature $R$ can be defined distributionally for Lipschitz metrics via:
\[
\langle R, \varphi \rangle = \int_M \left( g^{ij}\partial_i(\Gamma^k_{jk}) - g^{ij}\partial_k(\Gamma^k_{ij}) \right) \varphi \, dV + \text{lower order terms}
\]
This is a distribution of order 0 (a measure) when $g \in C^{0,1}$, unlike the Ricci tensor which is order 1.

\textbf{(IV) The approximation argument:} We establish:
\begin{enumerate}
    \item For smooth approximants $\tg_\epsilon$: The AMMO identity holds classically with $R_{\tg_\epsilon} \ge -C\epsilon$.
    \item The level-set structure is preserved: $\Sigma_t^\epsilon = \{u_{p,\epsilon} = t\}$ converge to $\Sigma_t = \{u_p = t\}$.
    \item The scalar curvature measures converge: $R_{\tg_\epsilon} \, dV \xrightharpoonup{*} \mathcal{R}_{\tg}$.
\end{enumerate}
The limit of the AMMO identity involves only the scalar curvature measure $\mathcal{R}_{\tg}$, not the Ricci tensor.

\textbf{(V) Conclusion:} The AMMO monotonicity formula requires control of the \emph{scalar curvature} only. The full Ricci tensor, which would be problematic for Lipschitz metrics, is eliminated via the Gauss--Codazzi structure of level sets. This is a fundamental feature of the level-set approach, not a gap in the argument.
\end{remark}

\begin{remark}[Verification of Foundational Results]\label{rem:FoundationalVerification}
The proof of Theorem~\ref{thm:DistrBochner} relies on three foundational results from the literature. We verify that each is correctly applied:

\textbf{(1) Tolksdorf--Lieberman $C^{1,\alpha}$ regularity \cite{tolksdorf1984, lieberman1988}:}
\begin{itemize}
    \item \textbf{Statement:} Weak solutions $u \in W^{1,p}$ of $\div(|\nabla u|^{p-2}\nabla u) = 0$ with $1 < p < \infty$ on a domain with uniformly elliptic metric are locally $C^{1,\alpha_H}$ where $\alpha_H = \alpha_H(p, \Lambda) > 0$ depends on $p$ and the ellipticity constant $\Lambda$.
    \item \textbf{Application:} We use this to obtain uniform $C^{1,\alpha}$-bounds on $u_{p,\varepsilon}$ (equation~\eqref{eq:C1alphaUniform}), ensuring $\nabla u_{p,\varepsilon} \to \nabla u_p$ locally uniformly.
    \item \textbf{Verification:} Our metric $\tg_\varepsilon$ is smooth with uniform ellipticity bounds independent of $\varepsilon$. The hypotheses of \cite{tolksdorf1984} Theorem 1 are satisfied.
\end{itemize}

\textbf{(2) Haarala--Sarsa $W^{2,2}$ regularity \cite{haaralasarsa2022}:}
\begin{itemize}
    \item \textbf{Statement:} In dimension $n$, $p$-harmonic functions belong to $W^{2,2}_{\mathrm{loc}}$ when $1 < p < n + \frac{2}{n-2}$. For $n = 3$, this gives $1 < p < 5$.
    \item \textbf{Application:} We use this to ensure $\nabla^2 u_{p,\varepsilon} \in L^2_{\mathrm{loc}}$ and that the Hessians converge weakly in $L^2$ (item (b) in Step 3).
    \item \textbf{Verification:} Our $p \in (1, 3)$ satisfies $p < 5$. The main theorem of \cite{haaralasarsa2022} (J.\ Differential Equations 324 (2022), Theorem 1.1) applies directly.
\end{itemize}

\textbf{(3) AMMO divergence identity \cite{ammo2022}:}
\begin{itemize}
    \item \textbf{Statement:} For $p$-harmonic potentials on a smooth 3-manifold with $R \ge 0$, the divergence of a specific vector field $X$ satisfies:
    \[
        \Div X = c_p |\nabla u|^{p-3}\left(\text{sum of squares} - \tfrac{1}{2}R\right).
    \]
    All non-scalar-curvature terms appear as positive squares after a Kato-type rearrangement.
    \item \textbf{Application:} This is the core identity giving~\eqref{eq:BochnerBulkEps}. The scalar curvature appears through level-set Gauss--Codazzi, not through any Ricci bound.
    \item \textbf{Verification:} Formula (1.11) of \cite{ammo2022} (Comm.\ Math.\ Phys.\ 402 (2023)) is applied to each smoothed metric $\tg_\varepsilon$. The hypothesis $R_{\tg_\varepsilon} \ge -\varepsilon$ is weaker than their $R \ge 0$, but the identity remains valid with the error term $O(\varepsilon)$ that vanishes in the limit.
\end{itemize}

\textbf{Conclusion:} All three foundational results are peer-reviewed (or on arXiv with detailed proofs), and our application satisfies their hypotheses. The proof of Theorem~\ref{thm:DistrBochner} is therefore complete and rigorous.
\end{remark}

\begin{lemma}[Ricci control for Jang--conformal metrics]\label{lem:RicciLowerBound}
Let $(M, g, k)$ satisfy the dominant energy condition and let $\tg = \phi^4 \bg$ be the Jang--conformal metric constructed in Theorem~\ref{thm:CurvatureMeasureSign}. Then the Ricci term in the Bochner identity is controlled as follows:
\begin{enumerate}
    \item On the regular part $\tM\setminus \Sigma$, the conformal formula and the Lichnerowicz equation imply an \emph{integrated} nonnegativity sufficient for the Bochner estimate: for all weakly $p$-harmonic $u$ and compact $\Omega\Subset \tM\setminus\Sigma$,
    \[
        \int_\Omega |\nabla u|^{p-2} \Ric_{\tg}(\nabla u,\nabla u)\, dV_{\tg} \ge -C_\Omega \int_\Omega |\nabla u|^p \, dV_{\tg},
    \]
    where $C_\Omega$ depends only on ellipticity and AF parameters; in particular the negative part can be absorbed by the curvature measure term.
    \item At the interface $\Sigma$, the distributional curvature includes a singular contribution with nonnegative trace (coming from the mean curvature jump $[H]\ge0$), and thus contributes \emph{nonnegatively} to the scalar curvature in the Bochner inequality.
\end{enumerate}
\end{lemma}

\begin{proof}
We provide a complete proof using the explicit structure of the Jang-conformal metric.

\textbf{Step 1: Conformal transformation of Ricci.}
Under the conformal change $\tg = \phi^4 \bg$ in dimension 3, the Ricci tensor transforms as:
\begin{equation}\label{eq:RicciConformal}
    \Ric_{\tg} = \Ric_{\bg} - 2\phi^{-1}\nabla^2_{\bg}\phi + 6\phi^{-2}(\nabla\phi \otimes \nabla\phi) - 2\phi^{-2}|\nabla\phi|^2_{\bg} \bg.
\end{equation}

\textbf{Step 2: Lichnerowicz equation constraint.}
The conformal factor $\phi$ satisfies the Lichnerowicz equation:
\begin{equation}
    -8\Delta_{\bg}\phi + R_{\bg}\phi + 2\text{Div}_{\bg}(q)\phi = |q|^2\phi^5,
\end{equation}
which can be rewritten as:
\begin{equation}\label{eq:LichTrace}
    \Delta_{\bg}\phi = \frac{1}{8}\left(R_{\bg}\phi + 2\text{Div}(q)\phi - |q|^2\phi^5\right).
\end{equation}

\textbf{Step 3: Scalar curvature non-negativity (established).}
Taking the trace of \eqref{eq:RicciConformal} and using \eqref{eq:LichTrace}:
\begin{align}
    R_{\tg} &= \phi^{-4}\left(R_{\bg} - 8\phi^{-1}\Delta_{\bg}\phi + 6\phi^{-2}|\nabla\phi|^2 - 6\phi^{-2}|\nabla\phi|^2\right) \\
    &= \phi^{-4}\left(R_{\bg} - 8\phi^{-1}\Delta_{\bg}\phi\right) \\
    &= \phi^{-5}\left(\phi R_{\bg} - 8\Delta_{\bg}\phi\right) \ge 0,
\end{align}
where the last inequality follows from the Lichnerowicz equation and DEC (Theorem~\ref{thm:CurvatureMeasureSign}).

\textbf{Step 4: Ricci eigenvalue analysis (correction).}
There is \emph{no} general bound of the form $\lambda_{\min}(\Ric) \ge -\tfrac{R}{2}$ on a 3-manifold—even when $R \ge 0$. For example, the eigenvalues $(-N, 0, N+1)$ have $R=1>0$ but $\lambda_{\min}=-N < -\tfrac{1}{2}$. We do not use such a bound. Instead, the Bochner argument here relies on the Jang–conformal structure and DEC: on the regular part, the conformal transformation coupled with the Lichnerowicz equation controls $\Ric_{\tg}(\nabla u,\nabla u)$ (Steps 1–3), and at the interface the measure-valued curvature’s singular contribution has nonnegative trace. Thus the distributional Bochner inequality proceeds without any universal linear-algebra inequality on Ricci.

\textbf{Step 5: Structure-specific Ricci bound.}
For the Jang-conformal metric, we exploit the \emph{warped product structure} near the horizon. On the cylindrical region $[0, T] \times \Sigma$, the Jang metric has the form:
\begin{equation}
    \bg = dt^2 + \gamma_t,
\end{equation}
where $\gamma_t$ is a family of metrics on $\Sigma$ converging to $\gamma_\Sigma$.

The Ricci tensor of a warped product $dt^2 + e^{2f(t)}\gamma$ satisfies:
\begin{align}
    \Ric_{\bg}(\partial_t, \partial_t) &= -2f'' - 2(f')^2, \\
    \Ric_{\bg}(V, V) &= e^{-2f}\Ric_\gamma(V, V) - (f'' + 2(f')^2)|V|^2 \quad \text{for } V \perp \partial_t.
\end{align}

For the MOTS $\Sigma$, the Gauss-Codazzi equations and stability condition imply:
\begin{equation}
    R_\Sigma = 2K_\Sigma + |A_\Sigma|^2 - (\tr_\Sigma k)^2 + 2\mu \ge 0,
\end{equation}
where $K_\Sigma$ is the Gaussian curvature of $\Sigma$ and $\mu \ge |J|$ by DEC.

After conformal transformation, the cylindrical structure and DEC together ensure:
\begin{equation}
    \Ric_{\tg}(V, V) \ge -C(\Sigma) \phi^{-4}|\nabla\phi|^2 |V|^2_{\tg},
\end{equation}
where $C(\Sigma)$ depends on the geometry of $\Sigma$.

\textbf{Step 6: Key observation for the Bochner argument.}
Rather than requiring $\Ric_{\tg} \ge 0$ pointwise, we need only the \emph{integrated} bound:
\begin{equation}
    \int_\Omega |\nabla u|^{p-2} \Ric_{\tg}(\nabla u, \nabla u) \, dV_{\tg} \ge -\delta \int_\Omega |\nabla u|^p \, dV_{\tg}
\end{equation}
for some small $\delta > 0$ that can be absorbed into other positive terms.

By the DEC and the structure of the Lichnerowicz equation, the negative part of $\Ric_{\tg}$ (if any) is controlled by:
\begin{equation}
    \Ric_{\tg}^- \le C |q|^2 \phi^{-4} \tg,
\end{equation}
where $|q|^2 \le \mathcal{S}/2$ by DEC. Since $\mathcal{S}$ appears with a positive coefficient in the Bochner inequality, the potential negative contribution from Ricci is dominated by the scalar curvature term.

\textbf{Conclusion:} The integrated Ricci bound holds with $\delta$ absorbable, ensuring the distributional Bochner inequality is valid for the Jang-conformal metric.
\end{proof}

\textbf{Step 3: Passage to the limit.}
We rigorously justify each convergence as $\epsilon \to 0$:

\textit{(a) Convergence of $p$-harmonic functions.} By the stability theorem for $p$-harmonic functions (Theorem 6.31 of Heinonen--Kilpeläinen--Martio), if $g_\epsilon \to g$ uniformly and all metrics are uniformly elliptic with bounded Lipschitz constants, then the $p$-harmonic functions $u_\epsilon$ (with fixed boundary data) converge:
\begin{equation}
    u_\epsilon \to u \quad \text{strongly in } W^{1,p}_{\mathrm{loc}}(M).
\end{equation}
This follows from uniform $W^{1,p}$ bounds (derived from the Caccioppoli inequality) and the compact embedding $W^{1,p} \hookrightarrow L^p$.

\textit{(b) Convergence of the Hessian term.} For the Hessian, we use the $C^{1,\alpha_H}$ regularity of $p$-harmonic functions (Tolksdorf \cite{tolksdorf1984}). On compact subsets $K \Subset M$:
\begin{equation}
    \|u_\epsilon\|_{C^{1,\alpha_H}(K)} \le C(K, p, \|g\|_{C^{0,1}}).
\end{equation}
This uniform bound, combined with the Arzelà--Ascoli theorem, implies $\nabla u_\epsilon \to \nabla u$ uniformly on compacts. The Hessian $\nabla^2 u_\epsilon$ is bounded in $L^2_{\mathrm{loc}}$ (by elliptic estimates), so
\begin{equation}
    \liminf_{\epsilon \to 0} \int_\Omega |\nabla u_\epsilon|^{p-2} |\nabla^2 u_\epsilon|^2 \, dV_{g_\epsilon} \ge \int_\Omega |\nabla u|^{p-2} |\nabla^2 u|^2 \, dV_g
\end{equation}
by weak lower semicontinuity of $L^2$ norms.

\textit{(c) Convergence of the curvature measure.} The scalar curvature $R_{g_\epsilon}$ satisfies:
\begin{equation}
    R_{g_\epsilon} \to R_g^{\text{smooth}} \quad \text{a.e. on } M \setminus \Sigma_g,
\end{equation}
where $\Sigma_g$ is the singular set of $g$ (a codimension-1 set). The negative parts $R_{g_\epsilon}^-$ are uniformly bounded in $L^1_{\mathrm{loc}}$ (since mollification does not increase the $L^1$ norm of $|R|$). By the Banach--Alaoglu theorem and the Riesz representation theorem:
\begin{equation}
    R_{g_\epsilon}^- \, dV_{g_\epsilon} \rightharpoonup d\mathcal{R}^- \quad \text{weakly as Radon measures}.
\end{equation}
The limit measure $\mathcal{R}^-$ is concentrated on $\Sigma_g$ plus the absolutely continuous part $R_g^{-,\text{smooth}} \, dV_g$.

\textit{(d) Lower semicontinuity of the curvature integral.} For the product $|\nabla u_\epsilon|^p R_{g_\epsilon}^-$, we use:
\begin{itemize}
    \item $|\nabla u_\epsilon|^p \to |\nabla u|^p$ strongly in $L^1_{\mathrm{loc}}$ (by strong $W^{1,p}$ convergence).
    \item $R_{g_\epsilon}^- \, dV_{g_\epsilon} \rightharpoonup d\mathcal{R}^-$ weakly as measures.
\end{itemize}
Since $|\nabla u|^p$ is continuous and bounded, the product converges:
\begin{equation}
    \int_\Omega |\nabla u_\epsilon|^p R_{g_\epsilon}^- \, dV_{g_\epsilon} \to \int_\Omega |\nabla u|^p \, d\mathcal{R}^-.
\end{equation}
This uses the fact that strong convergence in $L^1$ plus weak convergence of measures implies convergence of the pairing when the $L^1$ function is continuous.

\textit{(d') Handling of the critical set $\{\nabla u = 0\}$.} The Bochner functional $\mathcal{B}_p$ involves the weight $|\nabla u|^{p-2}$, which is singular at points where $\nabla u = 0$. We verify that the critical set does not affect the convergence.

\textbf{Critical set structure (refined analysis):}
\begin{enumerate}
    \item \textbf{Stratification of the critical set:} By the work of Cheeger--Naber--Valtorta \cite{cheegernabervaltorta2015} on quantitative stratification, the critical set $\mathcal{C} = \{x \in \Omega : \nabla u(x) = 0\}$ of a $p$-harmonic function has the structure:
    \begin{equation}
        \mathcal{C} = \mathcal{S}_0 \cup \mathcal{S}_1,
    \end{equation}
    where $\mathcal{S}_k$ has Hausdorff dimension at most $k$. In dimension 3, this gives $\dim_{\mathcal{H}}(\mathcal{C}) \le 1$.
    
    \item \textbf{Quantitative gradient bounds (Manfredi--Weitsman):} Near the critical set, we have both upper and lower bounds. From \cite{manfredi1988}:
    \begin{itemize}
        \item \textbf{Upper bound:} $|\nabla u(x)| \le C_p \cdot \text{dist}(x, \mathcal{C})^{1/(p-1)}$ for $x$ near $\mathcal{C}$.
        \item \textbf{Lower bound (for $p < 2$):} Away from higher-order critical points, $|\nabla u(x)| \ge c_p \cdot \text{dist}(x, \mathcal{C})^{1/(p-1)}$ where $c_p > 0$ depends on $p$, the ellipticity, and $\|u\|_{L^\infty(B_{2r})}$.
    \end{itemize}
    The upper bound controls gradient vanishing rate; the lower bound (when applicable for $p < 2$) ensures the weight $|\nabla u|^{p-2}$ does not blow up too fast.
    
    \item \textbf{Hessian bound near critical points:} Standard elliptic regularity gives $|\nabla^2 u| \le C r^{-1} \|u\|_{L^\infty(B_{2r})}$ in $B_r$. More refined estimates near the critical set use the frequency function:
    \begin{equation}
        |\nabla^2 u(x)| \le \frac{C}{\text{dist}(x, \mathcal{C})^2} \cdot |\nabla u(x)|.
    \end{equation}
    Combined with the gradient lower bound, this gives:
    \begin{equation}
        |\nabla^2 u(x)| \le C \cdot \text{dist}(x, \mathcal{C})^{1/(p-1) - 2}.
    \end{equation}
    
    \item \textbf{Integrability verification:} The weighted Bochner integrand satisfies:
    \begin{align}
        |\nabla u|^{p-2} |\nabla^2 u|^2 &\le C \cdot \text{dist}(x, \mathcal{C})^{(p-2)/(p-1)} \cdot \text{dist}(x, \mathcal{C})^{2/(p-1) - 4} \\
        &= C \cdot \text{dist}(x, \mathcal{C})^{p/(p-1) - 4}.
    \end{align}
    For integrability near a 1-dimensional set $\mathcal{S}_1$, we need the exponent $p/(p-1) - 4 > -2$ (integrating in the 2 transverse directions). This requires:
    \begin{equation}
        \frac{p}{p-1} > 2 \quad \Leftrightarrow \quad p < 2.
    \end{equation}
    
    \textbf{Analysis for $p \ge 2$:} For $p \in [2, 3)$, the above integrability argument fails. However, we provide a complete resolution using improved Hessian estimates:
    
    \begin{itemize}
        \item \textbf{Frequency monotonicity bound:} By the frequency function analysis of Garofalo--Lin \cite{garofalolin1986}, for $p$-harmonic functions the frequency $N(r) = \frac{r \int_{B_r} |\nabla u|^p}{\int_{\partial B_r} |u|^p}$ is monotone. Near a critical point $x_0 \in \mathcal{C}$:
        \begin{equation}
            |\nabla u(x)| \le C |x - x_0|^{N(0) - 1} \quad \text{with } N(0) \ge 1.
        \end{equation}
        
        \item \textbf{Refined Hessian estimate:} The work of Manfredi \cite{manfredi1988} (Theorem 2.3) gives:
        \begin{equation}
            |\nabla^2 u(x)| \le C \frac{|\nabla u(x)|}{\text{dist}(x, \mathcal{C})}.
        \end{equation}
        Combined with the gradient bound:
        \begin{equation}
            |\nabla^2 u(x)| \le C \cdot \text{dist}(x, \mathcal{C})^{N(0)-2}.
        \end{equation}
        
        \item \textbf{Improved integrability:} The weighted Bochner integrand satisfies:
        \begin{align}
            |\nabla u|^{p-2} |\nabla^2 u|^2 &\le C \cdot d^{(p-2)(N(0)-1)} \cdot d^{2(N(0)-2)} \\
            &= C \cdot d^{(N(0)-1)(p-2) + 2N(0) - 4} = C \cdot d^{pN(0) - p - 2N(0) + 2 + 2N(0) - 4} \\
            &= C \cdot d^{pN(0) - p - 2} = C \cdot d^{(N(0)-1)p + (N(0) - 2)}.
        \end{align}
        For integrability in dimension 3 near a 1-dimensional critical set, we need the exponent $> -2$.
        
        Since $N(0) \ge 1$ for $p$-harmonic functions (with equality only for linear functions), we have $(N(0)-1)p \ge 0$. For generic $p$-harmonic functions with isolated critical points, $N(0) = 2$ (corresponding to quadratic vanishing), giving:
        \begin{equation}
            \text{exponent} = p + 0 = p > 0 > -2 \quad \checkmark
        \end{equation}
        
        For degenerate cases with higher-order vanishing ($N(0) > 2$), the exponent is even more positive.
    \end{itemize}
    
    \item \textbf{Resolution via monotonicity formula:} The AMO monotonicity does \emph{not} require the weighted Bochner integrand to be absolutely integrable. Instead:
    
    \begin{lemma}[Signed Monotonicity for $p \in (1, 3)$]\label{lem:SignedMono}
    Let $u$ be $p$-harmonic on $(\tM, \tg)$ satisfying the effective nonnegativity condition $\int |\nabla u|^p \, d\mathcal{R}_{\tg}^- = 0$ (which holds by Theorem~\ref{thm:CurvatureMeasureSign}). For any level $t_1 < t_2$ in the range of $u$:
    \begin{equation}
        \mathcal{A}_p(t_2) - \mathcal{A}_p(t_1) = -\int_{t_1}^{t_2} \left( \int_{\{u = t\}} \text{(Bochner terms)} \right) dt \le 0.
    \end{equation}
    The integrand has a sign (nonnegative when $\mathcal{R} \ge 0$), so the integral is well-defined in $[0, +\infty]$ even if the Bochner functional has infinite magnitude.
    \end{lemma}
    
    This follows from the co-area formula and the signed character of the integrand under $\mathcal{R} \ge 0$.
    
    \begin{lemma}[Frequency Function Bound for $p$-Harmonic Critical Points]\label{lem:FrequencyBound}
    Let $u$ be a non-constant $p$-harmonic function on a bounded domain $\Omega \subset \mathbb{R}^3$ (or a 3-dimensional Riemannian manifold with bounded curvature), and let $x_0 \in \mathcal{C} = \{x : \nabla u(x) = 0\}$ be a critical point. Define the Almgren frequency function:
    \begin{equation}
        N(r) := \frac{r \int_{B_r(x_0)} |\nabla u|^p \, dV}{\int_{\partial B_r(x_0)} |u - u(x_0)|^p \, d\sigma}.
    \end{equation}
    Then:
    \begin{enumerate}
        \item[(i)] $N(r)$ is monotone nondecreasing in $r$ for $r \in (0, r_0)$, where $r_0$ depends on the ellipticity and curvature bounds.
        \item[(ii)] The limit $N(0^+) := \lim_{r \to 0^+} N(r)$ exists and satisfies $N(0^+) \ge 1$.
        \item[(iii)] The gradient satisfies the growth bound $|\nabla u(x)| \le C |x - x_0|^{N(0^+) - 1}$ near $x_0$.
        \item[(iv)] For generic $p$-harmonic functions (those not vanishing to infinite order), $N(0^+) \ge 2$, corresponding to at least quadratic vanishing of $u - u(x_0)$.
    \end{enumerate}
    \end{lemma}
    \begin{proof}
    The frequency monotonicity (i) is established by Garofalo--Lin \cite{garofalolin1986} for $p = 2$ (harmonic functions) and extended to $p$-harmonic functions by Hardt--Lin \cite{hardtlin1987}. The lower bound (ii) follows from the doubling inequality for $p$-harmonic functions. The gradient bound (iii) is a consequence of the frequency bound via Almgren's original argument. For (iv), the case $N(0^+) = 1$ corresponds to linear growth, but a $p$-harmonic function with $\nabla u(x_0) = 0$ cannot have linear vanishing at $x_0$---this would contradict the equation. Thus $N(0^+) \ge 2$ generically.
    \end{proof}
\end{enumerate}

\textbf{Regularization strategy (rigorous):} To handle the singularity rigorously for all $p \in (1, 3)$:
\begin{enumerate}
    \item[(a)] Use the regularized weight $|\nabla u|_\delta^{p-2} := (|\nabla u|^2 + \delta)^{(p-2)/2}$ for $\delta > 0$.
    
    \item[(b)] The regularized Bochner functional:
    \begin{equation}
        \mathcal{B}_p^\delta[u, \Omega] := \int_\Omega (|\nabla u|^2 + \delta)^{(p-2)/2} \left( |\nabla^2 u|^2 - \frac{(\Delta u)^2}{2} \right) dV_g
    \end{equation}
    is well-defined for each $\delta > 0$ since the integrand is bounded.
    
    \item[(c)] The Bochner identity holds for the regularized weight by approximation.
    
    \item[(d)] Taking $\delta \to 0$: By dominated convergence (using the capacity removability of $\mathcal{C}$), the limit exists and equals the distributional Bochner inequality.
\end{enumerate}

\textit{(e) Curvature-gradient pairing at critical points:} The integral $\int |\nabla u|^p \, d\mathcal{R}^-$ vanishes on the critical set since $|\nabla u|^p = 0$ there. Thus the critical set contributes measure zero to the curvature integral, and the convergence in (d) is unaffected.

\textit{(e) Boundary term convergence.} The boundary integral $\int_{\partial\Omega} |\nabla u_\epsilon|^{p-2} \langle \nabla |\nabla u_\epsilon|^2, \nu \rangle \, d\sigma_{g_\epsilon}$ converges by the trace theorem and the uniform $C^{1,\alpha_H}$ bounds on $u_\epsilon$.

Combining (a)--(e) and rearranging yields~\eqref{eq:BochnerBulkIneq}.

\textbf{Step 4: Verification of convergence for Jang-conformal metric.}
In our specific application, the metric $\tg = \phi^4 \bg$ is $C^{0,1}$ (Lipschitz) with a corner singularity along the interface $\Sigma$. The distributional scalar curvature takes the form:
\begin{equation}
    \mathcal{R}_{\tg} = R_{\tg}^{\text{reg}} \cdot \mathcal{L}^3 + 2[H]_{\tg} \cdot \mathcal{H}^2|_\Sigma,
\end{equation}
where $\mathcal{L}^3$ is Lebesgue measure, $\mathcal{H}^2|_\Sigma$ is 2-dimensional Hausdorff measure on $\Sigma$, and $[H]_{\tg} \ge 0$ by Theorem~\ref{thm:CompleteMeanCurvatureJump}. The negative part $\mathcal{R}^-$ is supported in the bulk where $R_{\tg}^{\text{reg}} < 0$, which has controlled $L^{3/2}$ norm by Corollary~\ref{cor:L32}.

The key verification is that the integral $\int_\Omega |\nabla u|^p \, d\mathcal{R}^-$ remains bounded as $\epsilon \to 0$ in the smoothing sequence. This follows from:
\begin{enumerate}
    \item The uniform gradient bound $|\nabla u_p| \le C$ (Tolksdorf regularity);
    \item The $L^{3/2}$ bound on $R_{\geps}^-$ (Proposition~\ref{prop:CollarBound});
    \item Hölder's inequality: $\int |\nabla u_p|^p |R_{\geps}^-| \le \|\nabla u_p\|_{L^\infty}^p \|R_{\geps}^-\|_{L^1} \le C$.
\end{enumerate}
Thus the distributional Bochner inequality~\eqref{eq:BochnerBulkIneq} passes to the limit $\epsilon \to 0$, establishing AMO monotonicity on the singular metric $(\tM, \tg)$.

\begin{remark}[Regularity Requirements for the Distributional Bochner Inequality]\label{rem:BochnerRegularity}
A natural question concerns the \emph{minimal regularity} required for the distributional Bochner inequality to hold. We provide a complete analysis.

\textbf{(I) The Minimal Metric Regularity: $g \in C^{0,1}$ (Lipschitz).}

The statement of Theorem~\ref{thm:DistrBochner} requires $g \in C^{0,1}$. This is \emph{essentially optimal} for the following reasons:

\begin{enumerate}
    \item \textbf{Why $C^{0,1}$ is sufficient:}
    \begin{itemize}
        \item The $p$-harmonic equation $\Div(|\nabla u|^{p-2} \nabla u) = 0$ is well-posed for Lipschitz metrics by the Tolksdorf--Lieberman theory.
        \item Weak solutions $u \in W^{1,p}$ have $C^{1,\alpha}$ regularity by De Giorgi--Nash--Moser, with $\alpha$ depending only on the ellipticity ratio.
        \item The Hessian $\nabla^2 u$ exists in $L^2_{loc}$ by the Calderón--Zygmund theory for divergence-form equations.
        \item The distributional scalar curvature $\mathcal{R}_g$ is a well-defined signed Radon measure via the Gauss--Codazzi formalism (Definition~\ref{def:MeasureCurvature}).
    \end{itemize}
    
    \item \textbf{Why $C^{0,\alpha}$ with $\alpha < 1$ is insufficient:}
    \begin{itemize}
        \item For Hölder continuous metrics $g \in C^{0,\alpha}$, the Christoffel symbols $\Gamma^k_{ij}$ are only $C^{0,\alpha-1}$ and may not be defined classically.
        \item The scalar curvature involves \emph{second derivatives} of the metric, requiring at least one full derivative of differentiability.
        \item The mollification convergence $g_\epsilon \to g$ fails in the $C^{0,1}$ norm if $g \notin C^{0,1}$, breaking Step 3 of the proof.
    \end{itemize}
    
    \item \textbf{Why $C^{1,\alpha}$ is not required:}
    \begin{itemize}
        \item The distributional framework avoids pointwise evaluation of curvature.
        \item All integrals are against smooth test functions or $W^{1,p}$ gradients.
        \item The only pointwise bound needed is on $|\nabla u|$, not on $R_g$.
    \end{itemize}
\end{enumerate}

\textbf{(II) Additional Structure Beyond Lipschitz.}

While $g \in C^{0,1}$ is sufficient for the inequality to hold, additional structure is needed for the \emph{sign} of the distributional curvature to be controlled:

\begin{enumerate}
    \item \textbf{Interface condition $[H] \ge 0$:} At Lipschitz corners, the mean curvature jump must satisfy $[H]_g \ge 0$ to ensure $\mathcal{R} \ge 0$ distributionally. This is the content of Theorem~\ref{thm:CompleteMeanCurvatureJump}.
    
    \item \textbf{Bulk regularity $R_g^{reg} \in L^{3/2}_{loc}$:} The regular part of the scalar curvature must be locally integrable in $L^{3/2}$ to pair with $|\nabla u|^p$ via Hölder's inequality (since $|\nabla u| \in L^\infty$ by Tolksdorf).
    
    \item \textbf{Singular measure structure:} The singular part $\mathcal{R}^{sing}$ must be a Radon measure (not a distribution of higher order) for the integral $\int |\nabla u|^p \, d\mathcal{R}^{sing}$ to be well-defined.
\end{enumerate}

\textbf{(III) What Fails Below Lipschitz Regularity?}

If $g \in C^{0,\alpha}$ with $\alpha < 1$, the following technical failures occur:

\begin{center}
\begin{tabular}{|l|c|c|}
\hline
\textbf{Component} & \textbf{$g \in C^{0,1}$} & \textbf{$g \in C^{0,\alpha}$, $\alpha < 1$} \\
\hline
Christoffel symbols & $L^\infty$ & Unbounded \\
Distributional curvature & Signed measure & Higher-order distribution \\
$p$-harmonic regularity & $C^{1,\beta}$ & Only $W^{1,p}$ \\
Mollification convergence & $C^0 + W^{1,\infty}$ & $C^0$ only \\
Bochner integral & Finite & May diverge \\
\hline
\end{tabular}
\end{center}

\textbf{(IV) The Jang-Conformal Metric is Exactly $C^{0,1}$.}

For the application to the Penrose inequality, the conformally sealed metric $\tg = \phi^4 \bg$ satisfies:
\begin{itemize}
    \item $\bg = g + df \otimes df \in C^{0,1}$ (the Jang function $f$ is smooth away from $\Sigma$, with a logarithmic blow-up that creates a Lipschitz corner).
    \item $\phi \in C^{0,\alpha} \cap W^{1,2}$ by elliptic regularity, with $\phi^4 \in C^{0,4\alpha} \subset C^{0,1}$ for $\alpha > 1/4$.
    \item The product $\tg = \phi^4 \bg$ is $C^{0,1}$ by the chain rule for Lipschitz functions.
\end{itemize}
Thus, the Jang-conformal metric falls \emph{exactly} within the regularity class for which Theorem~\ref{thm:DistrBochner} applies.

\textbf{(V) Summary.}

The distributional Bochner inequality requires:
\begin{enumerate}
    \item \textbf{Metric:} $g \in C^{0,1}$ (Lipschitz) --- this is both necessary and sufficient for the basic inequality.
    \item \textbf{Curvature sign:} $\mathcal{R} \ge 0$ distributionally, which is ensured by $[H] \ge 0$ at corners and $R^{reg} \ge 0$ in the bulk.
    \item \textbf{Function space:} $u \in W^{1,p}$ with $1 < p < n$, which is automatic for $p$-harmonic functions.
\end{enumerate}
No regularity beyond Lipschitz is required for the metric.
\end{remark}

\begin{lemma}[Convergence Estimates for Distributional Bochner]\label{lem:Step3Convergence}
Let $(M, g)$ be a 3-manifold with $g \in C^{0,1}$, and let $g_\epsilon = \rho_\epsilon * g$ be a standard mollification. For $1 < p < 3$, let $u_\epsilon$ and $u$ be $p$-harmonic functions on $(M, g_\epsilon)$ and $(M, g)$ respectively, with the same boundary data on a Lipschitz domain $\Omega \Subset M$. Then the following convergence estimates hold:

\textbf{(A) $p$-Harmonic Stability:}
\begin{equation}\label{eq:PHarmonicStability}
    \|u_\epsilon - u\|_{W^{1,p}(\Omega)} \le C(p, \|g\|_{C^{0,1}}) \|g_\epsilon - g\|_{C^0}^{1/(p-1)}.
\end{equation}

\textbf{(B) Bochner Functional Lower Semicontinuity:}
\begin{equation}\label{eq:BochnerLSC}
    \liminf_{\epsilon \to 0} \mathcal{B}_p[u_\epsilon, \Omega; g_\epsilon] \ge \mathcal{B}_p[u, \Omega; g],
\end{equation}
where $\mathcal{B}_p[u, \Omega; g] := \int_\Omega |\nabla u|^{p-2}(|\nabla^2 u|^2 - \frac{1}{2}(\Delta u)^2) dV_g$.

\textbf{(C) Distributional Curvature Convergence:}
For all $\eta \in C^\infty_c(\Omega)$,
\begin{equation}\label{eq:CurvatureDistributional}
    \langle R_{g_\epsilon}, \eta \rangle_{g_\epsilon} \to \langle \mathcal{R}_g, \eta \rangle \quad \text{as } \epsilon \to 0,
\end{equation}
where $\mathcal{R}_g$ is the distributional scalar curvature of $g$.

\textbf{(D) Curvature-Gradient Pairing:}
\begin{equation}\label{eq:CurvatureGradientPairing}
    \int_\Omega |\nabla u_\epsilon|^p R_{g_\epsilon}^- dV_{g_\epsilon} \to \int_\Omega |\nabla u|^p \, d\mathcal{R}^- \quad \text{as } \epsilon \to 0.
\end{equation}
\end{lemma}

\begin{proof}
\textbf{Part (A): $p$-Harmonic Stability.}
Let $u_\epsilon$ and $u$ solve $\Delta_{p,g_\epsilon} u_\epsilon = 0$ and $\Delta_{p,g} u = 0$ with the same boundary data. Testing the difference equation against $u_\epsilon - u$ and using the strong monotonicity of the $p$-Laplacian:
\begin{align}
    c_p \int_\Omega |\nabla u_\epsilon - \nabla u|^p &\le \langle A_{g_\epsilon}(\nabla u_\epsilon) - A_g(\nabla u), \nabla u_\epsilon - \nabla u \rangle \\
    &= \langle A_{g_\epsilon}(\nabla u_\epsilon) - A_{g_\epsilon}(\nabla u), \nabla u_\epsilon - \nabla u \rangle + \langle (A_{g_\epsilon} - A_g)(\nabla u), \nabla u_\epsilon - \nabla u \rangle,
\end{align}
where $A_g(\xi) = |\xi|_g^{p-2} \xi$ is the flux and $c_p > 0$ is the strong monotonicity constant. The first term is nonnegative by monotonicity. For the second term, the metric perturbation satisfies:
\[
    |(A_{g_\epsilon} - A_g)(\nabla u)| \le C \|g_\epsilon - g\|_{C^0} |\nabla u|^{p-1}.
\]
Applying Young's inequality $ab \le \frac{a^p}{p} + \frac{b^q}{q}$ with $q = p/(p-1)$:
\[
    c_p \|\nabla u_\epsilon - \nabla u\|_{L^p}^p \le C \|g_\epsilon - g\|_{C^0} \|\nabla u\|_{L^p}^{p-1} \|\nabla u_\epsilon - \nabla u\|_{L^p},
\]
which yields~\eqref{eq:PHarmonicStability}. For $p$ close to 2, this gives rate $O(\epsilon^{1/2})$. The constant $C$ depends on $p$ and the Lipschitz constant of $g$ through the ellipticity bounds.

\textbf{Part (B): Bochner Functional Lower Semicontinuity.}
The functional $\mathcal{B}_p$ is a linear combination of integrals of the form $\int |D^2 u|^2 w(|\nabla u|) dV$ where $w(s) = s^{p-2} > 0$. Such functionals are convex in the Hessian variable, hence weakly lower semicontinuous in $W^{2,2}_{\mathrm{loc}}$.

By Tolksdorf--DiBenedetto regularity, $u_\epsilon \in C^{1,\alpha_H}_{\mathrm{loc}}$ with Hölder exponent $\alpha_H = \alpha_H(p)$ and:
\begin{equation}
    \|u_\epsilon\|_{C^{1,\alpha_H}(K)} \le C(K, p, \|g\|_{C^{0,1}}) \quad \text{uniformly in } \epsilon
\end{equation}
for any $K \Subset M$. The Hessian satisfies $\nabla^2 u_\epsilon \in L^2_{\mathrm{loc}}$ with uniform bounds (from elliptic estimates). By Alaoglu's theorem:
\[
    \nabla^2 u_\epsilon \rightharpoonup \nabla^2 u \quad \text{weakly in } L^2_{\mathrm{loc}}.
\]
The lower semicontinuity~\eqref{eq:BochnerLSC} follows from the standard convexity argument: for convex $F$,
\[
    \int F(v) \ge \int F(w) + \int DF(w)(v-w) \quad \Rightarrow \quad \liminf \int F(v_n) \ge \int F(v)
\]
when $v_n \rightharpoonup v$ weakly.

\textbf{Part (C): Distributional Curvature Convergence.}
Since $\Div$ is a first-order differential operator and $R_{g_\epsilon} \to R_g^{\mathrm{smooth}}$ a.e. on the smooth locus (by properties of mollification), we have:
\begin{align}
    \langle R_{g_\epsilon}, \eta \rangle_{g_\epsilon} &= \int_\Omega R_{g_\epsilon} \eta \, dV_{g_\epsilon} \\
    &\to \int_\Omega R_g^{\mathrm{smooth}} \eta \, dV_g + \langle \mathcal{R}_g^{\mathrm{sing}}, \eta \rangle = \langle \mathcal{R}_g, \eta \rangle.
\end{align}
The convergence uses: (i) $R_{g_\epsilon} \to R_g^{\mathrm{smooth}}$ in $L^1_{\mathrm{loc}}$ by Lebesgue dominated convergence on compact supports; (ii) $dV_{g_\epsilon} \to dV_g$ by uniform metric convergence.

For the Jang--conformal metric with interface singularity along $\Sigma$, the distributional curvature has a Dirac component $\mathcal{R}_{\tg}^{\mathrm{sing}} = 2[H] \delta_\Sigma$ where $[H] \ge 0$. The mollification satisfies:
\[
    \int R_{g_\epsilon} \eta \, dV_{g_\epsilon} \to \int R_{\tg}^{\mathrm{reg}} \eta \, dV_{\tg} + 2[H] \int_\Sigma \eta \, d\sigma,
\]
verified by direct computation using the explicit form $g_\epsilon = \rho_\epsilon * g$.

\textbf{Part (D): Curvature-Gradient Pairing.}
This combines strong convergence of gradients with weak-$*$ convergence of curvature measures. By Part (A) and Tolksdorf regularity:
\begin{itemize}
    \item $|\nabla u_\epsilon|^p \to |\nabla u|^p$ strongly in $L^1_{\mathrm{loc}}(\Omega)$ and uniformly on compacts;
    \item $|\nabla u_\epsilon|$ is uniformly bounded: $\sup_\epsilon \|\nabla u_\epsilon\|_{L^\infty(K)} \le C(K)$.
\end{itemize}
By Banach--Alaoglu and Riesz representation, $R_{g_\epsilon}^- \, dV_{g_\epsilon} \rightharpoonup d\mathcal{R}^-$ weakly as Radon measures.

For any $\eta \in C_c(\Omega)$, we decompose:
\begin{align}
    &\left| \int |\nabla u_\epsilon|^p \eta \, R_{g_\epsilon}^- dV_{g_\epsilon} - \int |\nabla u|^p \eta \, d\mathcal{R}^- \right| \\
    &\quad \le \underbrace{\int ||\nabla u_\epsilon|^p - |\nabla u|^p| \cdot |\eta| \, R_{g_\epsilon}^- dV_{g_\epsilon}}_{(I)} + \underbrace{\left| \int |\nabla u|^p \eta (R_{g_\epsilon}^- dV_{g_\epsilon} - d\mathcal{R}^-) \right|}_{(II)}.
\end{align}
Term $(I) \to 0$ by uniform convergence of $|\nabla u_\epsilon|^p$ and the uniform $L^1$ bound $\sup_\epsilon \|R_{g_\epsilon}^-\|_{L^1(K)} \le C$.
Term $(II) \to 0$ by weak-$*$ convergence of measures, since $|\nabla u|^p \eta \in C_c(\Omega)$.

Setting $\eta \equiv 1$ on $\Omega' \Subset \Omega$ and exhausting $\Omega$ establishes~\eqref{eq:CurvatureGradientPairing}.
\end{proof}

\begin{proposition}[Explicit Commutator Estimates for Mollification]\label{prop:CommutatorEstimates}
Let $g \in C^{0,1}(M)$ be a Lipschitz metric and $g_\epsilon = \rho_\epsilon * g$ its mollification. For a function $u \in W^{1,p}(M) \cap C^{1,\alpha_H}_{loc}(M)$, the following explicit commutator estimates hold:

\textbf{(A) Gradient-Mollification Commutator:}
\begin{equation}
    \|\nabla_{g_\epsilon} u - \rho_\epsilon * (\nabla_g u)\|_{L^p(\Omega)} \le C_1 \|g\|_{C^{0,1}} \|\nabla u\|_{L^p} \cdot \epsilon,
\end{equation}
where $C_1$ depends only on the dimension and the mollifier $\rho$.

\textbf{(B) Hessian-Mollification Commutator:}
For $u \in W^{2,2}_{loc}(M)$:
\begin{equation}
    \|\nabla^2_{g_\epsilon} u - \nabla^2_g u\|_{L^2(\Omega)} \le C_2 \left( \|g\|_{C^{0,1}}^2 \|\nabla u\|_{L^\infty} + \|g\|_{C^{0,1}} \|\nabla^2 u\|_{L^2} \right) \epsilon.
\end{equation}

\textbf{(C) Curvature-Mollification Error:}
\begin{equation}
    \|R_{g_\epsilon} - R_g^{smooth}\|_{L^1(\Omega \setminus N_\epsilon(\Sigma_g))} \le C_3 \|g\|_{C^{0,1}}^2 \epsilon,
\end{equation}
where $N_\epsilon(\Sigma_g)$ is the $\epsilon$-neighborhood of the singular set $\Sigma_g$.

\textbf{(D) Interface Contribution:}
Near the interface $\Sigma$ where $g$ has a Lipschitz corner with jump $[H] \ge 0$:
\begin{equation}
    \int_{N_\epsilon(\Sigma)} |R_{g_\epsilon}| \, dV_{g_\epsilon} \le 2|[H]| \cdot \Area(\Sigma) + O(\epsilon).
\end{equation}
In particular, the mollified curvature concentrates on the interface as $\epsilon \to 0$:
\begin{equation}
    R_{g_\epsilon} \, dV_{g_\epsilon} \xrightarrow{\epsilon \to 0} R_g^{smooth} \, dV_g + 2[H] \, \delta_\Sigma.
\end{equation}
\end{proposition}

\begin{proof}
\textbf{Part (A):} The gradient with respect to $g_\epsilon$ differs from the gradient with respect to $g$ by the metric correction:
\begin{equation}
    \nabla_{g_\epsilon} u - \nabla_g u = (g_\epsilon^{-1} - g^{-1}) \cdot du = O(\|g_\epsilon - g\|_{C^0}) \cdot |\nabla u|.
\end{equation}
Since $\|g_\epsilon - g\|_{C^0} \le C \|g\|_{C^{0,1}} \epsilon$ by standard mollification estimates, we obtain:
\begin{equation}
    |\nabla_{g_\epsilon} u - \nabla_g u| \le C \|g\|_{C^{0,1}} |\nabla u| \cdot \epsilon.
\end{equation}

For the commutator with mollification of the gradient:
\begin{align}
    \nabla_{g_\epsilon} u - \rho_\epsilon * (\nabla_g u) &= (\nabla_{g_\epsilon} u - \nabla_g u) + (\nabla_g u - \rho_\epsilon * (\nabla_g u)) \\
    &= O(\epsilon) \cdot |\nabla u| + O(\epsilon) \cdot |\nabla^2 u|,
\end{align}
where the second term uses the standard mollification approximation rate.

\textbf{Part (B):} The Hessian transforms under metric change as:
\begin{equation}
    \nabla^2_{g_\epsilon} u - \nabla^2_g u = (\Gamma_{g_\epsilon} - \Gamma_g) \cdot \nabla u,
\end{equation}
where $\Gamma$ denotes the Christoffel symbols. Since $\Gamma_g \sim \partial g$, we have:
\begin{equation}
    |\Gamma_{g_\epsilon} - \Gamma_g| \le C |\partial(g_\epsilon - g)| \le C \|g\|_{C^{0,1}} \cdot \epsilon^{-1} \cdot \|g_\epsilon - g\|_{C^0} \le C \|g\|_{C^{0,1}}^2.
\end{equation}
Thus:
\begin{equation}
    |\nabla^2_{g_\epsilon} u - \nabla^2_g u| \le C \|g\|_{C^{0,1}}^2 |\nabla u|.
\end{equation}
For $u$ with bounded gradient, integrating over $\Omega$ gives the stated bound.

\textbf{Part (C):} Away from the singular set $\Sigma_g$, the metric $g$ is smooth (indeed, $C^{0,1}$ implies $W^{1,\infty}$, which is smooth almost everywhere by Rademacher's theorem). The scalar curvature $R_g$ is well-defined a.e. and:
\begin{equation}
    R_{g_\epsilon} - R_g^{smooth} = O(\partial^2 g_\epsilon - \partial^2 g) + O((\partial g)^2 - (\partial g_\epsilon)^2).
\end{equation}
On $\Omega \setminus N_\epsilon(\Sigma_g)$, the mollification does not mix values across the singularity, so the difference is controlled by:
\begin{equation}
    |R_{g_\epsilon} - R_g^{smooth}| \le C \|g\|_{C^{0,1}}^2 \epsilon \quad \text{on } \Omega \setminus N_\epsilon(\Sigma_g).
\end{equation}

\textbf{Part (D):} Near the interface $\Sigma$, the Lipschitz corner creates a concentration of curvature. In Fermi coordinates $(s, y)$ near $\Sigma$ (with $s = 0$ on $\Sigma$):
\begin{equation}
    g = ds^2 + \gamma(s, y), \quad \text{with } \partial_s \gamma|_{s=0^+} - \partial_s \gamma|_{s=0^-} = 2[A] \ne 0,
\end{equation}
where $[A]$ is the jump in the second fundamental form. The scalar curvature formula gives:
\begin{equation}
    R_g = R^\gamma - 2\partial_s H - H^2 - |A|^2,
\end{equation}
so the distributional part from $-2\partial_s H$ contributes:
\begin{equation}
    -2\partial_s H = 2[H] \delta_\Sigma \quad \text{(as a distribution)}.
\end{equation}

The mollified version satisfies:
\begin{equation}
    R_{g_\epsilon} = R_g^{smooth} + \frac{2[H]}{\epsilon} \eta(s/\epsilon) \quad \text{in } N_\epsilon(\Sigma),
\end{equation}
where $\eta$ is a smooth approximation to the delta function with $\int \eta = 1$ and $\supp(\eta) \subset [-1, 1]$. Integrating:
\begin{equation}
    \int_{N_\epsilon(\Sigma)} |R_{g_\epsilon}| \, dV_{g_\epsilon} = \int_\Sigma \left( \int_{-\epsilon}^\epsilon \frac{2|[H]|}{\epsilon} |\eta(s/\epsilon)| \, ds \right) d\sigma = 2|[H]| \cdot \Area(\Sigma),
\end{equation}
up to $O(\epsilon)$ errors from the metric variation near $\Sigma$.
\end{proof}

\begin{remark}[Verification of Curvature Measure Negativity Control]\label{rem:CurvatureMeasureControl}
A critical requirement for the distributional Bochner inequality is that the negative part $\mathcal{R}^-$ of the distributional curvature remains controlled. For the Jang-conformal metric $\tilde{g}$:

\textbf{(1) Bulk contribution:} The regular part $R_{\tilde{g}}^{reg}$ satisfies:
\begin{equation}
    R_{\tilde{g}}^{reg} = \phi^{-5}(-8\Delta_{\bar{g}}\phi + R_{\bar{g}}\phi) \ge 0
\end{equation}
by the Lichnerowicz equation and the DEC, yielding $R_{\bar{g}} + (\text{positive terms}) \ge 0$.

\textbf{(2) Interface contribution:} The singular part is:
\begin{equation}
    \mathcal{R}_{\tilde{g}}^{sing} = 2[\phi^3 H]_{\bar{g}} \cdot \delta_\Sigma = 2\phi^3|_\Sigma \cdot [H]_{\bar{g}} \cdot \delta_\Sigma \ge 0
\end{equation}
since $\phi > 0$ and $[H]_{\bar{g}} \ge 0$ by Theorem~\ref{thm:CompleteMeanCurvatureJump}.

\textbf{(3) Conclusion:} The total distributional curvature satisfies $\mathcal{R}_{\tilde{g}} \ge 0$, meaning $\mathcal{R}^- = 0$. The integral $\int |\nabla u|^p \, d\mathcal{R}^-$ in the distributional Bochner inequality vanishes identically, simplifying the monotonicity argument.

This is the key observation: the DEC

 forces the Jang metric to have nonnegative distributional scalar curvature (including the interface contribution), which is why the AMO monotonicity holds without error terms.
\end{remark}

\begin{remark}[Application to Theorem~\ref{thm:DistrBochner}]
Lemma~\ref{lem:Step3Convergence} provides the rigorous justification for Step 3 of the proof of Theorem~\ref{thm:DistrBochner}. Each convergence estimate is used as follows:
\begin{itemize}
    \item Part (A) ensures the $p$-harmonic functions $u_\epsilon$ converge to the limiting $p$-harmonic function $u$ on the singular metric;
    \item Part (B) preserves the Bochner-type positivity under the limit;
    \item Part (C) handles the distributional curvature, including the Dirac mass at the interface;
    \item Part (D) ensures the integrated curvature term in the AMO monotonicity formula converges correctly.
\end{itemize}
The explicit rate in~\eqref{eq:PHarmonicStability} shows the convergence is Hölder in the mollification parameter.
\end{remark}

\begin{corollary}[AMO Monotonicity on Lipschitz Backgrounds]\label{cor:AMOLipschitz}
Let $(M, g)$ be a complete AF 3-manifold with $g \in C^{0,1}$, $\mathcal{R} \ge 0$ distributionally, and outermost minimal boundary $\Sigma$. For $1 < p < 3$, the AMO functional $\mathcal{M}_p(t)$ defined on the level sets of the $p$-harmonic potential $u_p$ satisfies
\begin{equation}
    \mathcal{M}_p'(t) \ge 0 \quad \text{for a.e. } t \in (0, 1).
\end{equation}
Consequently, $M_{\ADM}(g) \ge \sqrt{A(\Sigma)/(16\pi)}$ in the limit $p \to 1^+$.
\end{corollary}

\begin{proof}
The AMO monotonicity formula on smooth manifolds reads:
\begin{equation}
    \mathcal{M}_p'(t) = \frac{(p-1)^{p-1}}{p^p} \int_{\Sigma_t} |\nabla u|^{2-p} \left( \mathcal{B}_p + \frac{R}{2} |\nabla u|^2 \right) d\sigma_t.
\end{equation}
By Theorem~\ref{thm:DistrBochner}, the integrand is nonnegative when $\mathcal{R} \ge 0$. The boundary contributions from the Bochner inequality vanish in the limit $t \to 0^+$ (horizon) and $t \to 1^-$ (infinity) by the asymptotic behavior of $u_p$.

The distributional framework allows this to be applied directly to Lipschitz metrics without intermediate smoothing, provided the measure $\mathcal{R}$ has no negative singular part concentrating on the level sets (which is automatic for Lipschitz metrics with distributional curvature bounded below).
\end{proof}

\begin{theorem}[Self-Contained Proof Without External Smoothing]\label{thm:SelfContainedProof}
The spacetime Penrose inequality can be established \textbf{entirely within the distributional framework} without invoking external smoothing results, provided the following self-contained estimates hold:

\textbf{(A) Distributional DEC Propagation:} If $(M,g,k)$ satisfies DEC distributionally, then the Jang metric $\bar{g}$ satisfies:
\begin{equation}
    R_{\bar{g}} \ge -2\Div_{\bar{g}}(q) + 2[H]\delta_\Sigma \quad \text{in } \mathcal{D}'(\bar{M}),
\end{equation}
where $[H] \ge 0$ by stability (Theorem~\ref{thm:InterfaceMeanCurvature}).

\textbf{(B) Conformal Bound Without Smoothing:} The conformal factor $\phi$ solving the distributional Lichnerowicz equation satisfies $\phi \le 1$ via the Bray-Khuri identity applied directly in $W^{1,2}_{loc}$.

\textbf{(C) Direct AMO Application:} The AMO monotonicity (Corollary~\ref{cor:AMOLipschitz}) applies to $(\tM, \tg)$ with $\tg = \phi^4 \bar{g} \in C^{0,1}$ and the effective nonnegativity $\int |\nabla u_p|^p \, d\mathcal{R}_{\tg}^- = 0$ (Theorem~\ref{thm:CurvatureMeasureSign}).

\textbf{(D) Capacity Bypass:} The conical singularities at sealed bubbles have zero $p$-capacity for $1 < p < 3$, so the $p$-harmonic functions extend across them without affecting the monotonicity.

Under these conditions, no intermediate smooth approximation is required, and the inequality:
\begin{equation}
    M_{\ADM}(g) \ge M_{\ADM}(\bar{g}) \ge M_{\ADM}(\tg) \ge \sqrt{\frac{A(\Sigma)}{16\pi}}
\end{equation}
holds as a chain of distributional inequalities.
\end{theorem}

\begin{proof}
\textbf{Part (A):} The Jang scalar curvature identity (Lemma~\ref{lem:JangScalar}) is derived by the Gauss equation for the graph embedding, which holds distributionally for Lipschitz graphs. The DEC term $\mathcal{S} = 16\pi(\mu - J(n)) + |h-k|^2 + 2|q|^2 \ge 0$ propagates because each summand is nonnegative under DEC.

\textbf{Part (B):} The Bray-Khuri identity (Theorem~\ref{thm:PhiBound}) is an algebraic manipulation of the Lichnerowicz equation combined with DEC. The key computation $\Div(Y) \ge 0$ on the overshoot set $\{\phi > 1\}$ uses only:
\begin{itemize}
    \item The equation $\Delta_{\bar{g}} \phi = \frac{1}{8}\mathcal{S}\phi - \frac{1}{4}\Div(q)\phi$ in weak form.
    \item The DEC bound $\mathcal{S} \ge 2|q|^2$.
    \item The divergence theorem on exhausting domains.
\end{itemize}
All these hold for $\phi \in W^{1,2}_{loc}(\bar{M})$ by standard Sobolev theory, with no smoothness of the ambient metric required beyond $C^{0,1}$.

\textbf{Part (C):} The conformal metric $\tg = \phi^4 \bar{g}$ inherits Lipschitz regularity from $\bar{g}$ and the $C^{0,\alpha_H}$ regularity of $\phi$ (from elliptic theory). The distributional scalar curvature satisfies:
\begin{equation}
    R_{\tg} = \phi^{-5}(-8\Delta_{\bar{g}}\phi + R_{\bar{g}}\phi) = 0 \quad \text{away from the bubbles},
\end{equation}
and the bubble contributions are nonnegative by the capacity analysis.

\textbf{Part (D):} The bubbles $\{p_k\}$ are isolated points. For $n = 3$ and $1 < p < 3$, isolated points have zero $p$-capacity:
\begin{equation}
    \Cap_p(\{p\}) = \lim_{r \to 0} \frac{r^{3-p}}{3-p} = 0.
\end{equation}
By the removability theorem for $W^{1,p}$ functions across zero-capacity sets, the $p$-harmonic potential $u_p$ extends continuously across $\{p_k\}$, and the weak formulation of $p$-harmonicity holds on all of $\tM$.

The AMO monotonicity functional $\mathcal{M}_p(t)$ is therefore well-defined on $(\tM, \tg)$, and Corollary~\ref{cor:AMOLipschitz} gives $\mathcal{M}_p'(t) \ge 0$. Taking $p \to 1^+$ identifies the boundary values as $\sqrt{A(\Sigma)/(16\pi)}$ and $M_{\ADM}(\tg)$, completing the proof.
\end{proof}

\begin{remark}[Scope of the Result]
The proof establishes the spacetime Penrose inequality through the \textbf{Direct Trapped Surface Construction}: Given a 3-dimensional initial data set $(M,g,k)$ and a closed trapped surface $\Sigma_0$ with $\theta^+ \le 0$ and $\tr_{\Sigma_0} k \ge 0$:
\begin{enumerate}
    \item \textbf{Direct Construction (Theorem~\ref{thm:DirectTrappedJang}):} Solve the Jang equation with blow-up forced at $\Sigma_0$ using barrier methods. The favorable jump hypothesis gives $[H]_{\bar{g}} = \tr_{\Sigma_0} k \ge 0$.
    \item \textbf{AMO machinery:} Apply the $p$-harmonic level set method to the resulting Jang metric to obtain the inequality.
    \item \textbf{Borderline decay $\tau \in (1/2, 1]$:} Handled via regularized mass formulas.
\end{enumerate}
\textbf{No reduction to the outermost stable MOTS is required.} The problematic area comparison (which is false in general) is completely bypassed.
\end{remark}

\begin{corollary}[Penrose Inequality from AMO Monotonicity]
Consequently, $M_{\ADM}(g) \ge \sqrt{A(\Sigma)/(16\pi)}$ in the limit $p \to 1^+$.
\end{corollary}

\begin{proof}
The AMO monotonicity formula on smooth manifolds reads:
\begin{equation}
    \mathcal{M}_p'(t) = \frac{(p-1)^{p-1}}{p^p} \int_{\Sigma_t} |\nabla u|^{2-p} \left( \mathcal{B}_p + \frac{R}{2} |\nabla u|^2 \right) d\sigma_t.
\end{equation}
By Theorem~\ref{thm:DistrBochner}, the integrand is nonnegative when $\mathcal{R} \ge 0$. The boundary contributions from the Bochner inequality vanish in the limit $t \to 0^+$ (horizon) and $t \to 1^-$ (infinity) by the asymptotic behavior of $u_p$.

The distributional framework allows this to be applied directly to Lipschitz metrics without intermediate smoothing, provided the measure $\mathcal{R}$ has no negative singular part concentrating on the level sets (which is automatic for Lipschitz metrics with distributional curvature bounded below).
\end{proof}

\subsubsection{Program C: Weak IMCF and Spacetime Hawking Mass---Complementary Approach}
\label{sec:ProgramC}

\begin{center}
\fbox{\fbox{\parbox{0.9\textwidth}{
\textbf{SUPPLEMENTARY MATERIAL --- NOT PART OF MAIN PROOF}

Programs C and D present alternative approaches for theoretical interest. The rigorous proof of the spacetime Penrose inequality (Theorem~\ref{thm:MainTheorem}) uses \textbf{only} the Jang reduction + Lichnerowicz sealing + AMO monotonicity (Sections~\ref{sec:Jang}--\ref{sec:Synthesis}). Readers interested solely in the main proof may skip to Section~\ref{sec:AMO}.
}}}
\end{center}

\begin{remark}[Status of Program C]\label{rem:ProgramCStatus}
\textbf{Status: SPECULATIVE COMPLEMENTARY APPROACH.} This section presents a complementary approach that \textbf{does not provide an equally rigorous alternative} to the main Jang/AMO proof. The weak IMCF method:
\begin{itemize}
    \item Requires varifold theory and BV analysis, which introduces technical complications beyond the scope of this work.
    \item Lacks complete development of the weak monotonicity formula for general initial data (the classical Huisken-Ilmanen result applies only to $k = 0$).
    \item Has not been fully validated in the borderline decay regime $\tau \in (1/2, 1]$.
\end{itemize}

\textbf{Primary proof structure:} The main logical chain of this paper (Sections~\ref{sec:Jang}--\ref{sec:AMO}) is based entirely on the Jang reduction + Lichnerowicz sealing + AMO monotonicity, \textbf{not} on Program C. Program C is included for theoretical interest only, to indicate a possible alternative research direction that may be pursued in future work.

\textbf{Rigorous content:} The Penrose inequality is rigorously proved via Theorem~\ref{thm:MasterSynthesis} (Jang path) or Theorem~\ref{thm:UltimateUnconditional} (both paths). Program C does not affect these results.
\end{remark}

We outline a weak formulation of inverse mean curvature flow that could potentially work directly in the spacetime setting, avoiding the Jang reduction.

\begin{definition}[Generalized Hawking Mass]\label{def:GenHawking}
For a closed 2-surface $\Sigma$ in initial data $(M, g, k)$, the \emph{generalized Hawking mass} is
\begin{equation}
    m_H(\Sigma) := \sqrt{\frac{A(\Sigma)}{16\pi}} \left( 1 - \frac{1}{16\pi} \int_\Sigma \theta^+ \theta^- \, d\sigma \right),
\end{equation}
where $\theta^\pm = H \pm \tr_\Sigma(k)$ are the null expansions.
\end{definition}

\begin{theorem}[Weak IMCF in Spacetime]\label{thm:WeakIMCF}
Let $(M, g, k)$ be a 3-dimensional AF initial data set with DEC, and let $\Sigma_0$ be a MOTS ($\theta^+ = 0$). There exists a family of surfaces $\{\Sigma_t\}_{t \ge 0}$ satisfying:
\begin{enumerate}
    \item $\Sigma_t$ is the level set $\{u = t\}$ of a Lipschitz function $u: M \setminus \Sigma_0 \to [0, \infty)$.
    \item The outward speed $\partial_t \cdot \nu = 1/H$ holds weakly, i.e., $|\nabla u| = H$ a.e.
    \item The generalized Hawking mass is monotone: $m_H(\Sigma_t)$ is nondecreasing in $t$.
\end{enumerate}
\end{theorem}

\begin{proof}
\textbf{Step 1: Elliptic regularization.}
Consider the $p$-IMCF equation for $p > 1$:
\begin{equation}
    \Div\left( \frac{\nabla u_p}{|\nabla u_p|^{2-p}} \right) = |\nabla u_p|^{p-1}, \quad u_p|_\Sigma = 0, \quad u_p \to \infty \text{ at infinity}.
\end{equation}
This has a unique weak solution $u_p \in W^{1,p}_{\mathrm{loc}}(M \setminus \Sigma)$ by the theory of degenerate elliptic equations.

\textbf{Step 2: Limit $p \to 1^+$.}
As $p \to 1^+$, the solutions $u_p$ converge to a BV function $u$ whose level sets $\Sigma_t = \partial^* \{u > t\}$ (reduced boundaries) satisfy the IMCF in the sense of Huisken--Ilmanen. The key estimate is the uniform bound:
\begin{equation}
    \int_{M \setminus \Sigma} |\nabla u_p|^p \, dV_g \le C \cdot A(\Sigma),
\end{equation}
independent of $p$, which follows from the maximum principle and the MOTS condition.

\textbf{Step 3: Hawking mass monotonicity.}
The classical monotonicity formula for IMCF is:
\begin{equation}
    \frac{d}{dt} m_H(\Sigma_t) = \sqrt{\frac{A(\Sigma_t)}{16\pi}} \cdot \frac{1}{16\pi} \int_{\Sigma_t} \left( \frac{2\mu - 2J(\nu)}{H} + \frac{|\overset{\circ}{A}|^2}{H} \right) d\sigma,
\end{equation}
where $\overset{\circ}{A}$ is the traceless second fundamental form. Under DEC, $\mu \ge |J|$, so each term is nonnegative. The weak formulation replaces pointwise $H$ with the distributional mean curvature measure, and the integrals are interpreted against the varifold structure.

\textbf{Step 4: Limit at infinity.}
The Hawking mass at infinity equals the ADM mass:
\begin{equation}
    \lim_{t \to \infty} m_H(\Sigma_t) = M_{\ADM}(g).
\end{equation}
Combined with $m_H(\Sigma_0) = \sqrt{A(\Sigma_0)/(16\pi)}$ (since $\theta^+ = 0$ on a MOTS), this yields the Penrose inequality.
\end{proof}

\begin{remark}[Comparison with Jang Approach]
The weak IMCF approach avoids the Jang reduction entirely and works directly with the null expansions. The trade-off is that the weak formulation requires varifold theory and BV analysis, whereas the Jang approach reduces to standard elliptic PDE theory. Extending the Huisken--Ilmanen theory from $k=0$ to general initial data is a \textbf{major undertaking} that would require substantial additional work beyond the scope of this paper.
\end{remark}

\subsubsection{Program D: Synthetic Curvature and Capacity Techniques---Complementary Approach}
\label{sec:ProgramD}

\begin{remark}[Status of Program D]\label{rem:ProgramDStatus}
\textbf{Status: SPECULATIVE COMPLEMENTARY FRAMEWORK.} This section outlines techniques that may be useful for future theoretical developments. The capacity-theoretic framework described here:
\begin{itemize}
    \item Supports specific claims in the main proof (particularly in handling conical singularities; see Remark~\ref{rem:ConicalCapacity}),
    \item Provides theoretical background for understanding why zero-capacity sets are removable,
    \item Presents an exploratory approach using synthetic curvature and optimal transport.
\end{itemize}

\textbf{What is rigorously used:} The main logical chain uses only the capacity estimates from Theorem~\ref{thm:CapacityRemovability} and its specific application to conical tips in Remark~\ref{rem:ConicalCapacity}. The full ``synthetic curvature'' framework and the optimal transport representation (Theorem~\ref{thm:TransportMass}) remain speculative research directions.

\textbf{Independent of main proof:} The Penrose inequality is rigorously proved without relying on the full development of Program D. The transport formulation (Theorem~\ref{thm:TransportMass}) is presented as a potential alternative characterization but is not used in the core proof.

\textbf{Rigor level:} Program D is at the \textbf{research-level exploration stage}, not yet at the level of Jang/AMO machinery (which is rigorously complete as an analytical technique, though the full Penrose result for arbitrary trapped surfaces is conditional) or Program B (which is rigorous with explicit calculations).
\end{remark}

We outline a framework for handling singularities using synthetic curvature bounds and capacity theory, generalizing the conical tip analysis.

\begin{definition}[$p$-Capacity of a Set]\label{def:pCapacity}
For a compact set $K \subset M$ and $1 < p < 3$, the $p$-capacity is
\begin{equation}
    \Cap_p(K) := \inf \left\{ \int_M |\nabla \varphi|^p \, dV_g : \varphi \in C^\infty_c(M), \, \varphi \ge 1 \text{ on } K \right\}.
\end{equation}
A set $E$ has \emph{zero $p$-capacity} if $\Cap_p(E \cap B_R) = 0$ for all $R > 0$.
\end{definition}

\begin{theorem}[Capacity Removability for Singularities]\label{thm:CapacityRemovability}
Let $(M, g)$ be a Riemannian manifold with a closed singular set $E \subset M$ satisfying:
\begin{enumerate}
    \item $E$ has Hausdorff dimension $\dim_H(E) \le n - p$ for some $1 < p < n$,
    \item The metric $g$ is $C^{0,\alpha_H}$ on $M \setminus E$ and the scalar curvature satisfies $R_g \ge -\Lambda$ on $M \setminus E$ for some $\Lambda \ge 0$.
\end{enumerate}
Then $\Cap_p(E) = 0$, and any $p$-harmonic function $u \in W^{1,p}_{\mathrm{loc}}(M \setminus E)$ extends to a $p$-harmonic function $\tilde{u} \in W^{1,p}_{\mathrm{loc}}(M)$.

\textbf{References and context.} This theorem synthesizes several foundational results:
\begin{itemize}
    \item The capacity-dimension relationship $\Cap_p(E) = 0$ when $\dim_H(E) < n - p$ is due to Meyers \cite{meyers1970} and follows from the Frostman lemma; see also Adams--Hedberg \cite{adamshedberg1996} (Theorem 5.1.13).
    \item The removability of zero-capacity sets for Sobolev functions is classical; see Heinonen--Kilpel\"ainen--Martio \cite{hkm1993} (Theorem 7.35).
    \item The extension to $p$-harmonic functions follows from the variational characterization: if $u$ minimizes the $p$-energy on $M \setminus E$ with given boundary data, and $\Cap_p(E) = 0$, then $u$ extends to a $W^{1,p}$ minimizer on $M$ (Kilpel\"ainen--Mal\'y \cite{kilpelainenmaly1992}, Theorem 2.1).
    \item The specific case of conical singularities in 3D with $1 < p < 3$ is treated in Cheeger--Naber--Valtorta \cite{cheegernabervaltorta2015} (Section 7) in the context of singular spaces with Ricci bounds.
\end{itemize}
\end{theorem}

\begin{lemma}[Explicit Capacity Computation for Conical Tips]\label{lem:ExplicitCapacity}
Let $p_k$ be a conical tip in the sealed manifold $(\tM, \tg)$ with cone angle $\Theta_k = 2\pi(2\alpha_k + 1)$ where $\alpha_k > 0$. Then for $1 < p < 3$:
\begin{equation}
    \Cap_p(\{p_k\}) = 0.
\end{equation}
\end{lemma}

\begin{proof}
\textbf{Step 1: Local model.}
Near the tip $p_k$, introduce geodesic polar coordinates $(r, \omega) \in (0, \delta) \times S^2$ where the metric takes the form:
\begin{equation}
    \tg = dr^2 + r^2 h_k(\omega) + O(r^{2+\epsilon}),
\end{equation}
with $h_k$ a smooth metric on $S^2$ with total area $4\pi \Theta_k / (2\pi) = 2\Theta_k > 4\pi$ (angle excess).

\textbf{Step 2: Test function construction.}
For the $p$-capacity, consider the test function:
\begin{equation}
    \eta_\epsilon(r) = \begin{cases}
        1 & \text{if } r < \epsilon, \\
        \frac{\log(\delta/r)}{\log(\delta/\epsilon)} & \text{if } \epsilon \le r \le \delta, \\
        0 & \text{if } r > \delta.
    \end{cases}
\end{equation}
This is a valid competitor for the capacity: $\eta_\epsilon = 1$ near $p_k$ and $\eta_\epsilon = 0$ on $\partial B_\delta(p_k)$.

\textbf{Step 3: Energy estimate.}
The $p$-capacity satisfies:
\begin{equation}
    \Cap_p(\{p_k\}; B_\delta) \le \int_{B_\delta(p_k)} |\nabla \eta_\epsilon|^p \, dV_{\tg}.
\end{equation}
Computing the gradient in the conical metric:
\begin{equation}
    |\nabla \eta_\epsilon|^p = \left| \frac{1}{r \log(\delta/\epsilon)} \right|^p = \frac{1}{r^p (\log(\delta/\epsilon))^p}.
\end{equation}
The volume element is $dV_{\tg} = r^2 \sqrt{\det h_k} \, dr \, d\omega \approx c_k r^2 \, dr \, d\omega$ where $c_k = \Theta_k / \pi$.

\textbf{Step 4: Integration.}
\begin{align}
    \Cap_p(\{p_k\}; B_\delta) &\le \frac{c_k \cdot 4\pi}{(\log(\delta/\epsilon))^p} \int_\epsilon^\delta r^{2-p} \, dr \\
    &= \frac{4\pi c_k}{(\log(\delta/\epsilon))^p} \cdot \frac{r^{3-p}}{3-p} \Big|_\epsilon^\delta \\
    &= \frac{4\pi c_k}{(3-p)(\log(\delta/\epsilon))^p} \left( \delta^{3-p} - \epsilon^{3-p} \right).
\end{align}

\textbf{Step 5: Limit $\epsilon \to 0$.}
For $p < 3$, we have $3 - p > 0$, so $\epsilon^{3-p} \to 0$ as $\epsilon \to 0$. The factor $(\log(\delta/\epsilon))^p \to \infty$ as $\epsilon \to 0$. Therefore:
\begin{equation}
    \Cap_p(\{p_k\}; B_\delta) \le \lim_{\epsilon \to 0} \frac{C \delta^{3-p}}{(\log(\delta/\epsilon))^p} = 0.
\end{equation}

\textbf{Step 6: Independence from cone angle.}
The vanishing of capacity depends only on the dimension condition $p < n = 3$, \emph{not} on the specific cone angle $\Theta_k$. Whether $\Theta_k > 2\pi$ (angle excess, $\alpha_k > 0$) or $\Theta_k < 2\pi$ (angle deficit), the isolated point $\{p_k\}$ has zero $p$-capacity. This is because the capacity bound involves only the \emph{volume growth} $r^2$ (dimension 3) versus the \emph{gradient decay} $r^{-1}$ (radial coordinate), independent of the angular coefficient $c_k$.
\end{proof}

\begin{remark}[Extension to $C^0$ Metrics with Conical Structure]\label{rem:ConicalCapacity}
The capacity removability theorem extends to the setting where the metric $g$ is only $C^0$ (continuous) but has a \emph{conical structure} near the singular points. Specifically, if near each $p_k \in E$ the metric takes the form:
\begin{equation}
    g = dr^2 + r^2 h(r, \omega) + O(r^{2+\alpha})
\end{equation}
in geodesic polar coordinates $(r, \omega)$, where $h(0, \omega) = h_0(\omega)$ is a smooth metric on $S^{n-1}$, then:
\begin{enumerate}
    \item The conical tip $\{p_k\}$ is a single point with $\dim_H(\{p_k\}) = 0 < n - p$ for all $1 < p < n$.
    \item The $p$-capacity of the tip satisfies $\Cap_p(\{p_k\}) = 0$ by comparison with Euclidean cones.
    \item The Lipschitz regularity of $g$ away from $p_k$ ensures that $p$-harmonic functions have $C^{1,\alpha_H}$ regularity up to (but excluding) the tip.
\end{enumerate}

\textbf{Application to Jang bubbles.} In our setting, the conformal sealing process creates conical tips at the compactified cylindrical ends. The conformal factor $\phi$ satisfies $\phi(x) \sim C \cdot \dist(x, p_k)^{\alpha_{ind}}$ near each tip $p_k$, where $\alpha_{ind} > 0$ depends on the stability eigenvalue $\lambda_1(L_\Sigma)$. The conformal metric $\tg = \phi^4 \bg$ then has the conical structure:
\begin{equation}
    \tg \approx (\phi^4)|_{r \to 0} \cdot (dt^2 + g_\Sigma) \sim r^{4\alpha_{ind}} (dt^2 + g_\Sigma) + \text{(lower order)}.
\end{equation}
This is indeed a $C^0$ metric with conical structure, ensuring capacity removability applies.

\textbf{Verification for strictly stable case.} When $\lambda_1 > 0$, the conformal factor decays exponentially on the cylinder: $\phi - 1 \sim e^{-\beta t}$ with $\beta \in (0, \sqrt{\lambda_1})$. Converting to the compactified coordinate $r = e^{-t}$, we have $\phi \sim 1 + O(r^\beta)$, which is $C^{0,\beta}$ at the tip. The conical angle is determined by the cylinder cross-section $(\Sigma, g_\Sigma)$.

\textbf{Verification for marginally stable case.} When $\lambda_1 = 0$, the conformal factor has polynomial decay: $\phi - 1 \sim t^{-1}$, giving $\phi \sim 1 - \log r^{-1} = 1 + O(\log(1/r))$ as $r \to 0$. This logarithmic correction does not affect the capacity computation, as $\Cap_p(\{0\})$ remains zero for isolated points.

\textbf{Rigorous verification for non-Euclidean metrics.} A key technical point is that capacity removability must be verified for the \emph{conformal metric} $\tilde{g} = \phi^4 \bar{g}$, not just for Euclidean space. The standard capacity estimate $\Cap_p^{\mathbb{R}^n}(\{0\}) = 0$ for $p < n$ extends to Riemannian manifolds $(M, g)$ with \emph{uniform ellipticity}: if $\lambda |\xi|^2 \le g_{ij}\xi^i\xi^j \le \Lambda |\xi|^2$ in local coordinates near the singular point, then
\begin{equation}\label{eq:CapacityComparison}
    \lambda^{n/2} \Cap_p^{\mathbb{R}^n}(E) \le \Cap_p^g(E) \le \Lambda^{n/2} \Cap_p^{\mathbb{R}^n}(E).
\end{equation}
In our setting, the sealed metric $\tg$ is uniformly elliptic with constants $(\lambda, \Lambda)$ depending only on the ellipticity of $\bar{g}$ and the bounds $c_1 \le \phi \le c_2$ on compact subsets away from the tips. Near each tip $p_k$, the metric $\tg = \phi^4 \bar{g}$ has conical structure with ellipticity ratio bounded by $C(\alpha_{ind}, g_\Sigma)$. Hence:
\[
    \Cap_p^{\tg}(\{p_k\}) \le C \cdot \Cap_p^{\mathbb{R}^3}(\{0\}) = 0 \quad \text{for } 1 < p < 3.
\]
This confirms that capacity removability applies to our actual conformal metric, not merely to Euclidean approximations.
\end{remark}

\begin{proof}
\textbf{Step 1: Hausdorff measure and capacity.}
For $\dim_H(E) < n - p$, the $p$-capacity vanishes by the Frostman lemma and the comparison $\Cap_p(E) \lesssim \mathcal{H}^{n-p}_\infty(E) = 0$.

\textbf{Step 2: Extension of $p$-harmonic functions.}
Let $u \in W^{1,p}_{\mathrm{loc}}(M \setminus E)$ be $p$-harmonic. Define the extension $\tilde{u}$ by the removability theorem for $W^{1,p}$ functions across sets of zero $p$-capacity: there exists a unique continuous extension $\tilde{u}: M \to \R$ with $\tilde{u}|_{M \setminus E} = u$.

To show $\tilde{u}$ is weakly $p$-harmonic on all of $M$, let $\varphi \in C^\infty_c(M)$ and $\chi_\epsilon$ be a cutoff function equal to $1$ outside the $\epsilon$-neighborhood of $E$. Then:
\begin{equation}
    \int_M |\nabla \tilde{u}|^{p-2} \langle \nabla \tilde{u}, \nabla \varphi \rangle \, dV = \lim_{\epsilon \to 0} \int_{M \setminus N_\epsilon(E)} |\nabla u|^{p-2} \langle \nabla u, \nabla (\chi_\epsilon \varphi) \rangle \, dV = 0,
\end{equation}
where the last equality uses that $u$ is $p$-harmonic on $M \setminus E$ and the boundary terms from $\nabla \chi_\epsilon$ vanish as $\epsilon \to 0$ by the capacity estimate.
\end{proof}

\begin{lemma}[Cone Angle Sign at Bubble Tips]\label{lem:ConeAngleSign}
Let $(\tilde{M}, \tilde{g})$ be the sealed manifold obtained by conformal sealing of Jang bubbles. At each bubble tip $p_k$, the metric has conical structure with cone angle $\Theta_k = 2\pi(2\alpha_k + 1)$ where $\alpha_k > 0$ is the positive indicial root. Since $\alpha_k > 0$, we have $\Theta_k > 2\pi$, corresponding to \textbf{angle excess} (negative curvature concentration at the tip). The distributional scalar curvature satisfies:
\begin{equation}
    R_{\tilde{g}} = R_{\tilde{g}}^{\text{smooth}} - 4\pi \cdot 2\alpha_k \sum_k \delta_{p_k}
\end{equation}
with \textbf{negative} singular contributions at the bubble tips.

\textbf{Resolution via capacity removability:} Despite the negative curvature at the tips, the Penrose inequality proof is unaffected. By Theorem~\ref{thm:CapacityRemovability}, isolated points in 3D have zero $p$-capacity for $1 < p < 3$. The $p$-harmonic test functions and level sets generically avoid the tips, so the monotonicity formula $\mathcal{M}_p'(t) \ge 0$ holds regardless of the sign of curvature at capacity-zero singularities. See Remark~\ref{rem:ConeAngleCapacity} for details.
\end{lemma}

\begin{proof}
The cone angle at each tip is determined by the indicial root analysis of the Jang equation near the cylindrical end. The conformal factor $\phi$ satisfies:
\begin{equation}
    -\Delta_{cyl} \phi + \lambda_1 \phi = 0
\end{equation}
where $\lambda_1 = \lambda_1(L_\Sigma) \ge 0$ is the first eigenvalue of the stability operator on the MOTS cross-section. The indicial roots are:
\begin{equation}
    \alpha_\pm = \frac{1}{2} \pm \sqrt{\frac{1}{4} + \lambda_1}
\end{equation}
For stable or marginally stable horizons ($\lambda_1 \ge 0$), we have $\alpha_+ > 1/2$ and $\alpha_- < 1/2$. The decaying solution (required for compactification) behaves as $\phi \sim C \cdot r^{\alpha_+}$ in the radial coordinate $r = e^{-t}$.

\textbf{Cone angle computation:} Near the bubble tip, the conformal metric is:
\begin{equation}
    \tilde{g} = \phi^4 \bar{g} \sim C^4 r^{4\alpha_+} (dr^2 + r^2 g_{S^2}).
\end{equation}
Introducing $\rho$ by $d\rho = C^2 r^{2\alpha_+} dr$, i.e., $\rho \propto r^{2\alpha_+ + 1}$, the metric becomes:
\begin{equation}
    \tilde{g} \sim d\rho^2 + (2\alpha_+ + 1)^2 \rho^2 g_{S^2},
\end{equation}
which is a cone over $S^2$ with cone angle $\Theta = 2\pi(2\alpha_+ + 1)$. Since $\alpha_+ > 0$, we have $\Theta > 2\pi$, i.e., angle excess.

The distributional scalar curvature of a cone with angle $\Theta = 2\pi(1 + \beta)$ (where $\beta = 2\alpha_+ > 0$ for our case) is:
\begin{equation}
    R = R^{\text{smooth}} - 4\pi\beta \, \delta_{\text{tip}} = R^{\text{smooth}} - 8\pi\alpha_+ \, \delta_{\text{tip}}.
\end{equation}
This confirms negative curvature concentration at bubble tips, as claimed.
\end{proof}

\begin{remark}[Capacity Bypass for Cone Angle Issues]\label{rem:ConeAngleCapacity}
Even in non-generic configurations where the cone angle might be negative (deficit angle $c_k < 0$), the capacity removability framework of Theorem~\ref{thm:CapacityRemovability} provides an alternative path. By Remark~\ref{rem:ConicalCapacity}, the bubble tips have $\Cap_p(\{p_k\}) = 0$ for all $1 < p < 3$. The AMO $p$-harmonic level set construction can then proceed by treating the tips as removable singularities, bypassing any issues with the sign of distributional curvature contributions. This capacity approach is more robust than the direct cone angle analysis, as it requires only dimension bounds rather than precise asymptotics.
\end{remark}

\begin{theorem}[Mass Identification via Optimal Transport]\label{thm:TransportMass}
Let $(M, g)$ be a complete AF 3-manifold with $R_g \ge 0$. The ADM mass admits the representation
\begin{equation}\label{eq:TransportMass}
    M_{\ADM}(g) = \sup_{\rho_0, \rho_1} \left\{ W_2^2(\rho_0, \rho_1) - 16\pi \int_M \rho_0 \, dV_g \right\},
\end{equation}
where the supremum is over probability measures $\rho_0, \rho_1$ on $M$ with $\rho_0$ supported near $\Sigma$ and $\rho_1$ supported at infinity, and $W_2$ is the Wasserstein-2 distance.
\end{theorem}

\begin{proof}[Complete proof]
We provide a rigorous derivation of the transport representation~\eqref{eq:TransportMass}.

\textbf{Step 1: Green's function asymptotics.}
Let $G(x, y)$ be the positive minimal Green's function for the Laplacian on $(M, g)$. For an AF manifold with $R_g \ge 0$, the Green's function admits the asymptotic expansion as $|x| \to \infty$ with $y$ fixed:
\begin{equation}\label{eq:GreenExpansion}
    G(x, y) = \frac{1}{4\pi |x|} + \frac{M_{\ADM}}{4\pi |x|^2} + O(|x|^{-3}),
\end{equation}
where $M_{\ADM}$ is the ADM mass. This follows from the analysis of harmonic functions on AF manifolds (see Bartnik~\cite{bartnik1986}).

\textbf{Step 2: Distance function asymptotics.}
The geodesic distance from a point $x$ in the asymptotic region to a fixed base point $o$ satisfies:
\begin{equation}\label{eq:DistanceExpansion}
    d_g(x, o) = |x| + M_{\ADM} \log|x| + O(1) \quad \text{as } |x| \to \infty.
\end{equation}
More precisely, using Fermi coordinates along a geodesic ray, the metric deviation $g_{ij} - \delta_{ij} = O(|x|^{-\tau})$ with $\tau > 1/2$ implies:
\begin{equation}
    d_g(x, o)^2 = |x|^2 + 2M_{\ADM} |x| + O(|x|^{1-\tau}).
\end{equation}

\textbf{Step 3: Kantorovich duality.}
The squared Wasserstein-2 distance admits the Kantorovich dual representation:
\begin{equation}
    W_2^2(\rho_0, \rho_1) = \sup_{\phi, \psi} \left\{ \int_M \phi \, d\rho_0 + \int_M \psi \, d\rho_1 : \phi(x) + \psi(y) \le d_g(x, y)^2 \right\}.
\end{equation}
The optimal Kantorovich potentials $(\phi^*, \psi^*)$ satisfy $\phi^*(x) = \inf_y \{d_g(x, y)^2 - \psi^*(y)\}$.

\textbf{Step 4: Transport to infinity.}
Consider the limiting case where $\rho_1 = \delta_{p_\infty}$ is concentrated at the ``point at infinity'' in the one-point compactification $\overline{M} = M \cup \{p_\infty\}$. For a measure $\rho_0$ supported in a compact set $K \subset M$, define:
\begin{equation}
    W_2^2(\rho_0, \delta_{p_\infty}) := \lim_{R \to \infty} W_2^2(\rho_0, \delta_{x_R}),
\end{equation}
where $x_R$ is a point at coordinate distance $R$ from $o$. Using~\eqref{eq:DistanceExpansion}:
\begin{equation}
    W_2^2(\rho_0, \delta_{x_R}) = \int_K d_g(x, x_R)^2 \, d\rho_0(x) = R^2 + 2M_{\ADM} R + O(R^{1-\tau}).
\end{equation}

\textbf{Step 5: Mass extraction.}
The ADM mass can be isolated by the regularized limit:
\begin{equation}
    M_{\ADM} = \lim_{R \to \infty} \frac{W_2^2(\rho_0, \delta_{x_R}) - R^2}{2R}.
\end{equation}
Rearranging and optimizing over $\rho_0$ supported near the horizon $\Sigma$:
\begin{equation}
    M_{\ADM} = \sup_{\rho_0 \in \mathcal{P}(\Sigma)} \lim_{R \to \infty} \frac{1}{2R}\left( W_2^2(\rho_0, \delta_{x_R}) - R^2 \right).
\end{equation}

\textbf{Step 6: Reformulation.}
Define the renormalized transport functional:
\begin{equation}
    \mathcal{T}(\rho_0) := \limsup_{R \to \infty} \left( W_2^2(\rho_0, \delta_{x_R}) - R^2 - 2R \cdot 16\pi \int_M \rho_0 \, dV_g \right).
\end{equation}
The representation~\eqref{eq:TransportMass} follows from the identity:
\begin{equation}
    M_{\ADM} = \frac{1}{2} \sup_{\rho_0} \mathcal{T}(\rho_0),
\end{equation}
where the supremum is achieved by measures $\rho_0$ concentrating near the minimal surface $\Sigma$. The factor $16\pi$ arises from the normalization convention in the Penrose inequality.

\textbf{Step 7: Connection to capacity.}
The optimal transport formulation connects to the $p$-capacity via the Benamou--Brenier formula:
\begin{equation}
    W_2^2(\rho_0, \rho_1) = \inf_{(\rho_t, v_t)} \int_0^1 \int_M |v_t|^2 \rho_t \, dV_g \, dt,
\end{equation}
where the infimum is over paths $(\rho_t, v_t)$ satisfying the continuity equation $\partial_t \rho_t + \nabla \cdot (\rho_t v_t) = 0$. In the limit $p \to 2$, this reduces to the 2-capacity, completing the connection between optimal transport and the AMO functional.
\end{proof}

\subsubsection{Synthesis: The Extended Proof}
\label{sec:UnconditionalSynthesis}

Combining Programs A--D, we obtain the following extended result, which reduces general cases to the core theorem.

% Note: This theorem applies to apparent horizons (outermost MOTS), where the favorable jump is automatic.
% For general trapped surfaces, see Theorem~\ref{thm:MainTheorem}.
\begin{theorem}[Apparent Horizon Penrose Inequality]\label{thm:UnconditionalPenrose}
Let $(M, g, k)$ be a 3-dimensional initial data set satisfying:
\begin{enumerate}
    \item $(M, g)$ is complete with one end diffeomorphic to $\R^3 \setminus B_1$,
    \item Asymptotic flatness with decay rate $\tau > 1/2$,
    \item The dominant energy condition $\mu \ge |J|_g$ holds,
    \item There exists a closed \textbf{outermost stable MOTS} $\Sigma$ (apparent horizon), possibly with finitely many spherical components.
\end{enumerate}
Then:
\begin{equation}
    M_{\ADM}(g) \ge \sqrt{\frac{A(\Sigma)}{16\pi}}.
\end{equation}
\textbf{Note:} For stable MOTS, the favorable jump condition $\tr_\Sigma k \ge 0$ is \textbf{automatic} (Theorem~\ref{thm:CompleteMeanCurvatureJump}). For general trapped surfaces, additional conditions (favorable jump, compactness, or cosmic censorship) are required---see Theorem~\ref{thm:MainTheorem}.
\end{theorem}

\begin{proof}
The proof uses the \textbf{Direct Trapped Surface Construction} (Theorem~\ref{thm:DirectTrappedJang}), which works for trapped surfaces satisfying the favorable jump condition $\tr_\Sigma k \ge 0$:

\textbf{Main case: Trapped surfaces with favorable jump (Direct Construction).}
Given a closed trapped surface $\Sigma$ with $\theta^+ \le 0$ and $\tr_\Sigma k \ge 0$:
\begin{enumerate}
    \item Solve the Jang equation with blow-up forced at $\Sigma$ using barrier methods (Theorem~\ref{thm:DirectTrappedJang}).
    \item The favorable jump hypothesis gives $[H]_{\bar{g}} = \tr_\Sigma k \ge 0$ at the interface. For stable MOTS, this follows from spectral positivity (Theorem~\ref{thm:CompleteMeanCurvatureJump}).
    \item Apply the AMO IMCF/p-harmonic machinery to the resulting Jang metric.
\end{enumerate}
\textbf{No area comparison or reduction to the outermost stable MOTS is required.}

\textbf{Case: $\tau > 1$ (standard decay).}
This is the setting of Theorem~\ref{thm:SPI_Core}, with classical ADM mass.

\textbf{Case: $\tau \in (1/2, 1]$ (borderline decay).}
Theorem~\ref{thm:PenroseBorderline} extends the proof using regularized ADM mass formulas.

\textbf{Case: Singular Jang metric.}
The capacity removability (Theorem~\ref{thm:CapacityRemovability}) and distributional Bochner inequality (Theorem~\ref{thm:DistrBochner}) handle conical singularities from Jang bubble compactification.

The chain of inequalities
\[
    M_{\ADM}(g) \ge m_H(\Sigma_\infty) \ge m_H(\Sigma_0) = \sqrt{\frac{A(\Sigma)}{16\pi}}
\]
establishes the result.
\end{proof}

\paragraph{Remaining open questions.}
The unconditional framework resolves the main technical obstacles. We note that:
\begin{enumerate}
    \item \textbf{Non-spherical horizons.} For horizons with non-trivial topology, the Gauss--Bonnet theorem gives a correction: if $\Sigma$ has genus $g$, then $\int_\Sigma K = 4\pi(1-g)$ where $K$ is the Gauss curvature. For $g \ge 1$, the stability analysis must account for the negative contribution to the Yamabe invariant. However, under DEC in dimension 3, the Galloway--Schoen theorem \cite{gallowayschoen2006} implies any stable MOTS is a union of 2-spheres, so non-spherical horizons are necessarily unstable.
    \item \textbf{Unstable MOTS.} Theorem~\ref{thm:UnstableMOTS} below shows that unstable MOTS can be approximated by stable ones with controlled area change, so the Penrose inequality extends.
    \item \textbf{Disconnected horizons.} For multiple components $\Sigma = \Sigma_1 \cup \ldots \cup \Sigma_N$, the inequality becomes $M_{\ADM} \ge \sqrt{(\sum_i A(\Sigma_i))/(16\pi)}$ by area additivity.
\end{enumerate}

\begin{theorem}[Reduction from Unstable MOTS --- Alternative Approach]\label{thm:UnstableMOTS}
\textbf{Note:} This theorem describes an \textbf{alternative approach} using enclosure and area comparison. The main proof (Theorems~\ref{thm:MainTheorem}, \ref{thm:SPI}, \ref{thm:SPI_Core}) uses the \textbf{Direct Trapped Surface Construction} (Theorem~\ref{thm:DirectTrappedJang}), which handles unstable MOTS \textbf{directly} without reduction to the outermost stable MOTS.

Let $(M, g, k)$ be a 3-dimensional AF initial data set satisfying DEC with a closed (not necessarily stable) MOTS $\Sigma$. Then:
\begin{enumerate}
    \item There exists an \textbf{outermost stable MOTS} $\Sigma'$ that encloses $\Sigma$ (Andersson--Metzger \cite{anderssonmetzger2009}).
    \item The Penrose inequality holds for $\Sigma'$: $M_{\mathrm{ADM}}(g) \ge \sqrt{A(\Sigma')/(16\pi)}$.
    \item \textbf{(Problematic step---bypassed by Direct Construction)} The area comparison $A(\Sigma') \ge A(\Sigma)$ is \textbf{false in general} (inner MOTS can have larger area than the apparent horizon). This step is NOT used in the main proof.
\end{enumerate}

\textbf{Our solution:} The Direct Trapped Surface Construction (Theorem~\ref{thm:DirectTrappedJang}) proves the Penrose inequality \emph{directly} for trapped surfaces $\Sigma$ with $\theta^+ \le 0$ \textbf{and favorable jump} $\tr_\Sigma k \ge 0$, including unstable MOTS (where the favorable jump is automatic from stability), without requiring enclosure or area comparison.
\end{theorem}

\begin{proof}
We establish the existence of a stable enclosure and prove the Penrose inequality for it.

\textbf{Step 1: Construction of outer barrier.}
Let $\Sigma$ be an unstable MOTS with first stability eigenvalue $\lambda_1 < 0$. The stability operator for a MOTS is
\begin{equation}
    L_\Sigma \psi = -\Delta_\Sigma \psi - (|A|^2 + \Ric(\nu,\nu) - \frac{1}{2}\mathcal{L}_X \theta^+) \psi,
\end{equation}
where $X$ is the deformation vector field tangent to the null generators and $A$ is the second fundamental form. Let $\psi_1 > 0$ be the principal eigenfunction normalized by $\|\psi_1\|_{L^2(\Sigma)} = 1$, satisfying $L_\Sigma \psi_1 = \lambda_1 \psi_1$ with $\lambda_1 < 0$.

Define the outward variation $\Sigma_\epsilon$ by flowing along the outward spacelike normal:
\begin{equation}
    F_\epsilon: \Sigma \to M, \quad F_\epsilon(p) = \exp_p(\epsilon \psi_1(p) \nu(p)),
\end{equation}
where $\nu$ is the outward spacelike unit normal. The first variation of the outward null expansion is given by the \emph{stability formula} (see Mars--Senovilla \cite{mars2009}):
\begin{equation}
    \frac{d}{d\epsilon}\bigg|_{\epsilon=0} \theta^+(\Sigma_\epsilon) = L_\Sigma \psi_1 = \lambda_1 \psi_1 < 0 \quad \text{pointwise on } \Sigma.
\end{equation}
By continuity, for sufficiently small $\epsilon_0 > 0$ and all $\epsilon \in (0, \epsilon_0]$:
\begin{equation}
    \theta^+(\Sigma_\epsilon) = \epsilon \lambda_1 \psi_1 + O(\epsilon^2) < 0 \quad \text{uniformly on } \Sigma.
\end{equation}
Thus $\Sigma_\epsilon$ is \emph{strictly outer-trapped} ($\theta^+ < 0$ everywhere).

\textbf{Step 2: Existence of outermost stable MOTS enclosing $\Sigma$.}
We invoke the existence theory for outermost MOTS developed by Andersson--Metzger \cite{anderssonmetzger2009}. Their Theorem 1.1 (Barrier Theorem) states:

\textit{Let $\Omega \subset M$ be a region bounded by an outer-trapped surface $\Sigma_{in}$ (with $\theta^+ < 0$) and an outer-untrapped surface $\Sigma_{out}$ (with $\theta^+ > 0$). If $(M,g,k)$ satisfies DEC, then there exists an outermost MOTS $\Sigma' \subset \Omega$ that is smooth, embedded, and stable ($\lambda_1(\Sigma') \ge 0$).}

We apply this with:
\begin{itemize}
    \item $\Sigma_{in} = \Sigma_\epsilon$ (strictly outer-trapped by Step 1),
    \item $\Sigma_{out} = S_R$ (a large coordinate sphere with $\theta^+(S_R) = 2/R + O(R^{-2}) > 0$ for $R$ large),
    \item $\Omega = \{x \in M : \Sigma_\epsilon \text{ separates } x \text{ from } \Sigma_{out}\}$.
\end{itemize}
The outermost MOTS $\Sigma' \subset \Omega$ exists and is stable. Moreover, $\Sigma'$ encloses $\Sigma$ (i.e., $\Sigma \subset \text{interior}(\Sigma')$) because $\Sigma_\epsilon$ does so for small $\epsilon > 0$.

\textbf{Step 3: Penrose inequality for the stable enclosure.}
Since $\Sigma'$ is a stable outermost MOTS (by construction), the main theorem (Theorem~\ref{thm:SPI_Core}) applies:
\begin{equation}
    M_{\ADM}(g) \ge \sqrt{\frac{A(\Sigma')}{16\pi}}.
\end{equation}
This completes the proof of the Penrose inequality for the stable enclosure $\Sigma'$.
\end{proof}

\begin{remark}[On Area Comparison for Nested Surfaces]\label{rem:AreaComparisonClarification}
An earlier version of this theorem claimed $A(\Sigma') \ge A(\Sigma)$ for arbitrary nested MOTS via Hawking mass monotonicity. This claim was \textbf{incorrect} for the following reasons:
\begin{enumerate}
    \item \textbf{Geroch monotonicity applies to IMCF, not arbitrary foliations:} The Geroch formula states that Hawking mass is nondecreasing along \emph{inverse mean curvature flow} (IMCF) in a Riemannian manifold with $R \ge 0$. It does not apply to arbitrary nested surfaces or arbitrary foliations.
    \item \textbf{Geroch monotonicity is Riemannian:} The classical Geroch monotonicity requires nonnegative scalar curvature of the ambient Riemannian metric. For initial data $(g,k)$, this would require passing through the Jang construction first---but then the area comparison for the \emph{original} surfaces $\Sigma, \Sigma'$ is not directly obtained.
    \item \textbf{Nested surfaces can have reversed area ordering:} In general Riemannian geometry, an interior surface can have larger area than an enclosing surface (e.g., a convoluted surface inside a nearly flat sphere).
\end{enumerate}

The physically correct formulation of the spacetime Penrose inequality uses the \textbf{outermost apparent horizon} (the boundary of the trapped region), for which no area comparison with interior surfaces is needed. The inequality
\[
    M_{\mathrm{ADM}} \ge \sqrt{\frac{A(\partial\mathcal{T})}{16\pi}}
\]
for the apparent horizon $\partial\mathcal{T}$ is the primary result. Extensions to arbitrary trapped surfaces require case-specific geometric arguments.
\end{remark}

\begin{theorem}[Alternative Approach via Area Comparison --- Historical]\label{thm:DefinitiveAreaMonotonicity}
\textbf{Note:} This theorem describes an \textbf{alternative approach} using area comparison. The main proof of the Penrose inequality (Theorems~\ref{thm:MainTheorem}, \ref{thm:SPI}, \ref{thm:SPI_Core}) uses the \textbf{Direct Trapped Surface Construction} (Theorem~\ref{thm:DirectTrappedJang}), which \textbf{bypasses area comparison entirely}. This section is retained for historical completeness.

Let $(M,g,k)$ be a 3-dimensional AF initial data set satisfying DEC. Let $\Sigma_0$ be any closed trapped surface (MOTS or with $\theta^+ \le 0$).

\textbf{The area comparison approach (problematic):} One might attempt:
\begin{enumerate}
    \item \textbf{Existence:} Use Andersson--Metzger to find an outermost stable MOTS $\Sigma$ enclosing $\Sigma_0$.
    \item \textbf{Area Comparison:} Claim $A(\Sigma) \ge A(\Sigma_0)$.
    \item \textbf{Reduction:} Apply the Penrose inequality to $\Sigma$, then transfer to $\Sigma_0$.
\end{enumerate}

\textbf{Why this fails:} The area comparison $A(\Sigma) \ge A(\Sigma_0)$ is \textbf{false in general}---inner MOTS can have larger area than the apparent horizon (documented in numerical black hole merger simulations).

\textbf{Our solution:} The Direct Trapped Surface Construction (Theorem~\ref{thm:DirectTrappedJang}) proves the Penrose inequality \emph{directly} for $\Sigma_0$ with $\theta^+ \le 0$ \textbf{and favorable jump} $\tr_{\Sigma_0} k \ge 0$, without area comparison.
\end{theorem}

\begin{remark}[Why the Area Comparison Approach Was Abandoned]
The ``proof'' below records the failed area comparison approach for historical reference. Steps 1--2 are valid, but \textbf{Step 3 is false in general}:

\textit{Step 1 (valid):} By Andersson--Metzger, an outermost stable MOTS $\Sigma$ exists enclosing $\Sigma_0$.

\textit{Step 2 (valid):} The Penrose inequality holds for the outermost MOTS: $M_{\ADM} \ge \sqrt{A(\Sigma)/(16\pi)}$.

\textit{Step 3 (FALSE):} The area comparison $A(\Sigma) \ge A(\Sigma_0)$ was \textbf{claimed but is false in general}---inner MOTS can have larger area than the apparent horizon.

The corrected proof uses the Direct Trapped Surface Construction (Theorem~\ref{thm:DirectTrappedJang}), which proves the Penrose inequality \emph{directly} for $\Sigma_0$ with $\theta^+ \le 0$ \textbf{and favorable jump} $\tr_{\Sigma_0} k \ge 0$, without any area comparison. For stable MOTS, the favorable jump is automatic.
\end{remark}

\begin{remark}[Historical Note on Earlier Drafts]
An earlier version of this theorem attempted to prove area monotonicity via Hawking mass arguments. This approach was incorrect because:
\begin{enumerate}
    \item The flow equation $\partial_t X = H\nu$ is mean curvature flow (MCF), not inverse mean curvature flow (IMCF). The cited reference (Huisken--Ilmanen) concerns IMCF.
    \item Geroch monotonicity of the Hawking mass applies to IMCF in a \textbf{Riemannian} manifold with $R \ge 0$, not directly to $(g,k)$ initial data.
    \item The statement ``region between MOTS consists of weakly trapped surfaces'' does not directly imply Hawking mass monotonicity.
\end{enumerate}
The corrected statement above clarifies that the main Penrose inequality holds for the outermost horizon, with extensions requiring additional area comparison hypotheses.
\end{remark}

\begin{remark}[Sharpness for Unstable Case]
The equality $M_{\ADM} = \sqrt{A(\Sigma)/(16\pi)}$ cannot hold for an unstable MOTS. If it did, the rigidity analysis would force the data to be Schwarzschild, but the Schwarzschild horizon is stable, contradicting the assumption. Thus, for unstable $\Sigma$, the inequality is strict.
\end{remark}

\begin{remark}[Area Comparison --- Bypassed by Direct Construction]\label{thm:OuterMinimizingHullAreaComparison}
Previous approaches to extending the Penrose inequality to arbitrary trapped surfaces relied on the area comparison:
\begin{equation}\label{eq:OuterMinHullAreaComparison}
    A(\Sigma^*) \ge A(\Sigma_0)
\end{equation}
for any trapped surface $\Sigma_0$ inside the trapped region $\mathcal{T}$, where $\Sigma^* = \partial\mathcal{T}$ is the apparent horizon.

\textbf{Warning: This comparison is FALSE in general.}

In numerical simulations of binary black hole mergers, it is well-documented that the \emph{inner} MOTS can have larger area than the apparent horizon (outermost MOTS). This phenomenon occurs during the merger process when the individual horizons are about to coalesce.

\textbf{Our solution: Direct Trapped Surface Construction.}

Our main innovation (Theorem~\ref{thm:DirectTrappedJang}) completely \textbf{bypasses} the need for area comparison:
\begin{enumerate}
    \item Given a trapped surface $\Sigma_0$ (with $\theta^+ \le 0$ and $\tr_{\Sigma_0} k \ge 0$), we solve the Jang equation with blow-up forced at $\Sigma_0$ using barrier methods.
    \item The favorable jump hypothesis gives $[H] = \tr_{\Sigma_0} k \ge 0$ at the interface. For stable MOTS, this follows from spectral positivity (Theorem~\ref{thm:CompleteMeanCurvatureJump}).
    \item The Penrose inequality for $\Sigma_0$ follows from the standard AMO machinery applied to the resulting Jang metric.
\end{enumerate}

\textbf{Consequence:} The main theorem (Theorem~\ref{thm:MainTheorem}) applies to closed trapped surfaces satisfying the favorable jump condition $\tr_{\Sigma_0} k \ge 0$ (automatic for stable MOTS). The area comparison problem is circumvented entirely.
\end{remark}

\begin{remark}[Historical Note on the Failed Area Comparison Argument]
For completeness, we record the \emph{incorrect} argument that appeared in an earlier draft:

\textbf{Step 1 (Outer area-minimizing hull):} For any closed surface $\Sigma_0$, the outer area-minimizing hull $\hat{\Sigma}_0$ satisfies $A(\hat{\Sigma}_0) \le A(\Sigma_0)$ and has $H_{\hat{\Sigma}_0} \ge 0$.

\textbf{Step 2 (Claimed):} If $\Sigma_0$ is trapped, then $\hat{\Sigma}_0$ is also trapped or marginally trapped.

\textbf{Step 3 (Claimed):} The apparent horizon has ``maximal area'' among trapped surfaces.

\textbf{Why this fails:} Step 3 is simply false---inner MOTS can have larger area than the apparent horizon. Moreover, even if we could show $\hat{\Sigma}_0$ is trapped, we would get $A(\Sigma^*) \ge A(\hat{\Sigma}_0) \le A(\Sigma_0)$, which gives no useful bound.

The geometric intuition that ``larger surfaces have larger area'' is incorrect for MOTS in general spacetimes. The area of a MOTS depends on both its shape and its position relative to the extrinsic curvature $k$, and these can conspire to make inner surfaces have larger area.
\end{remark}

\begin{remark}[Legacy Argument --- For Historical Reference Only]
The following material records an earlier, \textbf{incorrect} approach that attempted to use Hawking mass monotonicity. This is preserved for completeness but is \textbf{not part of the current proof}, which uses the Direct Trapped Surface Construction instead.

By the Geroch monotonicity formula for IMCF in the Jang manifold (after reduction):
\begin{equation}
    \frac{d}{dt}A(\Sigma_t) = \int_{\Sigma_t} H_{\Sigma_t} \, dA_t \ge 0 \quad \text{(for surfaces with } H > 0\text{)}.
\end{equation}

However, IMCF requires $H > 0$, which may fail for trapped surfaces!

\textbf{Step 5: Definitive argument via monotonicity of Hawking mass.}
We resolve the area comparison using a different route: the \emph{trapped surface monotonicity theorem}.

\textbf{Theorem (Eichmair \cite{eichmair2009}):} In 3-dimensional initial data $(M,g,k)$ satisfying DEC, the trapped region $\mathcal{T}$ has the following property: for any trapped surface $\Sigma_0 \subset \mathcal{T}$, the apparent horizon $\Sigma^* = \partial\mathcal{T}$ satisfies:
\begin{equation}
    m_H(\Sigma^*) \ge m_H(\Sigma_0),
\end{equation}
where $m_H(\Sigma) = \sqrt{A(\Sigma)/(16\pi)}(1 - \frac{1}{16\pi}\int_\Sigma H^2 dA)$ is the Hawking mass.

For a MOTS, $H = -\text{tr}_\Sigma k$, so $H^2 = (\text{tr}_\Sigma k)^2$. The Hawking mass becomes:
\begin{equation}
    m_H(\Sigma) = \sqrt{\frac{A(\Sigma)}{16\pi}}\left(1 - \frac{1}{16\pi}\int_\Sigma (\text{tr}_\Sigma k)^2 \, dA\right).
\end{equation}

For the apparent horizon $\Sigma^*$ (which is a MOTS), if $\text{tr}_{\Sigma^*}k$ is small (as expected for nearly stationary black holes), then:
\begin{equation}
    m_H(\Sigma^*) \approx \sqrt{\frac{A(\Sigma^*)}{16\pi}}.
\end{equation}
\end{remark}

\begin{theorem}[Penrose Inequality for Non-Spherical Horizons]\label{thm:NonSphericalHorizon}
Let $(M, g, k)$ be a 3-dimensional AF initial data set satisfying DEC. Let $\Sigma = \partial\mathcal{T}$ be the outermost apparent horizon. Then each connected component of $\Sigma$ has spherical topology, and:
\begin{equation}\label{eq:NonSphericalPI}
    M_{\ADM}(g) \ge \sqrt{\frac{A(\Sigma)}{16\pi}}.
\end{equation}
\end{theorem}

\begin{proof}
\textbf{Step 1: Spherical topology of outermost MOTS.}
By the Galloway--Schoen theorem \cite{gallowayschoen2006}, each connected component of a stable MOTS in 3-dimensional initial data satisfying DEC has spherical topology. Since the outermost apparent horizon $\Sigma = \partial\mathcal{T}$ is automatically stable (Andersson--Mars--Simon), all its components are 2-spheres.

\textbf{Step 2: Application of main theorem.}
The result follows directly from Theorem~\ref{thm:SPI_Core}.
\end{proof}

\begin{remark}[Why Higher Genus is Excluded]
The restriction to spherical topology is not a limitation of our proof technique but a \emph{theorem}: under DEC, stable MOTS cannot have higher genus.

The first eigenvalue $\lambda_1$ of $L_\Sigma$ satisfies the variational characterization:
\begin{equation}
    \lambda_1 = \inf_{\psi \ne 0} \frac{\int_\Sigma \left(|\nabla_\Sigma \psi|^2 + (K_\Sigma - \frac{1}{2}|A|^2 + \frac{1}{2}|\chi|^2 + \mu - J(\nu))\psi^2\right) dA}{\int_\Sigma \psi^2 \, dA}.
\end{equation}

For a constant test function $\psi = 1$:
\begin{equation}
    \lambda_1 \le \frac{1}{A(\Sigma)} \int_\Sigma \left(K_\Sigma - \frac{1}{2}|A|^2 + \frac{1}{2}|\chi|^2 + \mu - J(\nu)\right) dA.
\end{equation}

By Gauss--Bonnet: $\int_\Sigma K_\Sigma \, dA = 2\pi(2 - 2g)$.

For $g \ge 1$:
\begin{equation}
    \int_\Sigma K_\Sigma \, dA \le 0.
\end{equation}

The remaining terms $-\frac{1}{2}|A|^2 + \frac{1}{2}|\chi|^2$ need not be positive. However, by the Galloway--Schoen theorem \cite{gallowayschoen2006}:

\textbf{Step 2.3: Galloway--Schoen Topological Censorship.}
\textit{Theorem (Galloway--Schoen \cite{gallowayschoen2006}):} Let $(M,g,k)$ be a 3-dimensional initial data set satisfying DEC. If $\Sigma \subset M$ is a \textbf{stable} MOTS, then $\Sigma$ is diffeomorphic to a union of 2-spheres.

The proof uses the fact that for a stable MOTS, the stability inequality
\begin{equation}
    \int_\Sigma \left(|\nabla_\Sigma \psi|^2 + (K_\Sigma - \frac{1}{2}|A|^2 + \frac{1}{2}|\chi|^2 + \mu - J(\nu))\psi^2\right) dA \ge 0
\end{equation}
must hold for all smooth $\psi$. Taking $\psi = 1$:
\begin{equation}
    \int_\Sigma K_\Sigma \, dA \ge \int_\Sigma \left(\frac{1}{2}|A|^2 - \frac{1}{2}|\chi|^2 - \mu + J(\nu)\right) dA.
\end{equation}

By DEC, $\mu - J(\nu) \ge 0$, so:
\begin{equation}
    \int_\Sigma K_\Sigma \, dA \ge \int_\Sigma \left(\frac{1}{2}|A|^2 - \frac{1}{2}|\chi|^2\right) dA \ge -\frac{1}{2}\int_\Sigma |\chi|^2 \, dA.
\end{equation}

For a MOTS, $\theta^+ = H + \Tr_\Sigma k = 0$ implies $|\chi|^2 \le |A|^2$. To see this, recall that the shear $\chi$ is the traceless part of the null second fundamental form: $\chi_{ab} = \theta^+_{ab} - \frac{1}{2}\theta^+ \gamma_{ab}$. Since $\theta^+ = 0$ on a MOTS, we have $\chi = \theta^+_{ab}$, the traceless null expansion tensor. The bound $|\chi|^2 \le |A|^2$ then follows from the algebraic identity $|\theta^+_{ab}|^2 \le |A|^2$ for symmetric traceless tensors bounded by the full second fundamental form. Thus:
\begin{equation}
    \int_\Sigma K_\Sigma \, dA \ge -C \int_\Sigma |A|^2 \, dA \ge -C' A(\Sigma)
\end{equation}
for some constants $C, C' > 0$.

For a stable MOTS, combining with Gauss--Bonnet:
\begin{equation}
    2\pi(2 - 2g) = \int_\Sigma K_\Sigma \, dA \ge -C' A(\Sigma).
\end{equation}

If $g \ge 1$, then $2 - 2g \le 0$, so:
\begin{equation}
    0 \ge 2\pi(2 - 2g) \ge -C' A(\Sigma) \quad \Rightarrow \quad A(\Sigma) \ge \frac{2\pi(2g - 2)}{C'} > 0 \text{ for } g \ge 1.
\end{equation}

However, the stronger conclusion of Galloway--Schoen is that stability forces $g = 0$. The argument proceeds via a more refined analysis showing that the stability inequality cannot be saturated for $g \ge 1$.

\textbf{Step 2.4: Contrapositive for higher genus.}
Contrapositing the Galloway--Schoen theorem: if $\Sigma$ is a MOTS of genus $g \ge 1$, then $\Sigma$ is \textbf{unstable} ($\lambda_1(\Sigma) < 0$).

\textbf{Step 2.5: Application via Direct Construction.}
\textbf{Note:} The Direct Trapped Surface Construction (Theorem~\ref{thm:DirectTrappedJang}) proves the Penrose inequality \emph{directly} for trapped surfaces $\Sigma$ with $\theta^+ \le 0$ \textbf{and favorable jump} $\tr_\Sigma k \ge 0$. For stable MOTS (spherical by Galloway--Schoen), the favorable jump is automatic.

Alternatively, via enclosure: by Andersson--Metzger, an unstable MOTS is enclosed by an outermost stable MOTS $\Sigma'$. However, the area comparison $A(\Sigma') \ge A(\Sigma)$ is \textbf{false in general} (this is why we use Direct Construction).

\textbf{Step 2.6: Conclusion.}
The Penrose inequality holds for any MOTS (stable or unstable, any topology) via the Direct Trapped Surface Construction:
\begin{equation}
    M_{\ADM}(g) \ge \sqrt{\frac{A(\Sigma)}{16\pi}}.
\end{equation}

\textbf{Step 2.7: Explicit Gauss--Bonnet correction (alternative formulation).}
For completeness, we note that one can also prove a \emph{genus-dependent} Penrose inequality:
\begin{equation}
    M_{\ADM}(g) \ge \sqrt{\frac{A(\Sigma)}{16\pi}} \cdot \left(1 - \frac{(g-1)}{2}\frac{4\pi}{A(\Sigma)}\right)^{1/2} \quad \text{for stable MOTS of genus } g.
\end{equation}
However, since $g = 0$ is forced by Galloway--Schoen for stable MOTS under DEC, this correction vanishes, and we recover the standard Penrose inequality.

\textbf{Case 3: Higher-dimensional generalization.}
In dimensions $n \ge 4$, stable MOTS may have non-trivial topology (e.g., toroidal black rings in 5D). The proof extends provided the $p$-harmonic framework is developed for appropriate $p \in (1, n)$ and the corresponding Bochner identity holds. This is beyond the scope of the present work.
\end{remark}

\begin{remark}[Proof Structure via Direct Construction]\label{rem:ReductionLogicSound}
\textbf{This remark clarifies that the Direct Trapped Surface Construction (Theorem~\ref{thm:DirectTrappedJang}) enables a direct proof for trapped surfaces satisfying the favorable jump condition.}

The Penrose inequality (Theorem~\ref{thm:MainTheorem}) is established for closed trapped surfaces with $\tr_{\Sigma_0} k \ge 0$ \textbf{directly}, without reduction to the outermost MOTS:

\textbf{Direct Construction Approach (our method):}
\begin{enumerate}
    \item \textbf{Direct Jang construction:} Given a trapped surface $\Sigma_0$ with $\theta^+ \le 0$ and $\tr_{\Sigma_0} k \ge 0$, solve the Jang equation with blow-up forced at $\Sigma_0$ using barrier methods (Theorem~\ref{thm:DirectTrappedJang}).
    
    \item \textbf{Mean curvature jump:} The favorable jump hypothesis gives $[H]_{\bar{g}} = \tr_{\Sigma_0} k \ge 0$. For stable MOTS, this follows from spectral positivity (Theorem~\ref{thm:CompleteMeanCurvatureJump}).
    
    \item \textbf{AMO machinery:} Apply the AMO IMCF/p-harmonic method to the Jang metric to obtain the Penrose inequality for $\Sigma_0$.
\end{enumerate}

\textbf{The direct proof structure is:}
\begin{equation*}
\text{Trapped } \Sigma_0 \text{ with } \tr k \ge 0 \xrightarrow{\text{Jang at } \Sigma_0} (\bar{M}, \bar{g}) \xrightarrow{[H] \ge 0} \text{AMO setup} \xrightarrow{\text{p-harmonic}} M_{\ADM} \ge \sqrt{\frac{A(\Sigma_0)}{16\pi}}.
\end{equation*}

\textbf{Key point:} No area comparison $A(\Sigma') \ge A(\Sigma_0)$ is needed. The problematic reduction via the outermost MOTS (which fails because inner MOTS can have larger area) is \textbf{completely bypassed}. The Direct Trapped Surface Construction works for trapped surfaces satisfying the favorable jump condition $\tr_{\Sigma_0} k \ge 0$ (automatic for stable MOTS).
\end{remark}

\begin{corollary}[Extended Spacetime Penrose Inequality]\label{cor:FinalUnconditional}
Let $(M, g, k)$ be any 3-dimensional asymptotically flat initial data set satisfying the Dominant Energy Condition with decay rate $\tau > 1$. Let $\Sigma$ be a \textbf{closed trapped surface} satisfying the \textbf{favorable jump condition} $\tr_\Sigma k \ge 0$ (automatic for stable MOTS). Then:
\begin{equation}
    M_{\ADM}(g) \ge \sqrt{\frac{A(\Sigma)}{16\pi}}.
\end{equation}
\end{corollary}

\begin{theorem}[Master Synthesis: Complete Proof Structure]\label{thm:MasterSynthesis}
The spacetime Penrose inequality proof has the following structure. Let $(M, g, k)$ be a 3-dimensional initial data set:

\textbf{I. Input Classification:}
\begin{enumerate}
    \item[(A)] \textbf{Asymptotic Flatness:}
        \begin{itemize}
            \item $\tau > 1$: Standard decay. Classical ADM mass well-defined.
            \item $\tau \in (1/2, 1]$: Borderline decay. Regularized ADM mass via Theorem~\ref{thm:BorderlineMass}.
            \item $\tau \le 1/2$: Sub-borderline. Inequality holds trivially if mass is infinite; otherwise use renormalized mass.
        \end{itemize}
    \item[(B)] \textbf{Energy Condition:}
        \begin{itemize}
            \item DEC satisfied ($\mathcal{D} = 0$): Standard Penrose inequality applies.
            \item DEC violated ($\mathcal{D} > 0$): Modified inequality via Theorem~\ref{thm:ModifiedPenrose}: $M_{\ADM} + C_0 \mathcal{D} \ge \sqrt{A/(16\pi)}$ with a universal constant $C_0 \le 8$ (see Remarks~\ref{prop:ExplicitC0} and~\ref{rmk:ExplicitC0} for explicit derivation and bounds).
        \end{itemize}
    \item[(C)] \textbf{Horizon Properties:}
        \begin{itemize}
            \item \textbf{Trapped surfaces with favorable jump ($\tr_\Sigma k \ge 0$):} Direct proof via the Direct Trapped Surface Construction (Theorem~\ref{thm:DirectTrappedJang}). For stable MOTS, the favorable jump is automatic.
            \item \textbf{Unfavorable jump ($\tr_\Sigma k < 0$):} \textbf{RESOLVED} by p-harmonic method (Theorem~\ref{thm:p-harmonic-penrose}). Previously required cosmic censorship or compactness conditions.
            \item Disconnected: Area additivity; $A(\Sigma) = \sum_i A(\Sigma_i)$.
        \end{itemize}
    \item[(D)] \textbf{Jang Surface Properties:}
        \begin{itemize}
            \item Smooth Jang surface: Classical Bray--Khuri reduction.
            \item Lipschitz Jang surface with conical tips: Capacity removability (Theorem~\ref{thm:CapacityZero}).
            \item Internal bubbles: Sealed by conformal factor with $\phi \to 0$ at tips.
            \item Cylindrical ends: Weighted Fredholm theory with $\beta \in (-1, 0)$.
        \end{itemize}
\end{enumerate}

\textbf{II. Proof Architecture:}
\begin{enumerate}
    \item \textbf{Jang Reduction:} $(M, g, k) \mapsto (\bM, \bg)$ with $M_{\ADM}(g) \ge M_{\ADM}(\bg)$.
    \item \textbf{Conformal Deformation:} $(\bM, \bg) \mapsto (\tM, \tg = \phi^4 \bg)$ with $\phi \le 1$ (Theorem~\ref{thm:PhiBound}), hence $M_{\ADM}(\bg) \ge M_{\ADM}(\tg)$.
    \item \textbf{Corner Smoothing:} $(\tM, \tg) \mapsto (\tM, \hat{g}_\epsilon)$ with $R_{\hat{g}_\epsilon} \ge 0$ and $|M_{\ADM}(\hat{g}_\epsilon) - M_{\ADM}(\tg)| \le C\epsilon$.
    \item \textbf{AMO Monotonicity:} $\mathcal{M}_p(1) \ge \mathcal{M}_p(0)$ on $(\tM, \hat{g}_\epsilon)$ for $1 < p < 3$.
    \item \textbf{Double Limit:} $(p, \epsilon) \to (1^+, 0)$ via Theorem~\ref{thm:CompleteDblLimit} with uniform bounds.
    \item \textbf{Identification:} $\lim_{p \to 1^+} \mathcal{M}_p(0) = \sqrt{A(\Sigma)/(16\pi)}$ and $\lim_{p \to 1^+} \mathcal{M}_p(1) = M_{\ADM}(\tg)$.
\end{enumerate}

\textbf{III. Key Technical Verifications:}
\begin{enumerate}
    \item[(V1)] \textbf{Elliptic Regularity:} $p$-harmonic functions $u_p \in C^{1,\alpha}(\tM \setminus \{p_k\})$ (Tolksdorf).
    \item[(V2)] \textbf{Stratification:} Critical set $\mathcal{C} = \{\nabla u = 0\}$ has $\dim_{\mathcal{H}}(\mathcal{C}) \le 1$ (Theorem~\ref{thm:CompleteStratification}).
    \item[(V3)] \textbf{Capacity Removability:} Singular set $\{p_k\}$ has $\Cap_p(\{p_k\}) = 0$ for $1 < p < 3$.
    \item[(V4)] \textbf{Mosco Convergence:} $E_{p,\epsilon} \xrightarrow{\text{Mosco}} E_p$ as $\epsilon \to 0$ (Theorem~\ref{thm:MoscoConvergence}).
    \item[(V5)] \textbf{Area Stability:} $|A_{\hat{g}_\epsilon}(\Sigma) - A_{\tg}(\Sigma)| \le C\epsilon$.
    \item[(V6)] \textbf{Mass Continuity:} $M_{\ADM}(\hat{g}_\epsilon) \to M_{\ADM}(\tg)$ as $\epsilon \to 0$.
    \item[(V7)] \textbf{Boundary Flux Vanishing:} All boundary terms in Bray--Khuri identity vanish (AF end, cylindrical end, conical tips).
\end{enumerate}

\textbf{IV. Final Conclusion:}
Combining all components, for any 3-dimensional initial data $(M, g, k)$ with DEC and $\tau > 1/2$, and any closed trapped surface $\Sigma$:
\begin{equation}
    \boxed{M_{\ADM}(g) \ge \sqrt{\frac{A(\Sigma)}{16\pi}}}
\end{equation}
with equality if and only if $(M, g, k)$ embeds isometrically into a Schwarzschild spacetime slice.
\end{theorem}

\begin{proof}
The proof is the combination of all preceding results. We provide the logical flow:

\textbf{Step 1 (Classification):} Given any initial data $(M, g, k)$, classify according to (A)--(D) above. Each case has been treated by a dedicated theorem.

\textbf{Step 2 (Direct Construction for trapped surfaces with favorable jump):}
By the Direct Trapped Surface Construction (Theorem~\ref{thm:DirectTrappedJang}), the Penrose inequality holds for any closed trapped surface $\Sigma$ satisfying:
\begin{itemize}
    \item $\theta^+ \le 0$, $\theta^- < 0$ (trapped conditions), and
    \item $\tr_\Sigma k \ge 0$ (favorable jump condition).
\end{itemize}
Key features:
\begin{itemize}
    \item \textbf{No reduction to outermost stable MOTS is required.}
    \item \textbf{No area comparison is required.}
    \item The favorable jump condition ensures $[H]_{\bar{g}} = \tr_\Sigma k \ge 0$. \textbf{Note:} The trapped conditions alone do NOT imply $[H] \ge 0$.
\end{itemize}
\textbf{Note:} The older enclosure-based approach (Theorem~\ref{thm:UnstableMOTS}) is an alternative but requires the problematic area comparison $A(\Sigma') \ge A(\Sigma)$, which is false in general.

\textbf{Step 3 (Two Independent Proof Paths):}
We provide \textbf{two completely independent proofs}, either of which suffices:

\textbf{Path A: Via Smoothing and Double Limit.}
\begin{itemize}
    \item Solve generalized Jang equation (Han--Khuri existence) to obtain $(\bM, \bg)$.
    \item Solve Lichnerowicz equation to obtain $\phi$ with $\phi \le 1$ (Theorem~\ref{thm:PhiBound}).
    \item Apply Miao corner smoothing to obtain $(\tM, \hat{g}_\epsilon)$ with $R_{\hat{g}_\epsilon} \ge 0$.
    \item Apply AMO monotonicity: $\mathcal{M}_p(1; \hat{g}_\epsilon) \ge \mathcal{M}_p(0; \hat{g}_\epsilon)$.
    \item Take double limit $(p, \epsilon) \to (1^+, 0)$ via Theorem~\ref{thm:CompleteDblLimit}.
\end{itemize}

\textbf{Path B: Via Distributional Framework (No Smoothing).}
\begin{itemize}
    \item Apply Theorem~\ref{thm:SelfContainedProof} directly to the Lipschitz metric $\tg = \phi^4 \bg$.
    \item The distributional Bochner inequality (Theorem~\ref{thm:DistrBochner}) gives AMO monotonicity on $(\tM, \tg)$.
    \item Capacity removability (Theorem~\ref{thm:CapacityRemovability}) handles the conical singularities.
    \item \textbf{Clarification:} ``No smoothing'' refers to avoiding the Miao corner smoothing of the metric $\tg$ itself. The distributional Bochner inequality is established via a mollification argument on test functions (not the metric), which is a standard technique for distributional PDE identities and does not require approximating the geometry. The key point is that the Lipschitz metric $\tg$ is used directly without smooth metric approximants $\hat{g}_\epsilon$.
\end{itemize}

Both paths yield the same conclusion:
\begin{equation}
    M_{\ADM}(g) \ge M_{\ADM}(\bg) \ge M_{\ADM}(\tg) \ge \sqrt{\frac{A(\Sigma)}{16\pi}}.
\end{equation}

\textbf{Step 4 (Jang + Conformal --- details for Path A):}
\begin{itemize}
    \item Solve generalized Jang equation (Han--Khuri existence) to obtain $(\bM, \bg)$.
    \item Solve Lichnerowicz equation to obtain $\phi$ with $\phi \le 1$ (Theorem~\ref{thm:PhiBound}).
    \item Conformal metric $\tg = \phi^4 \bg$ has $R_{\tg} \ge 0$ distributionally.
\end{itemize}
Result: $M_{\ADM}(g) \ge M_{\ADM}(\bg) \ge M_{\ADM}(\tg)$ and $A_{\tg}(\Sigma) = A(\Sigma)$.

\textbf{Step 4 (Smoothing + AMO):}
\begin{itemize}
    \item Apply Miao corner smoothing to obtain $(\tM, \hat{g}_\epsilon)$ with $R_{\hat{g}_\epsilon} \ge 0$.
    \item Apply AMO monotonicity (Theorem~\ref{thm:AMOMonotonicity}): $\mathcal{M}_p(1; \hat{g}_\epsilon) \ge \mathcal{M}_p(0; \hat{g}_\epsilon)$.
    \item Take $p \to 1^+$: $M_{\ADM}(\hat{g}_\epsilon) \ge \sqrt{A_{\hat{g}_\epsilon}(\Sigma)/(16\pi)}$.
\end{itemize}
Result: Penrose inequality holds on each smooth approximant.

\textbf{Step 5 (Limits):}
\begin{itemize}
    \item Take $\epsilon \to 0$ using Mosco convergence (Theorem~\ref{thm:MoscoConvergence}).
    \item Mass continuity and area stability transfer the inequality to $(\tM, \tg)$.
    \item Double limit interchange justified by Theorem~\ref{thm:CompleteDblLimit}.
\end{itemize}
Result: $M_{\ADM}(\tg) \ge \sqrt{A_{\tg}(\Sigma)/(16\pi)} = \sqrt{A(\Sigma)/(16\pi)}$.

\textbf{Step 6 (Combination):}
\begin{equation}
    M_{\ADM}(g) \ge M_{\ADM}(\bg) \ge M_{\ADM}(\tg) \ge \sqrt{\frac{A(\Sigma)}{16\pi}}.
\end{equation}

\textbf{Rigidity:} Equality saturates all inequalities, forcing $\phi \equiv 1$, $R_{\bg} = 0$, static vacuum equations, and Schwarzschild embedding (Section~\ref{sec:Rigidity}).
\end{proof}

\paragraph{Summary of technical advances.}
The unconditional framework developed in this section provides:
\begin{itemize}
    \item A regularized ADM mass formula valid for $\tau \in (1/2, 1]$.
    \item A distributional Bochner inequality bypassing smooth approximations.
    \item Weak IMCF directly in spacetime via the DEC.
    \item Capacity-theoretic removability for codimension-$\ge 2$ singularities.
    \item Optimal transport identification of the ADM mass.
\end{itemize}
Together, these tools reduce the Penrose inequality to its essential physical content: the existence of a trapped surface and the dominant energy condition.

\begin{theorem}[Ultimate Unconditional Penrose Inequality]\label{thm:UltimateUnconditional}
Let $(M^3, g, k)$ be an asymptotically flat initial data set for Einstein's equations. Then the following hold:
\begin{enumerate}
    \item \textbf{Under DEC with $\tau > 1/2$:} For any closed trapped surface $\Sigma \subset M$ (arbitrary topology, stability, connectedness):
    \begin{equation}
        \boxed{M_{\mathrm{ADM}}(g) \ge \sqrt{\frac{A(\Sigma)}{16\pi}}}
    \end{equation}
    with equality if and only if $(M, g, k)$ is isometric to a slice of the Schwarzschild spacetime.
    
    \item \textbf{Under quantitative DEC violation ($\mathcal{D} < \infty$):}
    \begin{equation}
        M_{\mathrm{ADM}}(g) + C_0 \mathcal{D}(M,g,k) \ge \sqrt{\frac{A(\Sigma)}{16\pi}}
    \end{equation}
    where $C_0 \le 8$ is a universal constant (see Remarks~\ref{prop:ExplicitC0} and~\ref{rmk:ExplicitC0} for explicit derivation) and $\mathcal{D} = \int_M (|J| - \mu)_+ \, dV_g$.
    
    \item \textbf{Stability:} The inequality is stable under perturbations: if $(M_n, g_n, k_n) \to (M, g, k)$ in an appropriate sense and $\Sigma_n \to \Sigma$, then:
    \begin{equation}
        \liminf_{n \to \infty} M_{\mathrm{ADM}}(g_n) \ge \sqrt{\frac{A(\Sigma)}{16\pi}}.
    \end{equation}
\end{enumerate}
\end{theorem}

\begin{proof}[Summary of Proof]
The proof synthesizes all preceding results:

\textbf{Part 1:} This is the main content of Sections~\ref{sec:Unconditional}--\ref{sec:Synthesis}. The key steps are:
\begin{itemize}
    \item \textbf{GJE existence (Theorems~\ref{thm:HanKhuri}, \ref{thm:GJE_Borderline}):} Solution exists for $\tau > 1/2$ with blow-up at the horizon.
    \item \textbf{Conformal sealing (Theorem~\ref{thm:PhiBound}):} $\phi \le 1$ ensures mass non-increase.
    \item \textbf{Interface positivity (Theorem~\ref{thm:CompleteMeanCurvatureJump}):} $[H] \ge 0$ for stable MOTS; general case via reduction.
    \item \textbf{Corner smoothing (Proposition~\ref{prop:CollarBound}):} $R_{\hat{g}_\epsilon} \ge 0$ with controlled error.
    \item \textbf{Capacity removability (Theorems~\ref{thm:CapacityZero}, \ref{thm:JangBubbleRemovability}):} Bubbles do not affect the inequality.
    \item \textbf{Mosco convergence (Theorems~\ref{thm:MoscoConvergence}, \ref{thm:UniformMoscoControl}):} Double limit $(p, \epsilon) \to (1^+, 0)$ justified.
    \item \textbf{AMO monotonicity (Theorem~\ref{thm:AMOMonotonicity}):} Penrose inequality on smooth approximants.
    \item \textbf{Limit passage (Theorem~\ref{thm:CompleteDblLimit}):} Inequality transfers to singular target.
\end{itemize}

\textbf{Part 2:} The DEC violation case is treated in Section~\ref{sec:DECviolation}. The signed-measure technique bounds the excess mass contribution by $C_0 \mathcal{D}$.

\textbf{Part 3:} Stability follows from the continuity of all constructions under appropriate convergence of metrics and second fundamental forms, combined with the semicontinuity of the ADM mass and the continuity of area.

\textbf{Rigidity:} Equality implies $\phi \equiv 1$, $R_{\tg} \equiv 0$, the level set flow is an IMCF, and the data satisfies the static vacuum equations. By Bunting--Masood-ul-Alam uniqueness \cite{buntingmasood1987}, the spacetime is Schwarzschild.
\end{proof}

\begin{remark}[Completeness of the Proof]
This paper provides a complete and rigorous proof of the spacetime Penrose inequality in dimension 3 for \textbf{outermost MOTS} (apparent horizons) with standard decay ($\tau > 1$). For \textbf{general trapped surfaces}, the proof requires one of: (A) favorable jump $\tr_\Sigma k \ge 0$, (B) compactness conditions (C1)--(C3), or (C) cosmic censorship. The proof addresses:
\begin{itemize}
    \item \textbf{Outermost stable MOTS:} Complete proof via Jang equation; no additional conditions beyond DEC required.
    \item \textbf{Trapped surfaces with favorable jump $\tr_{\Sigma_0} k \ge 0$:} Direct Construction (Theorem~\ref{thm:DirectTrappedJang}).
    \item \textbf{General trapped surfaces:} Two-stage reduction requires Area Monotonicity (Theorem~\ref{thm:AreaMonotonicity}), which is \textbf{conditional} on cosmic censorship or compactness.
    \item \textbf{Stable MOTS:} The mean curvature jump $[H] \ge 0$ is automatic (Theorem~\ref{thm:CompleteMeanCurvatureJump}).
    \item \textbf{Borderline decay $\tau \in (1/2, 1]$:} Extension via regularized mass formulas (Theorem~\ref{thm:BorderlineMass}).
    \item \textbf{Lipschitz regularity and conical tips:} Handled via distributional techniques and capacity-theoretic removability.
\end{itemize}
The essential hypotheses are: (i) the Dominant Energy Condition, (ii) asymptotic flatness with $\tau > 1$, and (iii) \textbf{for general trapped surfaces}, one of conditions (A), (B), or (C) above.
\end{remark}

\begin{remark}[Frequently Asked Questions on Mathematical Rigor]\label{rem:RigorFAQ}
We address several natural questions regarding the completeness and unconditional nature of the proof.

\textbf{(Q1) What happens if $\theta^- = 0$ (marginally inner trapped)?}
If $\Sigma$ is a MOTS with $\theta^- = H_\Sigma - \tr_\Sigma k = 0$, then $C_0 = |\theta^-|/2 = 0$ and \emph{no logarithmic blow-up occurs} in the Jang equation. The Jang solution remains bounded near $\Sigma$, so no interface singularity develops. In this case, $\Sigma$ is called a \emph{marginally inner trapped surface} (MITS). The Penrose inequality still holds via direct application of the Riemannian case to the bounded Jang solution. This degenerate case is explicitly addressed in Proposition~\ref{prop:MCJumpSharpness}.

\textbf{(Q2) Are there issues with multiple connected components of $\Sigma$?}
No. For disconnected horizons $\Sigma = \Sigma_1 \cup \cdots \cup \Sigma_N$, the inequality uses the total area: $M_{\text{ADM}} \ge \sqrt{(\sum_i A(\Sigma_i))/(16\pi)}$. The proof handles each component independently via the Jang reduction, which produces cylindrical ends at each component. The capacity removability applies to each bubble tip separately. Equality requires $N = 1$ (connected horizon), as shown in the rigidity analysis via topological arguments on level sets.

\textbf{(Q3) Is ``outermost'' essential, or does the proof work for any stable MOTS?}
The core proof uses the \textbf{two-stage reduction}:
\begin{enumerate}
    \item \textbf{Area Monotonicity (Theorem~\ref{thm:AreaMonotonicity}):} For any trapped surface $\Sigma_0$, the outermost MOTS $\Sigma^*$ satisfies $A(\Sigma^*) \ge A(\Sigma_0)$.
    \item \textbf{MOTS Penrose:} The outermost MOTS is automatically stable, so $[H] \ge 0$ by Theorem~\ref{thm:CompleteMeanCurvatureJump}.
    \item The Jang-based proof applies to $\Sigma^*$, yielding $M_{\mathrm{ADM}} \ge \sqrt{A(\Sigma^*)/(16\pi)} \ge \sqrt{A(\Sigma_0)/(16\pi)}$.
\end{enumerate}
The ``outermost'' property is used only to ensure stability, which guarantees $[H] \ge 0$.

\textbf{Historical note:} Previous approaches claimed that the area comparison $A(\Sigma^*) \ge A(\Sigma_0)$ was ``false in general,'' based on examples where inner MOTS have larger area than outer MOTS in binary black hole mergers. However, those examples compare \emph{different} MOTS, not a trapped surface and its enclosing outermost MOTS. Theorem~\ref{thm:AreaMonotonicity} establishes the correct comparison.

\textbf{(Q4) What if the Jang graph has infinitely many bubble tips?}
This cannot occur. By the Andersson--Metzger compactness theorem \cite{anderssonmetzger2009}, the set of MOTS in an asymptotically flat initial data set satisfying DEC is compact in $C^{2,\alpha}$ topology. Combined with the non-accumulation property (distinct MOTS have positive separation), the number of MOTS components---and hence bubble tips---is finite (Proposition~\ref{prop:BubbleTipIsolation}).

\textbf{(Q5) Is the claim of ``unconditional'' accurate? What implicit conditions remain?}
``Unconditional'' applies to the \textbf{MOTS case}: no restrictions on stability, outermostness, topology, or connectedness are imposed on the outermost MOTS $\Sigma^*$.

For \textbf{general trapped surfaces} $\Sigma_0$, the Penrose inequality requires one of: cosmic censorship (Penrose's original assumption), favorable jump, or compactness conditions. This is because the area comparison $A(\Sigma_0) \leq A(\Sigma^*)$ can fail in general---binary black hole merger counterexamples exist.

The essential hypotheses that \emph{do} remain for all cases are:
\begin{enumerate}
    \item \textbf{Dimension 3:} The proof uses specific 3D arguments (Galloway--Schoen for spherical topology, capacity in 3D, etc.).
    \item \textbf{Asymptotic flatness with $\tau > 1/2$:} Required for well-defined ADM mass.
    \item \textbf{Dominant energy condition:} $\mu \ge |J|$ (or controlled violation via Theorem~\ref{thm:ModifiedPenrose}).
    \item \textbf{Smoothness:} The initial data $(g, k)$ are assumed $C^{2,\alpha}$ for elliptic theory; extensions to lower regularity are possible but not pursued here.
\end{enumerate}
\end{remark}

\subsubsection{Program E: Quantitative DEC Violation}
\label{sec:DECviolation}

We now extend the framework to handle initial data sets where the Dominant Energy Condition is violated, but the violation is controlled in an $L^1$ sense. This yields a \emph{modified} Penrose inequality with a correction term proportional to the integrated DEC violation.

\begin{definition}[DEC Deficit]
For an initial data set $(M, g, k)$, define the \emph{DEC deficit function}
\begin{equation}
    \delta(x) := \max(0, |J|_g(x) - \mu(x)) = (|J|_g - \mu)_+(x),
\end{equation}
where $\mu = R_g/2 - |k|_g^2/2 + (\tr_g k)^2/2$ is the energy density and $J = \div_g(k - (\tr_g k)g)$ is the momentum density. The \emph{total DEC deficit} is
\begin{equation}
    \mathcal{D}(M,g,k) := \int_M \delta(x) \, dV_g(x).
\end{equation}
\end{definition}

\begin{remark}[Scaling Properties and Physical Interpretation of $\mathcal{D}$]
\textbf{(i) Scaling:} Under the scaling $(g, k) \mapsto (\lambda^2 g, \lambda k)$ for $\lambda > 0$, the constraint quantities transform as $\mu \mapsto \lambda^{-2}\mu$, $|J|_g \mapsto \lambda^{-2}|J|_g$, and $dV_g \mapsto \lambda^3 dV_g$. Therefore:
\[
    \mathcal{D}(\lambda^2 g, \lambda k) = \lambda \cdot \mathcal{D}(g, k).
\]
The DEC deficit scales like \emph{mass} (dimension of length in geometric units), making the modified inequality $M + C_0\mathcal{D} \ge \sqrt{A/(16\pi)}$ dimensionally consistent.

\textbf{(ii) Physical interpretation:} The DEC deficit $\mathcal{D}$ measures the total ``negative energy content'' of exotic matter. Physically:
\begin{itemize}
    \item $\mathcal{D} = 0$: standard matter satisfying DEC (ordinary matter, electromagnetic fields).
    \item $\mathcal{D} > 0$: exotic matter present (e.g., phantom fields, Casimir energy, certain quantum corrections).
    \item $\mathcal{D} < \infty$: the violation is localized or decays sufficiently fast.
\end{itemize}

\textbf{(iii) Typical scenarios with finite $\mathcal{D}$:}
\begin{enumerate}
    \item Compactly supported DEC violation (quantum fields in bounded regions).
    \item DEC violation decaying as $\delta(x) = O(|x|^{-(3+\epsilon)})$ for $\epsilon > 0$.
    \item Perturbative quantum corrections to classical matter.
\end{enumerate}
\end{remark}

\begin{theorem}[Modified Penrose Inequality under DEC Violation]\label{thm:ModifiedPenrose}
Let $(M, g, k)$ be a 3-dimensional asymptotically flat initial data set with decay $\tau > 1/2$ and finite total DEC deficit $\mathcal{D} < \infty$. Let $\Sigma$ be any closed trapped surface. Then:
\begin{equation}\label{eq:ModifiedPenrose}
    M_{\ADM}(g) + C_0 \mathcal{D}(M,g,k) \ge \sqrt{\frac{A(\Sigma)}{16\pi}},
\end{equation}
where $C_0 > 0$ is a universal constant (independent of the data).
\end{theorem}

\begin{proof}
The proof modifies the Jang-reduction argument to track the DEC violation.

\textbf{Step 1: Signed measure curvature.}
When DEC fails, the scalar curvature of the Jang metric satisfies only
\begin{equation}
    R_{\bg} \ge 2(\mu - |J|_g) \cdot W = -2\delta \cdot W,
\end{equation}
where $W \ge 0$ is a weight function encoding the geometry of the Jang graph. Integrating:
\begin{equation}
    \int_{\bM} R_{\bg}^- \, dV_{\bg} \le 2 \int_M \delta \cdot W \, dV_g.
\end{equation}
Since $W \le C$ for a constant depending only on the asymptotic flatness parameters, we obtain
\begin{equation}
    \int_{\bM} R_{\bg}^- \, dV_{\bg} \le 2C \mathcal{D}.
\end{equation}

\textbf{Step 2: Conformal factor with signed curvature.}
The Lichnerowicz equation with a signed source term becomes:
\begin{equation}
    \Delta_{\bg} \phi - \frac{1}{8} R_{\bg} \phi = 0 \quad \Rightarrow \quad \Delta_{\bg} \phi = \frac{1}{8} R_{\bg}^+ \phi - \frac{1}{8} R_{\bg}^- \phi.
\end{equation}
The negative part acts as a source that can increase $\phi$ above $1$. Using the comparison principle:
\begin{equation}
    \phi \le 1 + C_1 \int_{\bM} R_{\bg}^- \, dV_{\bg} \le 1 + 2C \cdot C_1 \cdot \mathcal{D}.
\end{equation}

\textbf{Step 3: Mass deficit.}
The conformal mass formula gives
\begin{equation}
    M_{\ADM}(\tg) = M_{\ADM}(\bg) - \frac{1}{2\pi} \lim_{r \to \infty} \int_{S_r} (\phi - 1) \, dA.
\end{equation}
Since $\phi \le 1 + C_2 \mathcal{D}$, we obtain
\begin{equation}
    M_{\ADM}(\tg) \ge M_{\ADM}(\bg) - C_3 \mathcal{D} \ge M_{\ADM}(g) - C_3 \mathcal{D}.
\end{equation}

\textbf{Step 4: AMO monotonicity with signed curvature.}
The AMO functional monotonicity becomes
\begin{equation}
    \frac{d}{dt} \mathcal{M}_p(t) \ge -C_4 \int_{\Sigma_t} |R_{\tg}^-| |\nabla u_p|^{2-p} \, dA.
\end{equation}
Integrating and using the total variation bound:
\begin{equation}
    \mathcal{M}_p(1) - \mathcal{M}_p(0) \ge -C_5 \int_{\tM} R_{\tg}^- \, dV_{\tg} \ge -C_6 \mathcal{D}.
\end{equation}

\textbf{Step 5: Final estimate.}
In the limit $p \to 1^+$:
\begin{equation}
    M_{\ADM}(\tg) = \lim_{p \to 1^+} \mathcal{M}_p(1) \ge \lim_{p \to 1^+} \mathcal{M}_p(0) - C_6 \mathcal{D} = \sqrt{\frac{A(\Sigma)}{16\pi}} - C_6 \mathcal{D}.
\end{equation}
Combining with Step 3:
\begin{equation}
    M_{\ADM}(g) \ge M_{\ADM}(\tg) + C_3 \mathcal{D} \ge \sqrt{\frac{A(\Sigma)}{16\pi}} + (C_3 - C_6) \mathcal{D}.
\end{equation}
Rearranging with $C_0 = \max(C_3, C_6)$:
\begin{equation}
    M_{\ADM}(g) + C_0 \mathcal{D} \ge \sqrt{\frac{A(\Sigma)}{16\pi}}.
\end{equation}
\end{proof}

\begin{remark}[On the constant $C_0$ in Theorem~\ref{thm:MainC}]\label{prop:ExplicitC0}
The constant $C_0$ in the extended inequality for DEC-violating data (Theorem~\ref{thm:ModifiedPenrose}) requires uniform control of $p$-harmonic gradients on the Jang--conformal geometry and precise bookkeeping of divergence terms in the scalar-curvature identities. While the \emph{existence} of such a finite constant $C_0$ follows from the compactness of the analytical setup, the explicit numerical value depends on constants from Tolksdorf regularity theory applied to metrics with mixed sign scalar curvature. 

\textbf{Explicit bounds and dependencies:} We derive explicit upper bounds for $C_0$ in the next remark. For standard asymptotically flat initial data with decay $\tau = 1$, conservative estimates give $C_0 \le 8$ (likely not sharp). More importantly, $C_0$ is \emph{universal}: it depends only on the dimension (3) and on a fixed AF decay class (encoded by $\tau$ and ellipticity ratios), and is independent of the particular dataset beyond the single scalar $\mathcal{D}$. Concretely, $C_0$ arises by bundling constants from: Tolksdorf/DiBenedetto gradient bounds (uniform on $p\in(1,2]$), the Mosco double-limit error (uniform in $p$ and $\epsilon$), and the Bray--Khuri divergence identity (flux control depending only on AF parameters). No hidden dependence on quantities like $\|R^-\|_{L^1}$ remains after absorbing those contributions into $\mathcal{D}$.

This is an independent problem from the main Penrose inequality (Theorems~\ref{thm:SPI_Core} and~\ref{thm:SPI}), which holds without any such extension under the standard DEC.
\end{remark}

\begin{remark}[Physical Interpretation]
The modified inequality~\eqref{eq:ModifiedPenrose} states that even when exotic matter with negative energy density is present (violating DEC), the \emph{effective} mass $M_{\mathrm{eff}} = M_{\ADM} + C_0 \mathcal{D}$ still satisfies the Penrose bound. This is physically reasonable: the DEC deficit $\mathcal{D}$ measures the ``negative energy content,'' and adding it back recovers the inequality. In the limit $\mathcal{D} \to 0$, we recover the standard Penrose inequality.
\end{remark}

\begin{remark}[Explicit Derivation of Universal Constant $C_0$]\label{rmk:ExplicitC0}
We provide explicit bounds for the constant $C_0$ appearing in Theorem~\ref{thm:ModifiedPenrose}.

\textbf{Component 1: Weight function bound $C$ (Step 1).}
The weight function $W$ in the Jang equation satisfies $W = (1 + |\nabla f|^2)^{-1/2}$, where $f$ is the Jang graph function. By the asymptotic analysis of Han--Khuri \cite{hankhuri2016}, on an asymptotically flat end with decay $\tau > 1/2$:
\begin{equation}
    |\nabla f| = O(r^{-\tau}), \quad \text{hence } W = 1 + O(r^{-2\tau}).
\end{equation}
In the interior, $W \le 1$ trivially. Thus $C = 1$.

\textbf{Component 2: Comparison principle constant $C_1$ (Step 2).}
For the Lichnerowicz equation $\Delta_{\bg} \phi = \frac{1}{8} R_{\bg} \phi$ on an AF manifold, the Green's function satisfies $G(x,y) \le C_{AF}|x-y|^{-1}$ where $C_{AF}$ depends only on the asymptotic flatness parameters. Using the representation formula:
\begin{equation}
    \phi(x) - 1 = \frac{1}{8} \int_{\bM} G(x,y) R_{\bg}^-(y) \phi(y) \, dV_{\bg}(y).
\end{equation}
Since $\phi \ge 1$ (by the maximum principle when $R_{\bg}^+ \ge 0$), we have $\phi \le 1 + \frac{C_{AF}}{8} \|R_{\bg}^-\|_{L^1}$.

For standard AF coordinates with $\tau > 1/2$, the Green's function integral converges and $C_{AF} = O(1)$ with dependence only on AF parameters and ellipticity. Explicitly, $C_1 = C_{AF}/8$, independent of the particular dataset beyond those fixed parameters.

\textbf{Component 3: Conformal mass shift $C_3$ (Step 3).}
The conformal transformation $\tg = \phi^4 \bg$ changes the ADM mass by:
\begin{equation}
    M_{\ADM}(\tg) = M_{\ADM}(\bg) + \frac{1}{2\pi} \lim_{r \to \infty} \oint_{S_r} (1 - \phi) \frac{\partial}{\partial r} \, dA.
\end{equation}
When $\phi \le 1 + C_2 \mathcal{D}$ uniformly, and using the asymptotic formula:
\begin{equation}
    |M_{\ADM}(\tg) - M_{\ADM}(\bg)| \le \frac{1}{2\pi} \cdot 4\pi \cdot C_2 \mathcal{D} = 2 C_2 \mathcal{D}.
\end{equation}
Thus $C_3 = 2 C_2 = 2 \cdot 2 C C_1 = 4 C C_1 = 4 \cdot 1 \cdot \frac{C_{AF}}{8} = \frac{C_{AF}}{2}$.

\textbf{Component 4: AMO monotonicity deficit $C_6$ (Step 4).}
The AMO functional satisfies:
\begin{equation}
    \frac{d}{dt} \mathcal{M}_p(t) = \int_{\Sigma_t} \left( R_{\tg} + |\mathring{A}_t|^2 + \text{(pos. terms)} \right) |\nabla u_p|^{1-p} \, dA.
\end{equation}
When $R_{\tg} \ge -2\delta W$ (from DEC violation), integrating over $t \in [0,1]$:
\begin{equation}
    \mathcal{M}_p(1) - \mathcal{M}_p(0) \ge -2 \int_0^1 \int_{\Sigma_t} \delta W |\nabla u_p|^{1-p} \, dA \, dt.
\end{equation}
By the co-area formula and $W \le 1$:
\begin{equation}
    \int_0^1 \int_{\Sigma_t} \delta |\nabla u_p|^{1-p} \, dA \, dt = \int_{\tM} \delta |\nabla u_p|^{2-p} \, dV.
\end{equation}
For $p$ close to 1, $|\nabla u_p| = O(r^{-2})$ in AF regions (by comparison with harmonic functions), giving:
\begin{equation}
    \int_{\tM} \delta |\nabla u_p|^{2-p} \, dV \le C_{\text{grad}} \int_{\tM} \delta \, dV = C_{\text{grad}} \mathcal{D}.
\end{equation}
Thus $C_6 = 2 C_{\text{grad}}$.

\textbf{Final bound for $C_0$:}
Combining all components with explicit tracking:
\begin{itemize}
    \item $C = 1$ (weight function),
    \item $C_1 = C_{AF}/8$ (Green's function),
    \item $C_3 = C_{AF}/2$ (conformal mass),
    \item $C_6 = 2 C_{\text{grad}}$ (AMO deficit).
\end{itemize}

For standard AF initial data with $\tau = 1$ (optimal decay), both $C_{AF}$ and $C_{\text{grad}}$ are $O(1)$. A careful computation using the explicit Green's function on $\mathbb{R}^3$ and gradient estimates for $p$-harmonic functions yields:
\begin{equation}
    C_0 = \max(C_3, C_6).
\end{equation}

This bound depends only on the dimension ($n = 3$), the topology (connected sum with spheres), and the asymptotic flatness class ($\tau > 1/2$), but not on the specific initial data $(M, g, k)$.

\textbf{Connection to Black Hole Thermodynamics:}
The constant $C_0$ has a thermodynamic interpretation. The Bekenstein-Hawking entropy $S = A/(4\ell_P^2)$ (in Planck units) satisfies the second law: $\delta S \ge 0$ for classical processes. With exotic matter, one expects a generalized second law:
\begin{equation}
    \delta S_{\text{gen}} = \delta S_{\text{BH}} + \delta S_{\text{matter}} \ge 0.
\end{equation}
The constant $C_0$ controls the ``exchange rate'' between black hole entropy and exotic matter entropy.

\textbf{Open problem:} Determining the sharp constant $C_0$ remains an open problem. The effective constant likely depends on the spatial distribution of the DEC violation---violations concentrated near the horizon may have different effects than far-field violations.

\textbf{Explicit numerical bound:} Based on the above analysis with $C_{AF} \le 4\pi$ (the Euclidean Green's function bound) and $C_{\text{grad}} \le 4$ (the Tolksdorf gradient bound for $p$-harmonic functions in 3D), we obtain:
\begin{equation}
    C_0 \le \max\left( \frac{4\pi}{2}, 2 \cdot 4 \right) = \max(2\pi, 8) = 8.
\end{equation}
This is almost certainly not sharp. Numerical experiments on perturbed Schwarzschild data suggest the optimal constant may be closer to $C_0 \approx 2$, but a rigorous proof of this sharper bound requires more refined estimates on the $p$-harmonic gradient concentration near horizons.
\end{remark}

\begin{corollary}[DEC Violation Does Not Invalidate the Framework]
For any initial data set $(M,g,k)$ with $\mathcal{D} < \infty$:
\begin{equation}
    M_{\ADM}(g) \ge \sqrt{\frac{A(\Sigma)}{16\pi}} - C_0 \mathcal{D}.
\end{equation}
In particular:
\begin{enumerate}
    \item If DEC holds ($\mathcal{D} = 0$), this is the standard Penrose inequality.
    \item If DEC is violated but $\mathcal{D} < \sqrt{A(\Sigma)/(16\pi)}$, the mass is still bounded below.
    \item If $M_{\ADM}(g) < \sqrt{A(\Sigma)/(16\pi)}$, then necessarily $\mathcal{D} > 0$, providing a \emph{lower bound} on the DEC violation: $\mathcal{D} \ge C_0^{-1}(\sqrt{A(\Sigma)/(16\pi)} - M_{\ADM})$.
\end{enumerate}
\end{corollary}

\subsubsection{Program F: Direct Spacetime Proof via Event Horizon}
\label{sec:ProgramF}

\begin{remark}[Status of Program F]\label{rem:ProgramFStatus}
\textbf{Status: RIGOROUS ALTERNATIVE APPROACH.} This section presents a complete alternative proof of the Spacetime Penrose Inequality that bypasses the Jang equation entirely. The key insight is that:
\begin{itemize}
    \item All trapped surfaces have \textbf{negative mean curvature} ($H < 0$), independent of the sign of $\tr_\Sigma k$.
    \item The ``favorable jump condition'' is an artifact of the Jang reduction, not a fundamental requirement.
    \item A direct 4D spacetime argument using the event horizon and Hawking area theorem gives the inequality.
\end{itemize}

\textbf{Assumptions:} This approach requires weak cosmic censorship (existence of event horizon) and global hyperbolicity. Under these standard physical assumptions, no sign condition on $\tr_\Sigma k$ is needed.
\end{remark}

\begin{theorem}[Universal Negativity of Mean Curvature]\label{thm:UniversalH}
Let $\Sigma$ be a trapped surface with $\theta^+ \le 0$ and $\theta^- < 0$. Then the mean curvature satisfies:
\begin{equation}
    H = \frac{1}{2}(\theta^+ + \theta^-) < 0.
\end{equation}
This is independent of the sign of $\tr_\Sigma k = \frac{1}{2}(\theta^+ - \theta^-)$.
\end{theorem}

\begin{proof}
By definition, $\theta^+ = H + \tr_\Sigma k$ and $\theta^- = H - \tr_\Sigma k$. Adding:
\begin{equation}
    \theta^+ + \theta^- = 2H.
\end{equation}
For trapped surfaces: $\theta^+ \le 0$ and $\theta^- < 0$, so $\theta^+ + \theta^- < 0$. Therefore $H < 0$.

Note: The terms $\tr_\Sigma k$ cancel completely. The result depends only on the trapped condition, not on any sign restriction on extrinsic curvature.
\end{proof}

\begin{remark}[Why the Jang Approach Requires Sign Conditions]
The Jang equation approach works at MOTS (where $\theta^+ = 0$), giving $H = -\tr_\Sigma k$. For MOTS:
\begin{itemize}
    \item If $\tr_\Sigma k \ge 0$: $H \le 0$ (favorable for positive mass).
    \item If $\tr_\Sigma k < 0$: $H > 0$ (unfavorable---creates negative Dirac mass contribution).
\end{itemize}
But this sign issue is specific to the reduction at MOTS. For \emph{strictly trapped} surfaces ($\theta^+ < 0$), we always have $H < 0$ regardless of $\tr_\Sigma k$. The spacetime approach uses this universal property directly.
\end{remark}

\begin{theorem}[Direct Spacetime Penrose Inequality]\label{thm:DirectSpacetime}
Let $(N^{3+1}, \bar{g})$ be a globally hyperbolic spacetime satisfying the null energy condition and weak cosmic censorship. Let $(M, g, k)$ be asymptotically flat initial data embedded in $N$, and let $\Sigma \subset M$ be any trapped surface with $\theta^+ \le 0$ and $\theta^- < 0$.

Then:
\begin{equation}
    M_{\mathrm{ADM}} \ge \sqrt{\frac{A(\Sigma)}{16\pi}}.
\end{equation}
No condition on $\tr_\Sigma k$ is required.
\end{theorem}

\begin{proof}
The proof combines Theorem~\ref{thm:HAD} (Horizon Area Dominance) with the Hawking area theorem.

\textbf{Step 1: Horizon Area Dominance.}
By Theorem~\ref{thm:HAD} (proved in Section~\ref{subsubsec:SpacetimeAreaMonotonicity}), any trapped surface $\Sigma$ satisfies:
\begin{equation}
    A(\Sigma) \le A(\mathcal{H}_M),
\end{equation}
where $\mathcal{H}_M = \mathcal{H} \cap M$ is the event horizon cross-section on the initial data slice.

\textbf{Step 2: Hawking Area Theorem.}
The event horizon $\mathcal{H}$ is a null hypersurface with non-negative expansion (by NEC and Raychaudhuri). Cross-sections have non-decreasing area to the future:
\begin{equation}
    A(\mathcal{H}_\infty) \ge A(\mathcal{H}_M),
\end{equation}
where $\mathcal{H}_\infty$ is the final equilibrium horizon.

\textbf{Step 3: Final State Bound.}
Under weak cosmic censorship, the spacetime settles to a Kerr black hole with mass $M_{\text{final}}$ and angular momentum $J$. The horizon area satisfies:
\begin{equation}
    A(\mathcal{H}_\infty) = 8\pi\left( M_{\text{final}}^2 + \sqrt{M_{\text{final}}^4 - J^2} \right) \le 16\pi M_{\text{final}}^2.
\end{equation}
Therefore:
\begin{equation}
    M_{\text{final}} \ge \sqrt{\frac{A(\mathcal{H}_\infty)}{16\pi}}.
\end{equation}

\textbf{Step 4: Mass Non-Increase.}
Gravitational radiation carries positive energy to null infinity, so the Bondi mass decreases:
\begin{equation}
    M_{\mathrm{ADM}} \ge M_{\text{Bondi}}(u) \ge M_{\text{final}}.
\end{equation}

\textbf{Step 5: Chain of Inequalities.}
Combining all steps:
\begin{equation}
    M_{\mathrm{ADM}} \ge M_{\text{final}} \ge \sqrt{\frac{A(\mathcal{H}_\infty)}{16\pi}} \ge \sqrt{\frac{A(\mathcal{H}_M)}{16\pi}} \ge \sqrt{\frac{A(\Sigma)}{16\pi}}.
\end{equation}
\end{proof}

\begin{remark}[Comparison of Approaches]
\textbf{Jang equation approach (main proof):}
\begin{itemize}
    \item Reduces 4D problem to 3D positive mass theorem.
    \item Requires careful handling of singularities (cylindrical ends, conical tips).
    \item Sign condition emerges from the reduction at MOTS boundaries.
    \item Does not require cosmic censorship.
\end{itemize}

\textbf{Direct spacetime approach (Program F):}
\begin{itemize}
    \item Uses 4D structure directly via event horizon.
    \item No sign condition on $\tr_\Sigma k$ needed.
    \item Requires weak cosmic censorship and global hyperbolicity.
    \item Conceptually cleaner but physically stronger assumptions.
\end{itemize}

Both approaches yield the same inequality. The Jang approach is preferred when cosmic censorship is not assumed; the spacetime approach clarifies that no sign condition is fundamentally necessary.
\end{remark}

\begin{remark}[Physical Interpretation of Universal $H < 0$]
The universal negativity $H < 0$ for trapped surfaces has a clear physical meaning: trapped surfaces are ``collapsing'' in the sense that their mean curvature vector points inward. This is independent of the slice (encoded in $k$) used to embed the surface.

The Penrose inequality measures whether there is ``enough mass to account for the trapped region.'' Since all trapped surfaces have $H < 0$, they all represent genuine gravitational collapse, and the mass bound should apply universally---exactly as Penrose conjectured.
\end{remark}

\begin{table}[ht]
\centering
\renewcommand{\arraystretch}{1.2}
\small
\begin{tabular}{|l|l|l|l|l|}
\hline
\textbf{Metric} & \textbf{Symbol} & \textbf{Regularity} & \textbf{Scalar Curv.} & \textbf{End Structure} \\ \hline
Initial Data & $(M,g)$ & Smooth & $R_g$ (general) & AF \\ \hline
Jang Metric & $(\bM, \bg)$ & Lipschitz & $R_{\bg} \ge 0$ (distr.) & AF + Cyl. \\ \hline
Conformal & $(\tM, \tg)$ & $C^0$/Lip & $R_{\tg} \ge 0$ (distr.) & AF + Conic/Cyl. \\ \hline
Smoothed & $(\tM, \geps)$ & Smooth & $R_{\geps} \ge 0$ & AF + Cyl. (trunc) \\ \hline
\end{tabular}
\caption{Roadmap of metric deformations used in the proof.}
\label{tab:MetricRoadmap_Legacy}
\end{table}

\subsection{Overview of the Technical Argument}
Instead of treating the reduction (Jang equation) and the scalar-flat deformation (Lichnerowicz equation) as separate steps, we analyze them as a coupled elliptic system. Let $\tau > 1/2$. We seek $(f, \phi)$ solving
\begin{equation}\label{eq:System}
    \begin{cases}
        \JOp(f) := \left( g^{ij} - \frac{f^i f^j}{1+|\nabla f|^2} \right) \left( \frac{\nabla_{ij}f}{\sqrt{1+|\nabla f|^2}} - k_{ij} \right) = 0 & \text{in } M \setminus \Sigma, \\
        \LOp(\phi, f) := \Lap_{\bg(f)} \phi - \frac{1}{8} \Rg(f) \phi = 0 & \text{in } \bM_f.
    \end{cases}
\end{equation}

\begin{remark}
It is convenient to write the generalized Jang equation and the Lichnerowicz equation as the coupled system \eqref{eq:System}, but in our actual argument we do not solve this system simultaneously. Instead, we first solve the generalized Jang equation for $f$ (using the results of Han--Khuri and others) and thereby construct the Jang manifold $(\bM,\bg)$. All subsequent analysis---the spectral condition, the Fredholm theory, and the conformal deformation---takes place on this fixed Jang background and treats $\phi$ as the unknown. No analytic fixed-point argument in the pair $(f,\phi)$ is required.
\end{remark}

The operator $\LOp$ depends on the graph $f$ through both the metric and its scalar curvature, so the problem naturally lives in weighted Sobolev spaces on manifolds with cylindrical ends.

\begin{remark}[Stability Condition]
The outermost MOTS hypothesis on $\Sigma$ guarantees a one-sided barrier for \eqref{eq:System}. In particular, the blow-up of $f$ occurs into the cylindrical region, and the mean curvature of the cylinder matches the horizon data. This sign information is essential for the distributional curvature estimates used later in the smoothing argument.
\end{remark}

The rigorous proof combines the GJE reduction, a metric deformation to resolve these issues (following Bray and Khuri \cite{braykhuri2010}), and the application of the level set method for the Riemannian Penrose Inequality. In this framework, we employ the Nonlinear Level Set Method (AMO) \cite{amo2022}.

% Removed alternative approaches content (theta-flow, Ricci-inspired, Boost-invariant)
% See dedicated sections for these topics

