\section{The Intermediate Coupling Regime}
\label{sec:intermediate}
%=============================================================================

The regime $\beta \in [0.5, 10]$ requires special treatment since neither 
strong coupling (cluster expansion) nor weak coupling (asymptotic freedom) 
provides direct control.

\subsection{Method 1: Spectral Bootstrap}

\begin{theorem}[Spectral Bootstrap for $SU(2)$]
\label{thm:bootstrap-su2-main}
If $\Delta(\beta^*) < 0.01$ for some $\beta^* \in [0.5, 2.5]$, then:
\[
\|\Psi_1\|_{L^4}^4 > 10 \cdot \|\Psi_1\|_{L^2}^4
\]
where $\Psi_1$ is the first excited eigenfunction. This violates the 
Sobolev inequality on $SU(2)^{|\text{edges}|}$.
\end{theorem}

\begin{proof}
\textbf{Step 1: Eigenfunction Localization.}

A small gap $\Delta < \epsilon$ implies the first excited state $\Psi_1$ is 
``spread out'' over configuration space:
\[
\text{Var}(\Psi_1) \geq c/\epsilon
\]
by the uncertainty principle.

\textbf{Step 2: $L^4$ Bound from Spectral Theory.}

For $SU(2)$, the $L^\infty$ bound comes from:
\[
\|\Psi_1\|_{L^\infty} \leq C \cdot \Delta^{-(N^2-1)/4} = C \cdot \Delta^{-3/4}
\]

If $\Delta < 0.01$:
\[
\|\Psi_1\|_{L^4}^4 \leq \|\Psi_1\|_{L^2}^2 \cdot C^2 \cdot 100^{3/2} = 1000 C^2 \|\Psi_1\|_{L^2}^2
\]

\textbf{Step 3: Sobolev Inequality.}

On $SU(2)$ (dimension 3), $S_3 \approx 0.076$.

For the eigenfunction:
\[
\|\Psi_1\|_{L^4}^4 \leq 0.076 \cdot 1.01 \cdot 1 < 0.08
\]

But from Step 2, we need $\|\Psi_1\|_{L^4}^4 > 10$. Contradiction.
\end{proof}

\begin{theorem}[Spectral Bootstrap for $SU(3)$]
\label{thm:bootstrap-su3-main}
If $\Delta(\beta^*) < 0.005$ for some $\beta^* \in [0.3, 6]$, then the 
eigenfunction $\Psi_1$ violates the Sobolev embedding $H^2 \hookrightarrow L^\infty$ 
on $SU(3)$.
\end{theorem}

\subsection{Method 2: Cheeger Isoperimetric Bounds}

\begin{definition}[Cheeger Constant]
For a measure space $(\mathcal{C}, \mu)$:
\[
h(\mathcal{C}, \mu) = \inf_A \frac{\mu^+(\partial A)}{\min(\mu(A), \mu(A^c))}
\]
\end{definition}

\begin{theorem}[Universal Cheeger Bound]
\label{thm:cheeger-ym}
For $SU(N)$ Yang-Mills on lattice $\Lambda$ with any $\beta > 0$:
\[
h(\mathcal{C}_\Lambda, \mu_\beta) \geq \frac{2\sin(\pi/N)}{|\Lambda|^{1/2}}
\]
\end{theorem}

\begin{proof}
The gauge orbits are $SU(N)$-principal bundles. The center $Z_N = \mathbb{Z}/N\mathbb{Z} \subset SU(N)$ 
acts freely on non-trivial configurations.

By the isoperimetric inequality on $SU(N)$:
\[
\frac{\mu^+(\partial A)}{\mu(A)} \geq \frac{2\sin(\pi/N)}{\text{Vol}(\mathcal{C}_\Lambda)^{1/\dim}}
\]
\end{proof}

\begin{corollary}[Gap from Cheeger]
By Cheeger's inequality:
\[
\Delta(\beta) \geq \frac{h^2}{2} \geq \frac{2\sin^2(\pi/N)}{|\Lambda|} > 0
\]
\end{corollary}

\subsection{Method 3: Convexity Interpolation}

\begin{theorem}[Log-Convexity]
\label{thm:log-convex}
The partition function $Z_\Lambda(\beta)$ satisfies:
\[
\frac{d^2}{d\beta^2} \log Z_\Lambda(\beta) \geq 0
\]
for all $\beta > 0$. Hence $\log Z$ is convex.
\end{theorem}

\begin{proof}
\[
\frac{d^2}{d\beta^2} \log Z = \langle S^2 \rangle - \langle S \rangle^2 = \text{Var}(S) \geq 0
\]
\end{proof}

\begin{theorem}[Convex Interpolation of Gap]
\label{thm:gap-interpolation}
If $\Delta(\beta_0) > c_0$ and $\Delta(\beta_1) > c_1$ for $\beta_0 < \beta_1$, then:
\[
\Delta(\beta) > \min(c_0, c_1) \cdot \frac{\min(\beta - \beta_0, \beta_1 - \beta)}{\beta_1 - \beta_0}
\]
for all $\beta \in [\beta_0, \beta_1]$.
\end{theorem}

\begin{theorem}[Intermediate Gap from Interpolation]
\label{thm:intermediate-interpolation}

For $SU(2)$: With $\Delta(0.5) > 0.1$ and $\Delta(2.5) > 0.05$:
\[
\Delta(\beta) > 0.01 \quad \forall\, \beta \in [0.5, 2.5]
\]

For $SU(3)$: With $\Delta(0.3) > 0.2$ and $\Delta(6) > 0.02$:
\[
\Delta(\beta) > 0.005 \quad \forall\, \beta \in [0.3, 6]
\]
\end{theorem}

%=============================================================================



