\documentclass[11pt, a4paper]{article}
\usepackage{amsmath, amssymb, amsthm}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{tikz-cd}
\usepackage[numbers,sort&compress]{natbib}

\geometry{margin=1in}

\title{Adelic Geometry and the Geometric Flow of Primes}
\author{Agentic Research Group}
\date{}

\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\newtheorem{theorem}{Theorem}[section]

\newcommand{\A}{\mathbb{A}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Id}{\mathbb{I}}
\newcommand{\R}{\mathbb{R}}

\begin{document}

\maketitle

\begin{abstract}
The space of adele classes $\A_\Q / \Q^*$ plays a central role in the spectral interpretation of the Riemann zeta function, particularly in the work of Connes. We investigate the geometric flow on this space induced by the scaling action of the idele class group, interpreting it as the "arithmetic time" evolution in Chrono-Topological Field Theory.
\end{abstract}

\section{Introduction}

Connes \cite{Connes1999} identified the critical zeros as absorption lines in the spectrum of the scaling action on the adele class space. We extend this by defining a geometric flow that deforms the metric on the adelic space, seeking a fixed point where the symmetry of the adele class group is restored.

\section{The Adelic Space}

\begin{definition}[Adeles]
The ring of adeles $\A_\Q$ is the restricted product of $\R$ and the fields of $p$-adic numbers $\Q_p$ for all primes $p$:
\begin{equation}
    \A_\Q = \R \times {\prod_{p}}' \Q_p = \left\{ (x_\infty, x_2, x_3, \dots) \mid x_p \in \Z_p \text{ for almost all } p \right\}
\end{equation}
\end{definition}
The group of units of this ring is the Idele group $\Id_\Q$. The quotient space $\CTS = \A_\Q / \Q^*$ is the fundamental arena for global class field theory.

\section{The Scaling Action}

The idele class group $C_\Q = \Id_\Q / \Q^*$ acts on the space of adele classes. This action is identified with the time evolution of the arithmetic system.
Let $\lambda \in C_\Q$. The scaling operator $V_\lambda$ acts on $L^2(\CTS)$ by:
\begin{equation}
    (V_\lambda f)(x) = f(\lambda x)
\end{equation}
The Trace Formula for this action is equivalent to the Explicit Formula for the Riemann zeta function.

\section{Geometric Flow}

We propose a flow on the moduli space of metrics on $\CTS$. Let $g_t$ be a family of metrics parameterised by $t$. We postulate the flow equation:
\begin{equation}
    \frac{\partial g}{\partial t} = -2 \text{Ric}(g) + \mathcal{L}_V g
\end{equation}
where $V$ is the vector field generating the scaling action. This is an analogue of the Ricci flow, designed to smooth out "arithmetic curvature" concentrated at the prime places.

\bibliographystyle{plainnat}
\bibliography{references}

\end{document}
