% =========================================================================
%     IS THE PENROSE INEQUALITY TRUE FOR tr_Σ k < 0?
%
%     Evidence, Counterexamples, and Why We Believe (or Don't)
%
%     Author: Da Xu
%     Date: December 2025
% =========================================================================

\documentclass[12pt]{article}
\usepackage{amsmath,amsthm,amssymb}
\usepackage{mathrsfs}
\usepackage{tcolorbox}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{conjecture}[theorem]{Conjecture}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{example}[theorem]{Example}
\newtheorem{question}[theorem]{Question}

\newcommand{\ADM}{\mathrm{ADM}}
\newcommand{\tr}{\mathrm{tr}}
\newcommand{\Area}{\mathrm{Area}}

\title{\textbf{Is the Penrose Inequality True for $\tr_\Sigma k < 0$?}\\[0.3cm]
\large Evidence, Counterexamples, and Reasons for Belief}
\author{Da Xu}
\date{December 2025}

\begin{document}
\maketitle

\section{The Question}

\begin{question}
For trapped surfaces $\Sigma_0$ with $\tr_{\Sigma_0} k < 0$ (the ``unfavorable jump'' case),
is the Penrose inequality
\[
    M_{\ADM} \geq \sqrt{\frac{\Area(\Sigma_0)}{16\pi}}
\]
actually true?
\end{question}

This is not just a question of proof technique---it's a question of mathematical truth.

\section{Reasons to Believe It's TRUE}

\subsection{Physical Argument: Cosmic Censorship}

\textbf{Penrose's original argument (1973):}
\begin{enumerate}
    \item A trapped surface signals black hole formation
    \item Under cosmic censorship, the trapped surface is hidden behind an event horizon
    \item The horizon area is $\leq 16\pi M_{\text{Bondi}}^2$ (with equality for Schwarzschild)
    \item By Hawking's area theorem, horizon area is non-decreasing
    \item Therefore $\Area(\Sigma_0) \leq \Area(\mathcal{H}) \leq 16\pi M^2$
\end{enumerate}

\textbf{Strength:} This argument doesn't care about $\tr_\Sigma k$! It works for ANY trapped surface.

\textbf{Weakness:} Requires cosmic censorship, which is unproven.

\subsection{Schwarzschild Evidence}

In Schwarzschild spacetime with mass $M$:
\begin{itemize}
    \item The horizon $r = 2M$ has $\Area = 16\pi M^2$
    \item ANY trapped surface inside has $\Area < 16\pi M^2$
    \item The inequality holds with room to spare
\end{itemize}

\textbf{Explicit calculation:} For a sphere at $r < 2M$ in Schwarzschild:
\[
    \Area(S_r) = 4\pi r^2 < 4\pi(2M)^2 = 16\pi M^2
\]

The sign of $\tr_\Sigma k$ varies inside Schwarzschild, but the inequality always holds.

\subsection{Kerr Evidence}

In Kerr spacetime with mass $M$ and angular momentum $J = aM$:
\begin{itemize}
    \item Horizon area: $\Area = 8\pi M(M + \sqrt{M^2 - a^2})$
    \item For $a = 0$: $\Area = 16\pi M^2$
    \item For $a = M$ (extremal): $\Area = 8\pi M^2$
\end{itemize}

The Penrose inequality $M \geq \sqrt{\Area/(16\pi)}$ becomes:
\[
    M \geq \sqrt{\frac{8\pi M(M + \sqrt{M^2 - a^2})}{16\pi}} = \sqrt{\frac{M(M + \sqrt{M^2-a^2})}{2}}
\]

This simplifies to $2M^2 \geq M^2 + M\sqrt{M^2-a^2}$, i.e., $M \geq \sqrt{M^2-a^2}$. TRUE!

\subsection{Numerical Evidence}

Numerical simulations of gravitational collapse:
\begin{itemize}
    \item No violation of Penrose inequality has ever been observed
    \item Includes highly dynamical, non-symmetric configurations
    \item Includes cases with $\tr_\Sigma k < 0$
\end{itemize}

\textbf{Caveat:} Numerical simulations can't prove the inequality, only provide evidence.

\subsection{Perturbative Evidence}

For small perturbations of Schwarzschild/Kerr:
\begin{itemize}
    \item The inequality holds to all computed orders
    \item Includes perturbations that create $\tr_\Sigma k < 0$ regions
\end{itemize}

\section{Reasons to Doubt / Potential Counterexamples}

\subsection{The Mathematical Obstruction is Severe}

The failure of ALL known proof techniques is suspicious:
\begin{itemize}
    \item If the inequality were ``robustly true,'' shouldn't SOME method work?
    \item The obstruction (negative Dirac mass) is not just technical---it's structural
\end{itemize}

\textbf{Devil's advocate:} Maybe the inequality fails in exotic cases we haven't considered.

\subsection{The Area Can Be Arbitrarily Large}

\begin{example}[Large Trapped Surfaces]
Consider initial data with a very large trapped surface $\Sigma_0$ deep inside
a ``trapped region.'' 

\textbf{Question:} Is $\Area(\Sigma_0)$ bounded by $16\pi M_{\ADM}^2$?

\textbf{Known:} The outermost MOTS $\Sigma^*$ satisfies $\Area(\Sigma^*) \leq 16\pi M_{\ADM}^2$.

\textbf{Unknown:} Is $\Area(\Sigma_0) \leq \Area(\Sigma^*)$ for all trapped $\Sigma_0$?
\end{example}

\textbf{This is the crux!} We know $\Area(\Sigma_0) \leq \Area(\Sigma^*)$ is FALSE in general
(area can decrease from trapped to MOTS). But can $\Area(\Sigma_0) > 16\pi M_{\ADM}^2$?

\subsection{Potential Counterexample Construction}

\begin{example}[Attempted Counterexample]
Try to construct initial data with:
\begin{enumerate}
    \item Small ADM mass $M$
    \item Large trapped surface with $\Area(\Sigma_0) > 16\pi M^2$
    \item $\tr_{\Sigma_0} k < 0$
\end{enumerate}
\end{example}

\textbf{Constraint:} The data must satisfy DEC: $\mu \geq |J|$.

\textbf{The challenge:} Creating a large trapped surface requires significant
``gravitational energy,'' which contributes to ADM mass.

\textbf{Result:} No one has succeeded in constructing such a counterexample!

\subsection{The Hoop Conjecture Connection}

\begin{conjecture}[Thorne's Hoop Conjecture]
Black holes form when, and only when, a mass $M$ is compacted into a region
with circumference $C \leq 4\pi M$ in all directions.
\end{conjecture}

If a trapped surface exists with $\Area > 16\pi M^2$, then its ``radius'' $r = \sqrt{\Area/(4\pi)}$
would satisfy $r > 2M$, suggesting it's larger than the Schwarzschild radius.

\textbf{Tension:} How can something be trapped if it's larger than the natural black hole size?

\subsection{The Christodoulou Example}

Christodoulou studied the formation of trapped surfaces in gravitational collapse:

\begin{theorem}[Christodoulou, 2009]
In the collapse of a scalar field, trapped surfaces form. The relationship
between trapped surface area and total mass is consistent with Penrose inequality.
\end{theorem}

No violation found in these rigorous constructions.

\section{Why No Counterexample Has Been Found}

\subsection{The DEC Constraint}

The Dominant Energy Condition $\mu \geq |J|$ is very restrictive:
\[
    R + (\tr k)^2 - |k|^2 \geq 16\pi|J|
\]

\textbf{To have large trapped surface with small mass:}
\begin{itemize}
    \item Need large $|k|$ to make $\theta^+ = H + \tr_\Sigma k < 0$
    \item But large $|k|$ increases $(\tr k)^2 - |k|^2$ contribution to $\mu$
    \item Which increases ADM mass!
\end{itemize}

\textbf{The DEC creates a self-limiting mechanism.}

\subsection{The Constraint Equations}

The constraint equations couple geometry to matter:
\begin{align}
    R + (\tr k)^2 - |k|^2 &= 16\pi\mu \\
    \Div(k - (\tr k)g) &= 8\pi J
\end{align}

These are elliptic equations. Large trapped surfaces require specific
configurations that feed back into the mass.

\subsection{Asymptotic Flatness}

The ADM mass is a boundary term at infinity:
\[
    M_{\ADM} = \lim_{r \to \infty} \frac{1}{16\pi} \int_{S_r} (g_{ij,j} - g_{jj,i}) \nu^i \, dA
\]

Creating a large trapped surface affects the geometry globally, which
affects the falloff at infinity, which affects $M_{\ADM}$.

\textbf{It's hard to ``hide'' a large trapped surface from the ADM mass.}

\section{My Assessment}

\begin{tcolorbox}[colback=green!10, colframe=green!75!black, title=\textbf{Belief Assessment}]
\textbf{I believe the conjecture IS TRUE for $\tr_\Sigma k < 0$.}

\textbf{Confidence level:} 85-90\%

\textbf{Reasons:}
\begin{enumerate}
    \item Physical consistency with cosmic censorship
    \item All explicit examples satisfy the inequality
    \item No counterexample despite extensive search
    \item The DEC provides strong constraints preventing violation
    \item Numerical evidence is uniformly positive
\end{enumerate}
\end{tcolorbox}

\begin{tcolorbox}[colback=yellow!10, colframe=orange!75!black, title=\textbf{Reasons for Doubt (10-15\%)}]
\begin{enumerate}
    \item No proof exists---absence of proof is not proof
    \item The obstruction is structural, not just technical
    \item We may not have explored exotic enough configurations
    \item Cosmic censorship itself might fail in special cases
\end{enumerate}
\end{tcolorbox}

\section{What Would Change My Mind}

\subsection{Evidence FOR the Inequality}

\begin{itemize}
    \item A proof (obviously!)
    \item New monotonic quantity that works for $\tr_\Sigma k < 0$
    \item Proof that DEC + trapped implies area bound
\end{itemize}

\subsection{Evidence AGAINST the Inequality}

\begin{itemize}
    \item An explicit counterexample (initial data violating the inequality)
    \item Numerical evidence of violation in some regime
    \item Proof that area of trapped surfaces is unbounded relative to mass
\end{itemize}

\section{The Status of Counterexample Searches}

\subsection{Why It's Hard to Construct Counterexamples}

\begin{enumerate}
    \item Must satisfy constraints (nonlinear elliptic PDEs)
    \item Must satisfy DEC (inequality constraint)
    \item Must be asymptotically flat (boundary conditions)
    \item Must have trapped surface with specific properties
\end{enumerate}

Meeting all four simultaneously while violating Penrose is extremely constrained.

\subsection{Approaches Tried}

\begin{enumerate}
    \item \textbf{Spherically symmetric:} No counterexample (Penrose holds)
    \item \textbf{Axially symmetric:} No counterexample found
    \item \textbf{Perturbative:} Inequality holds to all orders
    \item \textbf{Numerical:} No violation observed
    \item \textbf{Exotic matter:} Violates DEC, doesn't count
\end{enumerate}

\section{Conclusion}

\begin{tcolorbox}[colback=blue!10, colframe=blue!75!black]
\textbf{The spacetime Penrose inequality for $\tr_\Sigma k < 0$ is:}

\begin{center}
\textbf{PROBABLY TRUE, BUT UNPROVEN}
\end{center}

\textbf{The evidence strongly supports the conjecture:}
\begin{itemize}
    \item Physical reasoning (cosmic censorship)
    \item All known examples
    \item No counterexamples despite searching
    \item DEC constraints make violation difficult
\end{itemize}

\textbf{But we lack:}
\begin{itemize}
    \item A rigorous proof
    \item Complete understanding of why it should be true
    \item A ``natural'' monotone quantity
\end{itemize}

\textbf{The gap between evidence and proof represents one of the deepest
mysteries in mathematical relativity.}
\end{tcolorbox}

\end{document}
