%% ORIGINAL_DISCOVERIES.tex
% A compact, provenance-tagged list of genuinely new mathematical constructions
% produced during the research. Each item is one-line (definition + short note)
% with provenance (source file(s)).

\section*{Original Discoveries (concise)}

% 1
\begin{description}

\item[Trapping Laplacian $L_T$] A surface differential operator encoding trapped-surface geometry via intrinsic Laplacian plus lower-order terms depending on null expansions and extrinsic curvature. (Provenance: MATHEMATICAL_INNOVATIONS.tex, TRAPPING_MASS_DUALITY.tex, SPECTRAL_TRAPPING_INEQUALITY.tex)

\item[Spectral Trapping Intensity / Spectral Gap $\delta_T$] Eigenvalue-based invariant built from the first eigenvalue $\lambda_1(L_T)$; conjectured links to quasi-local mass and area deficits. (Provenance: MATHEMATICAL_INNOVATIONS.tex, SPECTRAL_TRAPPING_INEQUALITY.tex)

\item[Sign-Invariant Trapping Intensity $\mathcal{I}(\Sigma)$] Averaged product of null expansions $\mathcal{I}:=\frac{1}{A}\int_\Sigma\theta^+\theta^-\,dA$, a sign-stable scalar capturing two-directional trapping. (Provenance: MATHEMATICAL_INNOVATIONS.tex)

\item[Dual $\theta$-Capacity $\widetilde{\mathrm{Cap}}_\theta$] A weighted capacitary functional coupling Riemannian capacity with null expansion weight; equals area on MOTS and controls area for general trapped surfaces. (Provenance: MATHEMATICAL_INNOVATIONS.tex, THETA_CAPACITY_THEORY.tex)

\item[Effective Area $A_{\mathrm{eff}}$] Modified area functional incorporating averaged extrinsic curvature (example formula: $A_{\mathrm{eff}}=A\,(1+2\overline{\kappa})$) used in entropic/transport bounds. (Provenance: MATHEMATICAL_INNOVATIONS.tex)

\item[Trapping Potential $\Psi$ and Trapping-Potential Mass Formula] A scalar solving a Poisson-type problem tied to trapped boundary data; its normal flux on an asymptotic surface yields ADM mass decomposition (flux + bulk matter term). (Provenance: MATHEMATICAL_INNOVATIONS.tex, TRAPPING_MASS_DUALITY.tex)

\item[New Quasi-local Mass Functionals] Several mass constructs tailored to trapped surfaces: Null-Product Hawking mass, Two-Term mass, Capacitary mass, Mass Aspect / Aspect mass; each combines null-expansion products, capacity or transport terms. (Provenance: MATHEMATICAL_INNOVATIONS.tex, NEW_QUASILOCAL_MASS.tex)

\item[Twisted Doubling Construction] A gluing/doubling method that flips extrinsic curvature signs asymmetrically to produce an auxiliary manifold with controlled null expansions for comparison arguments. (Provenance: MATHEMATICAL_INNOVATIONS.tex, TRAPPING_MASS_DUALITY.tex, DOUBLING_METHOD.tex)

\item[Symmetric--Antisymmetric (H--P) Decomposition] Decomposition of null expansions into symmetric (mean curvature) and antisymmetric (trace of $k$) parts: $\theta_S,\theta_A$; enables separating geometric vs extrinsic trapping contributions. (Provenance: MATHEMATICAL_INNOVATIONS.tex)

\item[Trapping Entropy $S_{\mathrm{trap}}$] An entropy-like functional built from $\theta^+\theta^-$ and effective area; conjectured monotonicity under causal/flow evolution and ties to generalized second law. (Provenance: MATHEMATICAL_INNOVATIONS.tex, TRAPPED_ENTROPY.tex)

\item[Lorentzian Optimal Transport / Lorentzian Cost $c=\tau^2$ and Causal Wasserstein] A causal optimal-transport framework using Lorentzian proper-time cost and causal transport plans; introduced transport Jacobian and a transport-based mass functional. (Provenance: MATHEMATICAL_INNOVATIONS.tex, OPTIMAL_TRANSPORT_PENROSE.tex, OPTIMAL_TRANSPORT_APPROACH.tex)

\item[Transport Jacobian \& Transport Mass] A Jacobian/area comparison along causal transport rays producing lower bounds of area via transport cost; used to define a transport-based quasi-local mass. (Provenance: MATHEMATICAL_INNOVATIONS.tex, OPTIMAL_TRANSPORT_PENROSE.tex)

\item[Trapping Flux Bound] Inequalities controlling the outward normal flux of the trapping potential from trapped surfaces; yields explicit ADM flux decomposition with geometry-dependent constants. (Provenance: MATHEMATICAL_INNOVATIONS.tex)

\item[Penrose Defect / Hawking Gap] Functionals measuring deficit between mass and area-informed lower bounds (Penrose Defect $D$, Hawking Gap $\Delta$) used to quantify how far a dataset is from equality (Schwarzschild). (Provenance: MATHEMATICAL_INNOVATIONS.tex)

\item[Variational Penrose Principle] A proposed variational characterization: Schwarzschild data minimize ADM mass among initial-data sets subject to fixed trapped-surface configuration (formulated as a constrained minimization over $(g,k)$). (Provenance: MATHEMATICAL_INNOVATIONS.tex, VARIATIONAL_PENROSE.tex)

\item[Raychaudhuri / Flow Compensation Inequalities] New compensation inequalities and evolution bounds for area/entropy under null flows derived from Raychaudhuri-type identities adapted to the trapping functionals. (Provenance: MATHEMATICAL_INNOVATIONS.tex)

\item[Spectral--Mass Conjectures] Conjectured inequalities linking spectral invariants of $L_T$ (e.g., $\lambda_1(L_T)$) to quasi-local mass/area via lower bounds analogous to Steklov or Cheeger-type inequalities. (Provenance: MATHEMATICAL_INNOVATIONS.tex, SPECTRAL_TRAPPING_INEQUALITY.tex)

\item[Causal Diamond Capacity] A Lorentzian capacity-like functional measuring the causal-volume/transport ability of the causal diamond generated by a trapped surface; proposed to control area via causal-volume isoperimetric bounds. (Provenance: NEW_TOOLS_PENROSE_1973.tex, paper.tex)

\item[Lorentzian Isoperimetric Inequality] A proposed family of inequalities comparing causal 4-volume (or diamond volume) to boundary 2-area; formulated as a Lorentzian analogue to Riemannian isoperimetric inequalities and suggested as a route to area bounds. (Provenance: NEW_TOOLS_PENROSE_1973.tex)

\end{description}

\section*{Short Verification Roadmap (immediate priorities)}

Contract (inputs/outputs, success):
\begin{itemize}
  \item Inputs: each item's precise definition in source file(s) named above; typical examples: spherically symmetric/Schwarzschild initial data, time-symmetric slices ($k=0$), simple nontrivial $k$ examples.
  \item Outputs: short proof sketch or worked example for each selected item; in particular numeric or analytic verification in symmetric cases and a one-paragraph provenance note.
  \item Success criteria: (i) formulas reproduce known special-case values (e.g., reduce to area or Hawking mass in MOTS/Schwarzschild), (ii) no immediate sign/definition pathologies, (iii) at least one rigorous lemma/proposition established for each top item.
\end{itemize}

Top-3 verification tasks (suggested, high impact):
\begin{enumerate}
  \item Trapping Laplacian $L_T$: compute $L_T$ explicitly on a round sphere in Schwarzschild slice and verify spectral trapping intensity formula; prove basic self-adjointness and first-eigenvalue variational characterization on closed surfaces.
  \item Dual $\theta$-Capacity: compute $\widetilde{\mathrm{Cap}}_\theta$ in spherically symmetric examples and show it equals area for MOTS; prove monotonicity property under outward null deformation in model case.
  \item Trapping Potential $\Psi$ and Flux Mass Formula: solve the model Poisson problem on a radial slice of Schwarzschild (or flat with a small $k$ perturbation) and verify the ADM flux decomposition (F2) stated in MATHEMATICAL_INNOVATIONS.tex.
\end{enumerate}

\section*{Next concrete actions I can take now}
\begin{itemize}
  \item Extract and expand the exact definitions and equations for the above top-3 items from their source files and produce small self-contained notes (definitions + a one-page worked Schwarzschild computation each).
  \item Produce short proofs/lemmas for basic analytical properties (well-posedness of $L_T$, variational formula for $\lambda_1$, existence/uniqueness for the trapping potential under reasonable boundary conditions).
  \item Add minimal tests/examples (analytic computations) and commit them as new tex files: e.g. ORIGINAL_VERIFICATIONS/1_trapping_laplacian_schwarzschild.tex, and run a quick consistency check.
\end{itemize}

% provenance note
\bigskip\noindent\textbf{Provenance:} This list was distilled from the project's master innovations file and source analyses, primarily: MATHEMATICAL_INNOVATIONS.tex, TRAPPING_MASS_DUALITY.tex, TRAPPED_ENTROPY.tex, OPTIMAL_TRANSPORT_PENROSE.tex, THETA_CAPACITY_THEORY.tex, TRAPPING_MASS_DUALITY.tex, NEW_QUASILOCAL_MASS.tex, DOUBLING_METHOD.tex, SPECTRAL_TRAPPING_INEQUALITY.tex.

% end
