% ACKNOWLEDGMENTS (CMP style - at end before references)
%=============================================================================

\vspace{1cm}
\noindent
\textbf{Acknowledgments.} The author thanks China Mobile Research Institute for institutional support during this research. The author is grateful to the anonymous referees for their careful reading and constructive suggestions that improved the exposition. The author also acknowledges helpful mathematical discussions with colleagues in the mathematical relativity community, particularly regarding the technical aspects of Jang equation analysis and the Mars--Simon characterization of Kerr spacetime. Special thanks are due to the developers of the symbolic computation tools used for verifying the Kerr saturation calculations.

%=============================================================================
% DATA AVAILABILITY STATEMENT (Required by CMP)
%=============================================================================

\vspace{0.5cm}
\noindent
\textbf{Data Availability Statement.} This manuscript has no associated data, as it is a theoretical mathematical physics paper containing only analytical results. The Python script used for numerical verification of Kerr saturation (Section~\ref{sec:kerr}) is available in the supplementary materials.

%=============================================================================
% CONFLICT OF INTEREST (Required by CMP)
%=============================================================================

\vspace{0.5cm}
\noindent
\textbf{Conflict of Interest Statement.} The author declares no conflicts of interest.

%=============================================================================
% REFERENCES (CMP uses numbered citations)
%=============================================================================

\newpage