\section{Function Space Compatibility Verification}\label{app:function-spaces}
%=============================================================================

This appendix provides a detailed verification that the hypotheses assumed in the external results (Han--Khuri, Dain--Reiris, AMO, Lockhart--McOwen) are compatible with the function space framework of this paper. This ensures the logical soundness of our proof, which builds upon these established results.

\subsection{Summary of Function Space Requirements}

\begin{table}[htbp]
\centering
\footnotesize
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{@{}p{3cm}p{4.5cm}p{4.5cm}p{2.5cm}@{}}
\toprule
\textbf{External Result} & \textbf{Their Hypotheses} & \textbf{Our Setting} & \textbf{Compatible?} \\
\midrule
Han--Khuri \cite{hankhuri2013} & $(g,K) \in C^{3,\beta}_{\mathrm{loc}}$, decay $\tau > 1/2$, DEC, stable MOTS & Def.~\ref{def:AF}, (H1), (H4) & \checkmark Yes \\
Dain--Reiris \cite{dain2011} & Axisymmetric, vacuum, stable MOTS, DEC & (H1)--(H4) & \checkmark Yes \\
AMO \cite{amo2022} & $R_{\tg} \geq 0$, AF end, compact boundary & Thm.~\ref{thm:lich-exist} output & \checkmark Yes \\
Lockhart--McOwen \cite{lockhartmccowen1985} & Asymp.\ cylindrical, $\beta_0 > 0$ & Thm.~\ref{thm:jang-exist}(iii) & \checkmark Yes \\
Mars--Simon \cite{mars1999, mars2009} & Vacuum, axisymmetric & (H2), (H3) & \checkmark Yes \\
\bottomrule
\end{tabular}
\caption{Function space compatibility between external results and our hypotheses.}
\label{tab:compatibility}
\end{table}

\subsection{Han--Khuri Jang Existence Theorem}

\begin{proposition}[Compatibility with Han--Khuri {\cite[Theorem~1.1]{hankhuri2013}}]\label{prop:hankhuri-compat}
The hypotheses of Theorem~\ref{thm:main} imply all requirements of the Han--Khuri Jang existence theorem.
\end{proposition}

\begin{proof}
We verify each hypothesis of \cite[Theorem~1.1]{hankhuri2013}:

\textbf{(HK1) Regularity:} Han--Khuri require $(g, K) \in C^{3,\beta}_{\mathrm{loc}}(M) \times C^{2,\beta}_{\mathrm{loc}}(M)$ for some $\beta \in (0,1)$. Our Definition~\ref{def:AF} specifies $C^{k,\beta}$ regularity with $k \geq 3$, which includes this case. The extrinsic curvature regularity $K \in C^{k-1,\beta}$ with $k \geq 3$ gives $K \in C^{2,\beta}$ as required.

\textbf{(HK2) Asymptotic flatness:} Han--Khuri use the standard Bartnik definition \cite{bartnik1986} with decay $\tau > 1/2$:
\begin{align*}
|g_{ij} - \delta_{ij}| &= O(r^{-\tau}), & |K_{ij}| &= O(r^{-\tau-1}).
\end{align*}
Our Definition~\ref{def:AF} specifies exactly these decay conditions with $\tau > 1/2$.

\textbf{(HK3) Dominant Energy Condition:} Han--Khuri require $\mu \geq |\momdens|_g$ where $\mu = \frac{1}{2}(R + (\tr K)^2 - |K|^2)$ and $\momdens_i = D^j K_{ji} - D_i(\tr K)$. This is precisely our hypothesis (H1) in Definition~\ref{def:DEC}.

\textbf{(HK4) Outermost Stable MOTS:} Han--Khuri require the existence of an outermost, stable MOTS $\Sigma$ with $\theta^+ = H + \tr_\Sigma K = 0$ and principal eigenvalue $\lambda_1(L_\Sigma) \geq 0$. Our hypothesis (H4) provides a \textbf{strictly stable} MOTS with $\lambda_1(L_\Sigma) > 0$, which is stronger.

\textbf{(HK5) Barrier conditions:} The existence of sub- and supersolutions for the Jang equation follows from DEC and the outermost property of $\Sigma$ \cite[Proposition~4.1]{hankhuri2013}.

All conditions are satisfied. \qedhere
\end{proof}

\subsection{Dain--Reiris Area-Angular Momentum Inequality}

\begin{proposition}[Compatibility with Dain--Reiris {\cite[Theorem~1]{dain2011}}]\label{prop:dainreiris-compat}
The hypotheses of Theorem~\ref{thm:main} imply all requirements of the Dain--Reiris inequality $A \geq 8\pi|J|$.
\end{proposition}

\begin{proof}
The Dain--Reiris theorem requires:

\textbf{(DR1) Axisymmetry:} The data admits a Killing field $\eta = \partial_\phi$ with axis $\Gamma$. This is our hypothesis (H2).

\textbf{(DR2) Vacuum:} The constraint equations hold with $\mu = |\momdens| = 0$. Our hypothesis (H3) requires vacuum in the exterior region $M_{\mathrm{ext}}$. Since the MOTS $\Sigma \subset M_{\mathrm{ext}}$ by definition of outermost, the Dain--Reiris inequality applies to $\Sigma$.

\textbf{(DR3) Stable MOTS:} The MOTS must be stable ($\lambda_1(L_\Sigma) \geq 0$). Our hypothesis (H4) gives strict stability $\lambda_1(L_\Sigma) > 0$, which is stronger.

\textbf{(DR4) Asymptotic flatness:} The decay conditions match Definition~\ref{def:AF}.

\textbf{Komar angular momentum agreement:} The Dain--Reiris angular momentum is defined as:
\[
J_{DR} = \frac{1}{8\pi}\int_\Sigma K(\eta, \nu)\,d\sigma,
\]
which is exactly our Definition in Theorem~\ref{thm:main}. The equivalence with ADM angular momentum follows from \cite[Proposition~2.3]{chrusciel2008} under the vacuum and decay hypotheses.

All conditions are satisfied. \qedhere
\end{proof}

\subsection{AMO \texorpdfstring{$p$}{p}-Harmonic Flow}

\begin{proposition}[Compatibility with AMO {\cite[Theorem~1.1]{amo2022}}]\label{prop:amo-compat}
The conformal manifold $(\tM, \tg)$ produced by Theorem~\ref{thm:lich-exist} satisfies all requirements of the AMO monotonicity theorem.
\end{proposition}

\begin{proof}
The AMO framework requires:

\textbf{(AMO1) Non-negative scalar curvature:} $R_{\tg} \geq 0$. By Theorem~\ref{thm:lich-exist}, after solving the AM-Lichnerowicz equation, we have $R_{\tg} = \Lambda_J \phi^{-12} \geq 0$ since $\Lambda_J \geq 0$ (Definition~\ref{def:Lambda-J}) and $\phi > 0$.

\textbf{(AMO2) Asymptotic flatness:} The conformal manifold $(\tM, \tg)$ is asymptotically flat with the same decay rate as the original data. This follows from $\phi \to 1$ as $r \to \infty$ (Theorem~\ref{thm:lich-exist}(ii)) and the conformal transformation formula:
\[
\tg_{ij} - \delta_{ij} = \phi^4(g_{ij} - \delta_{ij}) + (\phi^4 - 1)\delta_{ij} = O(r^{-\tau}).
\]

\textbf{(AMO3) Boundary structure:} The AMO theory requires a compact inner boundary. In our setting, the cylindrical end is \textbf{compactified} by adding the MOTS $\Sigma$ as a boundary component. The boundary condition $u_p|_\Sigma = 0$ is well-posed because the cylindrical end structure (Theorem~\ref{thm:jang-exist}(iii)) ensures the $p$-harmonic potential extends continuously to $\Sigma$.

\textbf{(AMO4) Bounded geometry:} The AMO estimates require bounded curvature and injectivity radius on compact subsets. This follows from:
\begin{itemize}
    \item $\tg$ is smooth on $\tM \setminus \Sigma$ (elliptic regularity);
    \item On the cylindrical end, $\tg = dt^2 + g_\Sigma + O(e^{-\beta_0 t})$ has exponentially controlled curvature;
    \item Injectivity radius is bounded below by compactness of $\Sigma$ and the controlled cylindrical geometry.
\end{itemize}

All conditions are satisfied. \qedhere
\end{proof}

\subsection{Lockhart--McOwen Fredholm Theory}

\begin{proposition}[Compatibility with Lockhart--McOwen {\cite{lockhartmccowen1985}}]\label{prop:lm-compat}
The AM-Lichnerowicz equation on the Jang manifold satisfies the hypotheses of Lockhart--McOwen Fredholm theory.
\end{proposition}

\begin{proof}
The Lockhart--McOwen framework applies to elliptic operators on manifolds with cylindrical ends. We verify:

\textbf{(LM1) Cylindrical end structure:} By Theorem~\ref{thm:jang-exist}(iii), the Jang manifold $(\bM, \bg)$ has a cylindrical end $\mathcal{C} \cong [0,\infty) \times \Sigma$ with metric:
\[
\bg = dt^2 + g_\Sigma + h(t), \quad |h(t)| = O(e^{-\beta_0 t}),
\]
where $\beta_0 = 2\sqrt{\lambda_1(L_\Sigma)} > 0$ by strict stability (Remark~\ref{rem:mots-decay-alignment}).

\textbf{(LM2) Elliptic operator:} The AM-Lichnerowicz operator $\mathcal{L}\phi = -8\Delta_{\bg}\phi + R_{\bg}\phi - \Lambda_J\phi^{-7}$ is uniformly elliptic. Linearizing around $\phi = 1$:
\[
D\mathcal{L}|_{\phi=1}[\psi] = -8\Delta_{\bg}\psi + (R_{\bg} + 7\Lambda_J)\psi.
\]
On the cylindrical end, this asymptotes to:
\[
-8\partial_t^2\psi - 8\Delta_\Sigma\psi + R_\Sigma\psi,
\]
which is the model operator for the Lockhart--McOwen theory.

\textbf{(LM3) Indicial roots:} The indicial equation at the cylindrical end is:
\[
-8\lambda^2 + \mu_k = 0 \quad \Rightarrow \quad \lambda_k = \pm\sqrt{\mu_k/8},
\]
where $\mu_k$ are eigenvalues of $-\Delta_\Sigma + R_\Sigma/8$ on $\Sigma$. By Lemma~\ref{lem:fredholm}, the smallest positive indicial root $\lambda_0 > 0$ ensures Fredholm theory applies for weights $\delta \in (-\lambda_0, 0)$.

\textbf{(LM4) Decay rate requirement:} The geometric decay rate $\beta_0 = 2\sqrt{\lambda_1(L_\Sigma)} > 0$ (from strict stability) satisfies $\beta_0 > \lambda_0$ generically, ensuring a non-empty weight interval.

All conditions are satisfied. \qedhere
\end{proof}

\subsection{Mars--Simon Kerr Characterization}

\begin{proposition}[Compatibility with Mars--Simon {\cite{mars1999, mars2009}}]\label{prop:mars-compat}
The rigidity analysis (Theorem~\ref{thm:rigidity}) correctly applies the Mars--Simon characterization of Kerr.
\end{proposition}

\begin{proof}
The Mars--Simon theorem characterizes Kerr spacetime via the vanishing of the Simon tensor. We verify the hypotheses:

\textbf{(MS1) Vacuum:} The Mars--Simon characterization requires vacuum Einstein equations. Our hypothesis (H3) ensures vacuum in the exterior region where the rigidity analysis takes place.

\textbf{(MS2) Axisymmetry:} A Killing field $\eta$ is required. This is hypothesis (H2).

\textbf{(MS3) Asymptotic flatness:} Standard AF conditions are required, matching Definition~\ref{def:AF}.

\textbf{(MS4) Stationarity (for spacetime):} The Mars theorem originally assumed stationarity. However, the B\"ackdahl--Valiente Kroon extension \cite{backdahl2010a, backdahl2010b} shows that the \textbf{initial data} version (vanishing of the Kerr deviation tensor $\mathcal{S}_{(g,K)} = 0$) characterizes Kerr slices without assuming the spacetime is stationary. This is the formulation we use in Definition~\ref{def:Lambda-J}.

The Kerr deviation tensor $\mathcal{S}_{(g,K)}$ is constructed intrinsically from $(g, K)$ using the electric/magnetic decomposition of the Weyl tensor (see Appendix~\ref{app:mars-simon}), and vanishes if and only if the data is a slice of Kerr.

All conditions are satisfied. \qedhere
\end{proof}

\subsection{Summary of Compatibility}

\begin{mdframed}[linewidth=1pt, linecolor=green!60!black, backgroundcolor=green!3]
\textbf{Conclusion.} All external results used in the proof of Theorem~\ref{thm:main} have been verified to be compatible with our function space framework. The key points are:
\begin{enumerate}[label=(\arabic*)]
    \item The regularity $C^{k,\beta}$ with $k \geq 3$ and $\beta \in (0,1)$ is sufficient for all PDE existence results.
    \item The decay rate $\tau > 1/2$ matches the standard Bartnik asymptotic flatness.
    \item Strict stability ($\lambda_1 > 0$) is stronger than the stability ($\lambda_1 \geq 0$) required by Han--Khuri and Dain--Reiris.
    \item The vacuum exterior hypothesis (H3) is used for both Dain--Reiris and Mars--Simon.
    \item The cylindrical decay rate $\beta_0 > 0$ from strict stability enables Lockhart--McOwen theory.
\end{enumerate}
The proof chain is therefore logically sound.
\end{mdframed}
