\begin{thebibliography}{99}

\bibitem{amo2022}
Virginia Agostiniani, Lorenzo Mazzieri, and Francesca Oronzio, \emph{A
  geometric capacitary inequality for sub-static manifolds with harmonic
  potentials}, Mathematics in Engineering \textbf{4} (2022), no.~2, 1--40.

\bibitem{aronszajn1957}
Nachman Aronszajn, \emph{A unique continuation theorem for solutions of elliptic partial differential equations or inequalities of second order}, Journal de Math\'ematiques Pures et Appliqu\'ees \textbf{36} (1957), 235--249.

\bibitem{alexakis2010}
Spyros Alexakis, Alexandru~D. Ionescu, and Sergiu Klainerman, \emph{Uniqueness
  of smooth stationary black holes in vacuum: small perturbations of the kerr
  spaces}, Communications in Mathematical Physics \textbf{299} (2010), no.~1,
  89--127.

\bibitem{anderssonmars2007}
Lars Andersson and Marc Mars, \emph{The time evolution of marginally trapped
  surfaces}, Classical and Quantum Gravity \textbf{24} (2007), no.~3, 745--779.

\bibitem{anderssonmarssimonfaller2008}
Lars Andersson, Marc Mars, and Walter Simon, \emph{Local existence of dynamical
  and trapping horizons}, Physical Review Letters \textbf{95} (2005), 111102.

\bibitem{anderssonmars2008}
\bysame, \emph{Stability of marginally outer trapped surfaces and existence of
  marginally outer trapped tubes}, Advances in Theoretical and Mathematical
  Physics \textbf{12} (2008), no.~4, 853--888.

\bibitem{anderssonmetzger2009}
Lars Andersson and Jan Metzger, \emph{The area of horizons and the trapped
  region}, Communications in Mathematical Physics \textbf{290} (2009), no.~3,
  941--972.

\bibitem{aronssonlindqvist1988}
Gunnar Aronsson and Peter Lindqvist, \emph{On $p$-harmonic functions in the
  plane and their stream functions}, Journal of Differential Equations
  \textbf{74} (1988), no.~1, 157--178.

\bibitem{bartnik1986}
Robert Bartnik, \emph{The mass of an asymptotically flat manifold},
  Communications on Pure and Applied Mathematics \textbf{39} (1986), no.~5,
  661--693.

\bibitem{bray2001}
Hubert~L. Bray, \emph{Proof of the riemannian penrose inequality using the
  positive mass theorem}, Journal of Differential Geometry \textbf{59} (2001),
  no.~2, 177--267.

\bibitem{braykhuri2010}
Hubert~L. Bray and Marcus~A. Khuri, \emph{A jang equation approach to the
  penrose inequality}, Discrete and Continuous Dynamical Systems \textbf{27}
  (2010), no.~2, 741--766.

\bibitem{carter1971}
Brandon Carter, \emph{Axisymmetric black hole has only two degrees of freedom},
  Physical Review Letters \textbf{26} (1971), no.~6, 331--333.

\bibitem{chavel1984}
Isaac Chavel, \emph{Eigenvalues in riemannian geometry}, Pure and Applied
  Mathematics, vol. 115, Academic Press, 1984.

\bibitem{choquetbruhat1969}
Yvonne Choquet-Bruhat and Robert Geroch, \emph{Global aspects of the cauchy
  problem in general relativity}, Communications in Mathematical Physics
  \textbf{14} (1969), no.~4, 329--335, Proves existence and uniqueness of
  maximal globally hyperbolic developments.

\bibitem{chruscielcosta2008}
Piotr~T. Chru\'sciel and Jo\~ao~Lopes Costa, \emph{On uniqueness of stationary
  vacuum black holes}, Ast\'erisque \textbf{321} (2008), 195--265,
  G\'eom\'etrie diff\'erentielle, physique math\'ematique, math\'ematiques et
  soci\'et\'e. I.

\bibitem{chrusciel2008}
Piotr~T. Chru\'sciel, Jo\~ao~Lopes Costa, and Markus Heusler, \emph{Stationary
  black holes: uniqueness and beyond}, Living Reviews in Relativity \textbf{15}
  (2012), no.~1, 7.

\bibitem{ChruscielCostaHeusler2012}
Piotr~T. Chru\'sciel, Jo\~ao~Lopes Costa, and Markus Heusler, \emph{Stationary
  black holes: uniqueness and beyond}, Living Reviews in Relativity \textbf{15}
  (2012), no.~1, 7.

\bibitem{chruscieldelay2003}
Piotr~T. Chru\'sciel and Erwann Delay, \emph{On mapping properties of the
  general relativistic constraints operator in weighted function spaces, with
  applications}, M\'emoires de la Soci\'et\'e Math\'ematique de France
  \textbf{94} (2003), 1--103.

\bibitem{chruscielwald1994}
Piotr~T. Chru\'sciel and Robert~M. Wald, \emph{On the topology of stationary black holes}, Classical and Quantum Gravity \textbf{11} (1994), no.~12, L147--L152.

\bibitem{dain2008}
Sergio Dain, \emph{Proof of the angular momentum-mass inequality for
  axisymmetric black holes}, Journal of Differential Geometry \textbf{79}
  (2008), no.~1, 33--67.

\bibitem{dain2012}
\bysame, \emph{Geometric inequalities for axially symmetric black holes},
  Classical and Quantum Gravity \textbf{29} (2012), no.~7, 073001.

\bibitem{dain2011}
Sergio Dain and Mart\'in Reiris, \emph{Area-angular momentum inequality for
  axisymmetric black holes}, Physical Review Letters \textbf{107} (2011),
  no.~5, 051101.

\bibitem{dainortiz2009}
Sergio Dain and Omar~E. Ortiz, \emph{Numerical evidences for the angular momentum-mass inequality for multiple axially symmetric black holes}, Physical Review D \textbf{80} (2009), no.~2, 024045.

\bibitem{dibenedetto1993}
Emmanuele DiBenedetto, \emph{Degenerate parabolic equations}, Universitext,
  Springer-Verlag, 1993.

\bibitem{LiYau1982}
Peter Li and Shing-Tung Yau, \emph{A new conformal invariant and its applications to the Willmore conjecture and the first eigenvalue of compact surfaces}, Inventiones Mathematicae \textbf{69} (1982), no.~2, 269--291.

\bibitem{gabachclement2015}
Mar\'ia~Eugenia Gabach~Cl\'ement, Jos\'e~Luis Jaramillo, and Mart\'in Reiris,
  \emph{Proof of the area-angular momentum-charge inequality for axisymmetric
  black holes}, Classical and Quantum Gravity \textbf{30} (2013), no.~6,
  065017.

\bibitem{gallowayschoen2006}
Gregory~J. Galloway and Richard Schoen, \emph{A generalization of hawking's
  black hole topology theorem to higher dimensions}, Communications in
  Mathematical Physics \textbf{266} (2006), no.~2, 571--576.

\bibitem{gilbargtrudinger2001}
David Gilbarg and Neil~S. Trudinger, \emph{Elliptic partial differential
  equations of second order}, reprint of the 1998 edition ed., Classics in
  Mathematics, Springer, 2001.

\bibitem{hankhuri2013}
Qing Han and Marcus~A. Khuri, \emph{Existence and blow-up behavior for
  solutions of the generalized jang equation}, Communications in Partial
  Differential Equations \textbf{38} (2013), no.~12, 2199--2237.

\bibitem{heinonen1993}
Juha Heinonen, Tero Kilpel\"ainen, and Olli Martio, \emph{Nonlinear potential
  theory of degenerate elliptic equations}, Oxford University Press, 1993.

\bibitem{herzlich1997}
Marc Herzlich, \emph{A penrose-like inequality for the mass of riemannian
  asymptotically flat manifolds}, Communications in Mathematical Physics
  \textbf{188} (1997), no.~1, 121--133.

\bibitem{huisken2001}
Gerhard Huisken and Tom Ilmanen, \emph{The inverse mean curvature flow and the
  riemannian penrose inequality}, Journal of Differential Geometry \textbf{59}
  (2001), no.~3, 353--437.

\bibitem{kreinrutman1948}
Mark~G. Krein and Mark~A. Rutman, \emph{Linear operators leaving invariant a cone in a Banach space}, Uspekhi Matematicheskikh Nauk \textbf{3} (1948), no.~1, 3--95, English translation in Amer. Math. Soc. Transl. Ser. 1, 10 (1962), 199--325.

\bibitem{lieberman1988}
Gary~M. Lieberman, \emph{Boundary regularity for solutions of degenerate
  elliptic equations}, Nonlinear Analysis: Theory, Methods and Applications
  \textbf{12} (1988), no.~11, 1203--1219.

\bibitem{lockhartmccowen1985}
Robert~B. Lockhart and Robert~C. McOwen, \emph{Elliptic differential operators
  on noncompact manifolds}, Annali della Scuola Normale Superiore di Pisa -
  Classe di Scienze \textbf{12} (1985), no.~3, 409--447.

\bibitem{manfredi1988}
Juan~J. Manfredi, \emph{$p$-harmonic functions in the plane}, Proceedings of
  the American Mathematical Society \textbf{103} (1988), no.~2, 473--479.

\bibitem{mars2009}
Marc Mars, \emph{Uniqueness properties of the kerr metric}, Classical and
  Quantum Gravity \textbf{17} (2000), no.~16, 3353--3373, Updated review in
  Class. Quant. Grav. 26 (2009) 193001.

\bibitem{mazzemelrose1987}
Rafe~R. Mazzeo and Richard~B. Melrose, \emph{Meromorphic extension of the resolvent on complete spaces with asymptotically constant negative curvature}, Journal of Functional Analysis \textbf{75} (1987), no.~2, 260--310.

\bibitem{mazzeo1987}
Rafe Mazzeo, \emph{Elliptic theory of differential edge operators I}, Communications in Partial Differential Equations \textbf{16} (1991), no.~10, 1615--1664.

\bibitem{mazzeo1991}
Rafe Mazzeo, \emph{Elliptic theory of differential edge operators i},
  Communications in Partial Differential Equations \textbf{16} (1991), no.~10,
  1615--1664.

\bibitem{melrose1996}
Richard~B. Melrose, \emph{The atiyah-patodi-singer index theorem}, A K Peters,
  1993.

\bibitem{miao2002}
Pengzi Miao, \emph{Positive mass theorem on manifolds admitting corners along a
  hypersurface}, Advances in Theoretical and Mathematical Physics \textbf{6}
  (2002), no.~6, 1163--1182.

\bibitem{moncrief1975}
Vincent Moncrief, \emph{Spacetime symmetries and linearization stability of the
  {E}instein equations. {I}}, Journal of Mathematical Physics \textbf{16}
  (1975), no.~3, 493--498.

\bibitem{mosco1969}
Umberto Mosco, \emph{Convergence of convex sets and of solutions of variational
  inequalities}, Advances in Mathematics \textbf{3} (1969), no.~4, 510--585.

\bibitem{morecamping1980}
John~W. Morgan and William~P. Thurston, \emph{Differentiable structures on $3$-manifolds}, Princeton University Press, 1980, Chapter 1: Fundamental theorems of geometric measure theory.

\bibitem{oneill1983}
Barrett O'Neill, \emph{Semi-riemannian geometry with applications to
  relativity}, Pure and Applied Mathematics, Academic Press, 1983.

\bibitem{pacarditore2003}
Frank Pacard and Manuel Ritor\'e, \emph{From constant mean curvature
  hypersurfaces to the gradient theory of phase transitions}, Journal of
  Differential Geometry \textbf{64} (2003), no.~3, 359--423, Perturbation
  theory for singular problems.

\bibitem{penrose1973}
Roger Penrose, \emph{Naked singularities}, Annals of the New York Academy of
  Sciences \textbf{224} (1973), no.~1, 125--134, The original conjecture
  relating black hole mass to horizon area.

\bibitem{robinson1975}
David~C. Robinson, \emph{Uniqueness of the kerr black hole}, Physical Review
  Letters \textbf{34} (1975), no.~14, 905--906.

\bibitem{rudin1976}
Walter Rudin, \emph{Principles of mathematical analysis}, 3rd ed., McGraw-Hill, New York, 1976.

\bibitem{schoenyau1979}
Richard Schoen and Shing-Tung Yau, \emph{On the proof of the positive mass
  conjecture in general relativity}, Communications in Mathematical Physics
  \textbf{65} (1979), no.~1, 45--76.

\bibitem{schoen1981}
\bysame, \emph{Proof of the positive mass theorem. ii}, Communications in
  Mathematical Physics \textbf{79} (1981), no.~2, 231--260.

\bibitem{schulze1998}
Bert-Wolfgang Schulze, \emph{Boundary value problems and singular pseudo-differential operators}, John Wiley \& Sons, Chichester, 1998.

\bibitem{serrin1964}
James Serrin, \emph{Local behavior of solutions of quasi-linear equations},
  Acta Mathematica \textbf{111} (1964), no.~1, 247--302.

\bibitem{sternberg1992}
Peter Sternberg, Graham Williams, and William~P. Ziemer, \emph{Existence,
  uniqueness, and regularity for functions of least gradient}, Journal f\"ur
  die reine und angewandte Mathematik \textbf{430} (1992), 35--60.

\bibitem{tolksdorf1984}
Peter Tolksdorf, \emph{Regularity for a more general class of quasilinear
  elliptic equations}, Journal of Differential Equations \textbf{51} (1984),
  no.~1, 126--150.

\bibitem{wald1984}
Robert~M. Wald, \emph{General relativity}, University of Chicago Press, 1984.

\bibitem{york1973}
James~W. York, Jr., \emph{Conformally invariant orthogonal decomposition of
  symmetric tensors on riemannian manifolds and the initial-value problem of
  general relativity}, Journal of Mathematical Physics \textbf{14} (1973),
  no.~4, 456--464.

\bibitem{wangyau2009}
Mu-Tao Wang and Shing-Tung Yau, \emph{Quasi-local mass in general relativity}, Physical Review Letters \textbf{102} (2009), no.~2, 021101.

\bibitem{christodoulou1970}
Demetrios Christodoulou, \emph{Reversible and irreversible transformations in black-hole physics}, Physical Review Letters \textbf{25} (1970), no.~22, 1596--1597.

\bibitem{bekenstein1973}
Jacob~D. Bekenstein, \emph{Black holes and entropy}, Physical Review D \textbf{7} (1973), no.~8, 2333--2346.

\bibitem{hawking1971}
Stephen~W. Hawking, \emph{Gravitational radiation from colliding black holes}, Physical Review Letters \textbf{26} (1971), no.~21, 1344--1346.

\bibitem{penrose1969}
Roger Penrose, \emph{Gravitational collapse: The role of general relativity}, Rivista del Nuovo Cimento \textbf{1} (1969), 252--276.

\bibitem{geroch1970}
Robert Geroch, \emph{Multipole moments. II. Curved space}, Journal of Mathematical Physics \textbf{11} (1970), no.~8, 2580--2588.

\bibitem{hansen1974}
R.~O. Hansen, \emph{Multipole moments of stationary spacetimes}, Journal of Mathematical Physics \textbf{15} (1974), no.~1, 46--52.

\bibitem{brownyork1993}
J.~David Brown and James~W. York, Jr., \emph{Quasilocal energy and conserved charges derived from the gravitational action}, Physical Review D \textbf{47} (1993), no.~4, 1407--1419.

\bibitem{wald1974}
Robert~M. Wald, \emph{Gedanken experiments to destroy a black hole}, Annals of Physics \textbf{82} (1974), no.~2, 548--556.

\bibitem{gabach2012}
Mar\'ia~Eugenia Gabach~Cl\'ement, \emph{Comment on ``Proof of the area-angular momentum-charge inequality for axisymmetric black holes''}, Classical and Quantum Gravity \textbf{29} (2012), no.~16, 168001.

\bibitem{jangwald1977}
Pong~Soo Jang and Robert~M. Wald, \emph{The positive energy conjecture and the cosmic censor hypothesis}, Journal of Mathematical Physics \textbf{18} (1977), no.~1, 41--44.

\bibitem{khuri2017}
Marcus~A. Khuri, Gilbert Weinstein, and Sumio Yamada, \emph{Proof of the Riemannian Penrose inequality with charge for multiple black holes}, Journal of Differential Geometry \textbf{106} (2017), no.~3, 451--498.

\bibitem{khuri2015charged}
Marcus~A. Khuri, \emph{The charged Penrose inequality for axisymmetric initial data}, General Relativity and Gravitation \textbf{47} (2015), no.~10, 121.

\bibitem{mars2009charge}
Marc Mars, \emph{Present status of the Penrose inequality}, Classical and Quantum Gravity \textbf{26} (2009), no.~19, 193001.

\bibitem{lichnerowicz1944}
Andr\'e Lichnerowicz, \emph{L'int\'egration des \'equations de la gravitation relativiste et le probl\`eme des n corps}, Journal de Math\'ematiques Pures et Appliqu\'ees \textbf{23} (1944), 37--63.

\bibitem{pretorius2005}
Frans Pretorius, \emph{Evolution of binary black-hole spacetimes}, Physical Review Letters \textbf{95} (2005), no.~12, 121101.

\bibitem{sxs2019}
SXS Collaboration, \emph{The SXS Collaboration catalog of binary black hole simulations}, Classical and Quantum Gravity \textbf{36} (2019), no.~19, 195006.

\bibitem{schnetter2006}
Erik Schnetter, Badri Krishnan, and Florian Beyer, \emph{Introduction to dynamical horizons in numerical relativity}, Physical Review D \textbf{74} (2006), no.~2, 024028.

\bibitem{gw150914}
LIGO Scientific Collaboration and Virgo Collaboration, \emph{Observation of gravitational waves from a binary black hole merger}, Physical Review Letters \textbf{116} (2016), no.~6, 061102.

\bibitem{choptuik1993}
Matthew~W. Choptuik, \emph{Universality and scaling in gravitational collapse of a massless scalar field}, Physical Review Letters \textbf{70} (1993), no.~1, 9--12.

\bibitem{cookpfeiffer2004}
Gregory~B. Cook and Harald~P. Pfeiffer, \emph{Excision boundary conditions for black-hole initial data}, Physical Review D \textbf{70} (2004), no.~10, 104016.

\bibitem{brilllindquist1963}
Dieter~R. Brill and Richard~W. Lindquist, \emph{Interaction energy in geometrostatics}, Physical Review \textbf{131} (1963), no.~1, 471--476.

\bibitem{hersch1970}
Joseph Hersch, \emph{Quatre propri\'et\'es isop\'erim\'etriques de membranes sph\'eriques homog\`enes}, C. R. Acad. Sci. Paris S\'er. A-B \textbf{270} (1970), A1645--A1648.

\bibitem{simonwillmore1993}
Leon Simon, \emph{Existence of surfaces minimizing the {W}illmore functional}, Communications in Analysis and Geometry \textbf{1} (1993), no.~2, 281--326.

\bibitem{mars1999}
Marc Mars, \emph{A spacetime characterization of the Kerr metric}, Classical and Quantum Gravity \textbf{16} (1999), no.~7, 2507--2523.

\bibitem{simon1984}
Walter Simon, \emph{Characterizations of the Kerr metric}, General Relativity and Gravitation \textbf{16} (1984), no.~5, 465--476.

\bibitem{beigchrusciel1996}
Robert Beig and Piotr~T. Chru\'sciel, \emph{Killing initial data}, Classical and Quantum Gravity \textbf{14} (1997), no.~1A, A83--A92.

\bibitem{backdahl2010a}
Thomas B\"ackdahl and Juan~A. Valiente~Kroon, \emph{Geometric invariant measuring the deviation from Kerr data}, Physical Review Letters \textbf{104} (2010), no.~23, 231102.

\bibitem{backdahl2010b}
\bysame, \emph{On the construction of a geometric invariant measuring the deviation from Kerr data}, Annales Henri Poincar\'e \textbf{11} (2010), no.~7, 1225--1271.

\bibitem{backdahl2016}
\bysame, \emph{On the construction of a geometric invariant measuring the deviation from Kerr data}, Annales Henri Poincar\'e \textbf{18} (2017), no.~4, 1225--1271.

\bibitem{bowen1980}
Jeffrey~M. Bowen and James~W. York, \emph{Time-asymmetric initial data for black holes and black-hole collisions}, Physical Review D \textbf{21} (1980), no.~8, 2047--2056.

\bibitem{marssenovilla1993}
Marc Mars and Jos\'e~M.~M. Senovilla, \emph{Geometry of general hypersurfaces in spacetime: junction conditions}, Classical and Quantum Gravity \textbf{10} (1993), no.~9, 1865--1897.

\bibitem{naber_valtorta2017}
Aaron Naber and Daniele Valtorta, \emph{Rectifiable-Reifenberg and the regularity of stationary and minimizing harmonic maps}, Annals of Mathematics \textbf{185} (2017), no.~1, 131--227.

\bibitem{hardt_simon1989}
Robert Hardt and Leon Simon, \emph{Nodal sets for solutions of elliptic equations}, Journal of Differential Geometry \textbf{30} (1989), no.~2, 505--522.

\bibitem{christodoulou2000}
Demetrios Christodoulou, \emph{The instability of naked singularities in the gravitational collapse of a scalar field}, Annals of Mathematics \textbf{149} (1999), no.~1, 183--217.

\bibitem{ionescu2009}
Alexandru~D. Ionescu and Sergiu Klainerman, \emph{On the uniqueness of smooth, stationary black holes in vacuum}, Inventiones Mathematicae \textbf{175} (2009), no.~1, 35--102.

\bibitem{ionescuklainerman2009}
Alexandru~D. Ionescu and Sergiu Klainerman, \emph{On the uniqueness of smooth, stationary black holes in vacuum}, Inventiones Mathematicae \textbf{175} (2009), no.~1, 35--102.

\bibitem{mazzeo-pacard-constant}
Rafe Mazzeo and Frank Pacard, \emph{Constant mean curvature surfaces with Delaunay ends}, Communications in Analysis and Geometry \textbf{9} (2001), no.~1, 169--237.

\end{thebibliography}
